\documentclass[12pt]{article}
\usepackage{pmmeta}
\pmcanonicalname{HomotopyCoherentCoalgebras}
\pmcreated{2026-02-28 00:33:00}
\pmmodified{2026-02-28 00:33:00}
\pmowner{codex}{00000}
\pmmodifier{codex}{00000}
\pmtitle{point-set models for homotopy coherent coalgebras}
\pmrecord{11}{999996}
\pmprivacy{1}
\pmauthor{codex}{00000}
\pmtype{Topic}
\pmclassification{msc}{18G99}
\pmdefines{homotopy coherent coalgebra}
\pmdefines{$\infty$-operad coalgebra}

\endmetadata

\usepackage{amsmath, amssymb}

\begin{document}
Homotopy coherent coalgebras arise when one equips chain complexes with coalgebra structures defined only up to higher coherent homotopies. Roca i Lucio--Petersen--Yalin (arXiv:2601.03101) provide explicit point-set models for such objects by comparing two different $\infty$-categorical descriptions.

\medskip
\noindent\textbf{Two $\infty$-categories of coalgebras.} On one side they start with differential graded coalgebras over an operad and localize with respect to quasi-isomorphisms, producing an $\infty$-category via Dwyer--Kan localization. On the other they define coalgebras for an enriched $\infty$-operad inside the derived $\infty$-category of chain complexes. The main theorem proves these two $\infty$-categories are equivalent whenever the operad is cofibrant.

\medskip
\noindent\textbf{Rectification.} The equivalence is obtained inductively by attaching cells and comparing mapping spaces at each stage. It shows that every homotopy coherent coalgebra admits a strict (point-set) representative up to contractible choice. As a result one can work concretely with dg coalgebras without losing higher information.

\medskip
\noindent\textbf{Examples.} The authors specialize to $E_n$- and $E_\infty$-coalgebras in the derived $\infty$-category of chain complexes over a field, obtaining honest dg models. They also recover an explicit point-set model for the cellular chains functor equipped with its $E_\infty$-coalgebra structure and combine this with work of Bachmann--Burklund to produce algebraic models for nilpotent $p$-adic homotopy types.

\medskip
These rectification results turn the abstract notion of homotopy coherent coalgebra into something one can compute with: a dg coalgebra whose structure maps and higher coherences are recorded by an enriched operad but whose underlying objects live in an ordinary (point-set) category.

\bigskip
\noindent\textbf{Reference.}
\begin{itemize}
  \item V. Roca i Lucio, D. Petersen, S. Yalin, \emph{Point-set models for homotopy coherent coalgebras}, arXiv:2601.03101 (2026).
\end{itemize}
\end{document}
