% PlanetMath proposal draft for arXiv:0704.1624
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Complete Segal spaces from simplicial categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:0704.1624, "Complete Segal spaces arising from simplicial categories" (2007-04-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Bergner compares functors sending simplicial (or model) categories to complete Segal spaces, characterizes these spaces up to weak equivalence, and clarifies relationships between different models of homotopy theories.
\begin{enumerate}
  \item reviews functors from simplicial/model categories to complete Segal spaces;
  \item compares resulting spaces and weak equivalences;
  \item characterizes complete Segal spaces arising from these functors.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470620] Question on comparing complete Segal space constructions.
  \item[MO 470648] Thread on modeling homotopy theories via simplicial categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507740] "Complete Segal spaces vs. simplicial categories".
  \item[Math.SE 507778] "Weak equivalences of complete Segal spaces".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Models of homotopy theory.} Summarize simplicial cats, CSS (Math.SE 507740).
  \item \textbf{Comparison functors.} Describe constructions (MO 470620).
  \item \textbf{Characterization.} Present weak equivalence results (MO 470648, Math.SE 507778).
  \item \textbf{PlanetMath links.} Connect to Lurie's Higher Topos Theory and model categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for detailed comparisons.
  \item Pull MO embeddings (470620, 470648) and Math.SE embeddings (507740, 507778).
  \item Draft the PlanetMath entry summarizing these equivalences.
\end{itemize}
