% PlanetMath proposal draft for arXiv:0704.2207
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Adjoint functors via heteromorphisms}
\subsection*{Source}
\begin{itemize}
  \item arXiv:0704.2207, "Adjoint Functors and Heteromorphisms" (2007-04-17)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Ellerman develops a theory of adjoint functors grounded in heteromorphisms—object-to-object maps between different categories (e.g., set-to-group insertions). He shows heteromorphisms can be treated categorically and that adjunctions arise from birepresentations of heteromorphisms.
\begin{enumerate}
  \item formalizes heteromorphisms within category theory;
  \item relates heteromorphisms to adjunction birepresentations;
  \item recasts adjoint functors using this framework and provides examples.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470750] Question on heteromorphisms and adjunctions.
  \item[MO 470788] Discussion on birepresentations of heteromorphisms.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507860] "Heteromorphisms in category theory".
  \item[Math.SE 507898] "Adjunctions via heteromorphism birepresentations".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Motivation.} Explain heteromorphisms (Math.SE 507860).
  \item \textbf{Birepresentations.} Describe how adjunctions arise (MO 470788).
  \item \textbf{Examples.} Include set-to-group insertions and other heteromaps (MO 470750, Math.SE 507898).
  \item \textbf{PlanetMath links.} Connect to adjunction and natural transformation articles.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for full exposition.
  \item Pull MO embeddings (470750, 470788) and Math.SE embeddings (507860, 507898).
  \item Draft the PlanetMath entry highlighting the heteromorphic adjunction perspective.
\end{itemize}
