% PlanetMath proposal draft for arXiv:0704.1378
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Triangulated categories without models}
\subsection*{Source}
\begin{itemize}
  \item arXiv:0704.1378, "Triangulated categories without models" (2007-04-11)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Muro, Schwede, and Strickland exhibit triangulated categories that are neither stable categories of Frobenius categories nor full triangulated subcategories of homotopy categories of stable model categories. Moreover, these categories admit no nontrivial exact functors to/from algebraic or topological triangulated categories.
\begin{enumerate}
  \item constructs triangulated categories lacking algebraic/topological models;
  \item proves absence of exact functors connecting them to algebraic/topological examples;
  \item analyzes implications for triangulated classification.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470560] Question on triangulated categories without models.
  \item[MO 470592] Discussion on model-independent triangulated phenomena.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507680] "Examples of non-algebraic triangulated categories".
  \item[Math.SE 507718] "Exact functors between triangulated worlds".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Outline algebraic/topological triangulated categories (Math.SE 507680).
  \item \textbf{Counterexamples.} Describe the constructed categories (MO 470560).
  \item \textbf{No exact functors.} Explain obstructions (MO 470592, Math.SE 507718).
  \item \textbf{Implications.} Discuss consequences for triangulated classification.
  \item \textbf{PlanetMath links.} Connect to model category theory and triangulated frameworks.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for construction details.
  \item Pull MO embeddings (470560, 470592) and Math.SE embeddings (507680, 507718).
  \item Draft the PlanetMath entry summarizing these model-free triangulated categories.
\end{itemize}
