% PlanetMath proposal draft for arXiv:0704.0502
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Generic representations in Fquad}
\subsection*{Source}
\begin{itemize}
  \item arXiv:0704.0502, "Generic representations of orthogonal groups: projective functors in the category Fquad" (2007-04-04)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Vespa refines the study of the functor category Fquad (finite $\mathbb{F}_2$-vector spaces with nondegenerate quadratic forms). She defines filtrations of standard projectives, decomposes the first two into indecomposables, and applies the decompositions to describe polynomial functors of Fquad.
\begin{enumerate}
  \item recalls the structure of Fquad and standard projectives;
  \item defines filtrations refining projectives into indecomposable factors;
  \item applies decompositions to characterize polynomial functors; and
  \item analyzes generic representations of orthogonal groups.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470500] Question on quadratic functor categories like Fquad.
  \item[MO 470532] Discussion on indecomposable projectives in Fquad.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507610] "Polynomial functors in Fquad".
  \item[Math.SE 507646] "Generic representations of orthogonal groups".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Fquad background.} Summarize objects/morphisms (Math.SE 507610).
  \item \textbf{Standard projectives.} Describe filtrations and indecomposables (MO 470532).
  \item \textbf{Polynomial functors.} Present characterization results (Math.SE 507646).
  \item \textbf{Applications.} Connect to generic orthogonal representations.
  \item \textbf{PlanetMath links.} Tie to functor categories and quadratic forms.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for detailed filtrations.
  \item Fetch MO embeddings (470500, 470532) and Math.SE embeddings (507610, 507646).
  \item Draft the PlanetMath entry focusing on projective decompositions and polynomial functors.
\end{itemize}
