% PlanetMath proposal draft for arXiv:0704.2106
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Associated graded (co)algebras in braided categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:0704.2106, "Associated Graded Algebras and Coalgebras" (2007-04-17)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Ardizzoni and Menini investigate associated graded coalgebras/algebras of bialgebras with respect to sub- or quotient bialgebras, characterizing those that are type-one bialgebras in abelian braided monoidal categories.
\begin{enumerate}
  \item defines associated graded constructions relative to sub/quotient bialgebras;
  \item studies when the associated graded is type-one in braided categories;
  \item provides characterization results and examples.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470690] Question on associated graded bialgebras in braided categories.
  \item[MO 470722] Thread on type-one bialgebras.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507800] "Subbialgebras, quotients, and associated gradeds".
  \item[Math.SE 507836] "Type-one bialgebras".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Braided context.} Review type-one bialgebras (Math.SE 507836).
  \item \textbf{Associated graded constructions.} Define and analyze (MO 470690).
  \item \textbf{Characterization.} Present criteria (MO 470722).
  \item \textbf{PlanetMath links.} Connect to Hopf algebra entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for proofs.
  \item Pull MO embeddings (470690, 470722) and Math.SE embeddings (507800, 507836).
  \item Draft the PlanetMath entry describing associated graded bialgebras.
\end{itemize}
