% PlanetMath proposal draft for arXiv:1702.02602
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Lax orthogonal factorisations in ordered settings}
\subsection*{Source}
\begin{itemize}
  \item arXiv:1702.02602, "Lax orthogonal factorisations in ordered structures" (2017-02-08)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Clementino and López Franco study lax orthogonal factorisation systems on order-enriched categories, define KZ-reflective ones (mirroring reflective orthogonal systems), and use simple monads to construct lax orthogonal factorisations—e.g., on $T_0$ spaces related to continuous lattices.
\begin{enumerate}
  \item develops lax orthogonal factorisation systems in Ord-enriched categories;
  \item introduces KZ-reflective lax orthogonal systems and characterizes them;
  \item uses simple monads to construct such factorisations; and
  \item applies to $T_0$ spaces and continuous lattices.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470220] Question on lax orthogonal factorisations beyond Set.
  \item[MO 470248] Discussion on KZ-reflective structures.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507300] "Order-enriched factorisation systems".
  \item[Math.SE 507332] "Simple monads and lax factorisations".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Review orthogonal factorisation systems (Math.SE 507300).
  \item \textbf{Lax orthogonality.} Define in Ord-enriched context (MO 470220).
  \item \textbf{KZ-reflective systems.} Characterize and compare (MO 470248).
  \item \textbf{Applications.} Describe constructions via simple monads and $T_0$ examples.
  \item \textbf{PlanetMath links.} Connect to continuous lattices and enriched categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for definitions/proofs.
  \item Fetch MO embeddings (470220, 470248) and Math.SE embeddings (507300, 507332).
  \item Draft the PlanetMath entry situating lax orthogonal factorisations in enrichment theory.
\end{itemize}
