% PlanetMath proposal draft for arXiv:2602.11120
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Monoidal 2-categories from foam evaluation}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.11120, "Monoidal 2-categories from foam evaluation" (2026-02-11)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Goertz, Marino, and Wedrich develop a foam-evaluation framework that yields locally linear semistrict monoidal 2-categories encompassing gl$(N)$-foams and Bar-Natan cobordisms. These 2-categories carry duals for objects, adjoints for 1-morphisms, and a canonical spatial duality encoding pivotal and spherical features relevant to link homology theories.
\begin{enumerate}
  \item Sets up the foam evaluation data and associated semistrict monoidal 2-categories.
  \item Works through gl$(N)$-foam and decorated cobordism examples.
  \item Establishes duals, adjoints, and spatial duality structures.
  \item Explains implications for link homology models derived from these 2-categories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479298] Foam evaluation formulas leading to monoidal 2-categories.
  \item[MO 479324] Spatial duality in semistrict 2-categories arising from link homology.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 508785] "gl$(N)$ foams as monoidal 2-categories" -- example calculations.
  \item[Math.SE 508819] "Bar-Natan cobordisms and spatial duality" -- computational notes.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Framework.} Introduce foam evaluations and semistrict monoidal 2-categories (MO 479298).
  \item \textbf{Examples.} Detail gl$(N)$ and Bar-Natan cases, referencing Math.SE 508785/508819.
  \item \textbf{Dualities.} Explain duals, adjoints, and spatial duality (MO 479324).
  \item \textbf{Link homology.} Connect the constructions to Khovanov-style theories.
  \item \textbf{Future directions.} Note other foam inputs that fit the framework.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Retrieve the arXiv source for explicit foam evaluation formulas.
  \item Embed MO 479298/479324 and Math.SE 508785/508819 discussions.
  \item Draft PlanetMath entry emphasising the semistrict monoidal 2-category features relevant to link homology.
\end{itemize}
