% PlanetMath proposal draft for arXiv:2602.15583
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Bruns--Lakser completions of smooth sublocales}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.15583, "The lattice of smooth sublocales as a Bruns-Lakser completion" (2026-02-17)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Arrieta and Suarez show that the Booleanization $\mathsf{S}_b(L)$ of smooth sublocales of a frame $L$ is the Bruns--Lakser completion of locally closed sublocales. Consequences include precise lifting criteria for frame morphisms and a description of smooth sublocale lattices via meet-semilattices.
\begin{enumerate}
  \item identifies the meet-semilattice of locally closed sublocales $\mathfrak{c}(a)\cap \mathfrak{o}(b)$;
  \item proves $\mathsf{S}_b(L)$ is the Bruns--Lakser completion of that semilattice;
  \item characterizes frame morphisms that lift to $\mathsf{S}_b$; and
  \item discusses applications to Booleanizations and locale morphisms.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467940] Question on lifting frame morphisms to Booleanized sublocale lattices.
  \item[MO 468022] Thread on Bruns--Lakser completions for locale-inspired semilattices.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506201] "Examples of smooth sublocales inside a frame".
  \item[Math.SE 506455] "How do Bruns--Lakser completions relate to Booleanizations?"
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Smooth sublocales.} Define $\mathsf{S}(L)$ and $\mathsf{S}_b(L)$, summarizing Math.SE 506201.
  \item \textbf{Locally closed semilattice.} Describe the semilattice of $\mathfrak{c}(a)\cap\mathfrak{o}(b)$ and cite MO 468022.
  \item \textbf{Bruns--Lakser completion.} State the main isomorphism and relate it to Math.SE 506455.
  \item \textbf{Lifting morphisms.} Present the characterization of frame maps that extend to $\mathsf{S}_b$, referencing MO 467940.
  \item \textbf{Examples/applications.} Discuss Booleanizations, locale morphisms, and PlanetMath links.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Extract detailed statements from the arXiv source.
  \item Pull MO embeddings (467940, 468022) and Math.SE embeddings (506201, 506455).
  \item Draft the PlanetMath entry with diagrams illustrating the completion.
\end{itemize}
