% PlanetMath proposal draft for arXiv:2602.09241
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Algebraic exponentiation and actions for V-groups}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09241, "Algebraic exponentiation and action representability for V-groups" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Clementino and Montoli show that V-groups (groups internal to a cartesian quantale V) are locally algebraically cartesian closed with respect to points underlying the product V-category structure; the corresponding actions are representable.
\begin{enumerate}
  \item interprets points as (V-Cat)-enriched functors from one-object V-categories;
  \item proves local algebraic cartesian closedness for V-groups;
  \item describes action representability for the relevant points; and
  \item specializes to preordered groups.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468760] Question on algebraic exponentiation for V-groups.
  \item[MO 468802] Thread on representable actions in enriched settings.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505448] "V-groups and cartesian quantales".
  \item[Math.SE 505476] "Action representability for enriched categories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{V-groups recap.} Define groups internal to a cartesian quantale (Math.SE 505448).
  \item \textbf{Points and functors.} Interpret points as enriched functors (MO 468760).
  \item \textbf{Local ACC.} Present the algebraic exponentiation result.
  \item \textbf{Action representability.} Describe the representable actions (MO 468802, Math.SE 505476).
  \item \textbf{Examples.} Include preordered groups and other V choices.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Ingest the arXiv source for the categorical proofs.
  \item Pull MO embeddings (468760, 468802) and Math.SE embeddings (505448, 505476).
  \item Draft the PlanetMath entry linking to enriched-category resources.
\end{itemize}
