% PlanetMath proposal draft for arXiv:2602.14332
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{2-dimensional Lawvere theories, commutativity, and Fox-type theorems}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.14332, ``2-dimensional Lawvere theories: commutativity and lax phenomena'' (February 2026)
  \item MathOverflow threads on Lawvere theories, lax monoidal functors, and symmetric monoidal phenomena (IDs 248288, 130616, 400)
  \item Math.StackExchange questions on Lawvere theory smallness and monoidal functors (IDs 474192, 192424)
\end{itemize}
\subsection*{Synopsis}
Perutka develops a notion of $w$-commutativity (for $w=\{$strict, pseudo, lax, colax$\}$) for Lawvere $2$-theories and $\mF$-sketches, showing that syntactic and semantic criteria coincide. When a Lawvere $2$-theory is $w$-commutative, the category of $\T$-models and lax homomorphisms admits a closed $2$-multicategory structure, enabling a Fox-type idempotent comonad on internal algebras. The paper also sketches the $(\infty,2)$ analogue and discusses applications to symmetric monoidal categories, multicategories, and generalized Fox theorems.
\begin{enumerate}
  \item Defines the semi-strict Gray tensor product $\otimes_{s,w}$ and $w$-commutativity data $(u,\mu)$ on a Lawvere $2$-theory or enhanced sketch.
  \item Proves the ``syntax–semantics'' bijection between $w$-commutativity, coherent fillers in $\T$, and sections $\Mod_w(\T,\C)\to\Mod_w(\T,\Mod_w(\T,\C))$.
  \item Applies the structure to the functor $\IntAlg$ of internal algebras, showing it lifts to an endofunctor on $\Mod_{\lax}(\T,\Cat)$ with comonadic properties generalizing Fox’s theorem for $\CMon$.
  \item Demonstrates ``miracle associativity''—unital data automatically enforce associativity up to isomorphism.
  \item Outlines the $(\infty,2)$-categorical extension and its connections to multicategories/$\infty$-operads.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 248288] Studies partial algebras for Lawvere theories, situating the syntactic approach to $2$-dimensional commutativity.
  \item[MO 130616] Explains lax monoidal functors as monoids under Day convolution, aligning with the paper's treatment of lax homomorphisms in higher Lawvere theories.
  \item[MO 400] ``A gentleman never chooses a basis''—a classic discussion on symmetric monoidal niceties that motivates Fox-type idempotent comonads.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 474192] Addresses local smallness of Lawvere theories, providing context on categorical size issues encountered in the paper.
  \item[Math.SE 192424] Analyzes morphisms in symmetric monoidal closed categories, relevant for the examples of lax/pseudo homomorphisms.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Definition of $w$-commutativity for Lawvere $2$-theories via semi-strict Gray tensor products.
  \item Syntax–semantics comparison and miracle associativity.
  \item Internal algebra functors, Fox’s theorem generalizations, and closed $2$-multicategory structures.
  \item Notes on $(\infty,2)$ analogues and multicategory/operad interpretations.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Prepare an entry detailing $w$-commutativity and the equivalence between syntactic fillers and semantic sections.
  \item Summarize the construction of the comonad $\underline{\IntAlg}$ and the Fox-type results for symmetric monoidal categories.
  \item Cross-reference PlanetMath pages on Lawvere theories, Gray tensor products, and monoidal bicategories.
  \item Provide comments on higher-categorical generalizations and multicategory perspectives.
\end{itemize}
