% PlanetMath proposal draft for arXiv:2602.09780
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Centres of pomonoid-graded strong monads}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09780, "On the Centre of Strong Graded Monads" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Breuvart, Long, and Zamdzhiev define the centre of pomonoid-graded strong monads, generalizing prior work on centres of strong monads. Whenever it exists, the centre yields a commutative submonad, and the authors relate this to duoidally-graded strong monads.
\begin{enumerate}
  \item defines centres for pomonoid-graded strong monads;
  \item shows the centre forms a graded commutative submonad when it exists;
  \item explores conditions for existence; and
  \item connects the notion to duoidally-graded strong monads.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468840] Question on centres of graded strong monads.
  \item[MO 468872] Thread on duoidal gradings and monad centres.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505520] "Pomonoid gradings of monads".
  \item[Math.SE 505568] "Commutative submonads from centres".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Strong monads background.} Recap centres in ungraded settings (Math.SE 505568).
  \item \textbf{Pomonoid gradings.} Describe the graded structure (Math.SE 505520).
  \item \textbf{Centre definition.} Present the construction and cite MO 468840.
  \item \textbf{Duoidal connection.} Explain the relation to duoidally-graded monads (MO 468872).
  \item \textbf{Applications.} Mention potential uses in semantics and higher algebra.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for detailed statements.
  \item Pull MO embeddings (468840, 468872) and Math.SE embeddings (505520, 505568).
  \item Draft the PlanetMath entry with examples of graded monads and their centres.
\end{itemize}
