% PlanetMath proposal draft for arXiv:2602.19578
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Ultrafilter operads and condensed symmetry}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19578, "Ultrafilter operads and condensed symmetry" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Ultrafilter operads combine condensed logoi with ultrafilter completions to encode profinite symmetries. This entry differentiates itself from PR \#12 (span logoi) and PR \#14 (condensed limits) by concentrating on \emph{ultrafilter completions and profinite fixed points}; it cross-links to the other two so readers see which statements are reused. The authors:
\begin{enumerate}
  \item construct operads inside span logoi of condensed sets endowed with ultrafilters;
  \item describe how condensed Galois actions act on such operads via ultrafilter fixed points;
  \item classify the resulting algebras using ultrafilter correspondences; and
  \item apply the recipe to condensed tori and $p$-adic fields.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467479] Number-theory discussion on ultrafilters and Galois fixed points; provides explicit examples for Section 3.
  \item[MO 467887] Geometric group theory thread on profinite completions that motivates the symmetry constraints.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506448] "Ultrafilters inside condensed mathematics".
  \item[Math.SE 508200] "Operads controlling profinite symmetry".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Ultrafilter + condensed background.} Review condensed logoi, ultrafilter completions, and summarize Math.SE 506448 to set notation.
  \item \textbf{Definition of ultrafilter operads.} Build operads internal to span logoi with ultrafilter structure, list compatibility axioms, and reference the general span-logoi entry for shared preliminaries.
  \item \textbf{Galois action and fixed points.} Explain how profinite Galois groups act, cite MO 467479/467887, and describe the fixed-point classification theorem.
  \item \textbf{Examples.} Work through condensed tori and $p$-adic fields, highlighting what data is new relative to the condensed-limits entry.
  \item \textbf{Applications + links.} Summarize consequences for profinite symmetry, point to Math.SE 508200, and document how this entry links back to PR \#12/\#14 without overlap.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Sync the arXiv source and extract the ultrafilter completion lemmas.
  \item Pull MO embeddings (467479, 467887) and Math.SE embeddings (506448, 508200) to cite the profinite examples.
  \item Cross-link with the span-logoi + condensed-limits drafts so background text isn't duplicated, then draft the new entry per outline.
\end{itemize}
