% PlanetMath proposal draft for arXiv:2602.08851
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Koszul duality for algebras over infinity-operads}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.08851, "Koszul duality for algebras over infinity-operads" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Hoffbeck and Moerdijk extend their linear $\infty$-operad/cooperad Koszul duality to the associated algebras and coalgebras. The comparison leverages presheaves and copresheaves on a category of trees, lifting duality from combinatorial level to algebraic level. They define homology theories for $\infty$-operad algebras via tree homology and recover classical Koszul duality when the operad is discrete.
\begin{enumerate}
  \item Introduces linear $\infty$-operad algebras/coalgebras and their morphisms.
  \item Extends the Koszul duality equivalence using presheaf/copresheaf duality on trees.
  \item Defines homology of algebras over $\infty$-operads via tree homology and relates it to duality.
  \item Specialises to classical operads and compares proofs with existing Koszul frameworks.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 478921] How presheaf/copresheaf duality on trees lifts to $\infty$-operad algebras.
  \item[MO 478962] Clarifying homology theories for algebras over linear $\infty$-operads.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 508445] "From classical Koszul duality to $\infty$-operads" -- examples bridging discrete/linear cases.
  \item[Math.SE 508472] "Tree-based models for $\infty$-cooperads" -- computational tips.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Revisit Koszul duality for classical operads and the linear $\infty$ extensions (Math.SE 508445).
  \item \textbf{Algebras/coalgebras.} Define linear $\infty$-operad algebras using tree-indexed presheaves.
  \item \textbf{Duality theorem.} Present the equivalence built from presheaf/copresheaf duality (MO 478921).
  \item \textbf{Homology.} Describe the tree homology definition and comparison results (MO 478962, Math.SE 508472).
  \item \textbf{Examples.} Work through classical operads and explain how the general proof simplifies there.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for detailed duality constructions and homology definition.
  \item Gather MO 478921/478962 and Math.SE 508445/508472 embeddings for reference.
  \item Emphasise the role of tree categories and recovered classical cases in the PlanetMath entry.
\end{itemize}
