% PlanetMath proposal draft for arXiv:2602.15726
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Stability for minimal projective resolutions}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.15726, "Minimal Projective Resolutions, Möbius Inversion, and Bottleneck Stability" (2026-02-17)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Asashiba and Patel define the Galois transport distance for $\mathbf{P}$-modules (finite metric posets) and a bottleneck distance on their minimal projective resolutions, proving the latter is bounded by the former. Applications include persistence modules, Möbius inversion, and signed persistence diagrams.
\begin{enumerate}
  \item introduces the Galois transport distance generalizing interleavings;
  \item defines a resolution-level bottleneck distance via matches of indecomposable projectives;
  \item proves stability between the two distances; and
  \item applies the theory to persistence diagrams and Möbius homology.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468428] Discussion on metrics for minimal projective resolutions.
  \item[MO 468455] Question about Möbius inversion viewed through persistence.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507712] "Interleavings vs. Galois transport distance".
  \item[Math.SE 507770] "Stability of signed persistence diagrams".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Modules over metric posets.} Review $\mathbf{P}$-modules and persistence (Math.SE 507712).
  \item \textbf{Galois transport distance.} Define the apex poset construction and distance formula.
  \item \textbf{Resolution bottleneck distance.} Describe the matching of indecomposable projectives and contractible cones.
  \item \textbf{Stability theorem.} Present the main inequality and relate to MO 468428/468455.
  \item \textbf{Applications.} Cover persistence diagrams, Möbius homology, and PlanetMath links.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source and capture the stability argument.
  \item Fetch MO embeddings (468428, 468455) and Math.SE embeddings (507712, 507770).
  \item Draft the PlanetMath entry with illustrative diagrams of resolutions.
\end{itemize}
