% PlanetMath proposal draft for arXiv:2602.03149
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Homodular pseudofunctors and module bicategories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.03149, "Homodular pseudofunctors and bicategories of modules" (2026-02-03)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Street clarifies the universal property of the Bénabou bicategory of distributors (modules) by identifying it as a completion of $\mathcal{W}$-enriched categories with freely adjoined lax colimits. The paper frames homological functors (homodular pseudofunctors) as objective versions of constructions introduced by Joyal.
\begin{enumerate}
  \item recalls the bicategory $\mathcal{W}\text{-}\mathrm{Mod}$ and its collage completion property;
  \item states the universal property of adjoining modules to $\mathcal{W}\text{-}\mathrm{Cat}$;
  \item interprets homodular pseudofunctors as homological functors; and
  \item discusses examples such as Morita contexts and objective homology theories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467455] Question on the universal property of bicategories of distributors.
  \item[MO 467530] Thread relating Joyal's homological functors to modules.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 503230] "Collages and lax colimits for enriched categories".
  \item[Math.SE 503284] "Objective homology and homodular pseudofunctors".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Distributors/modules.} Define $\mathcal{W}\text{-}\mathrm{Mod}$ and recall collage completions (Math.SE 503230).
  \item \textbf{Universal property.} State the characterization and cite MO 467455.
  \item \textbf{Homodular pseudofunctors.} Explain the link to Joyal's homological functors (MO 467530, Math.SE 503284).
  \item \textbf{Examples.} Present Morita contexts and objective homology cases.
  \item \textbf{PlanetMath links.} Connect to distributor, profunctor, and enriched-category entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Sync the arXiv source and capture the universal property proof.
  \item Pull MO embeddings (467455, 467530) and Math.SE embeddings (503230, 503284).
  \item Draft the PlanetMath entry with emphasis on collage completions.
\end{itemize}
