% PlanetMath proposal draft for arXiv:2602.14015
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{On the zero-classes of monoid semi-congruences}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.14015, "On the zero-classes of monoid semi-congruences" (2026-02-15)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Hoefnagel, Martins-Ferreira, and Sobral characterise zero-classes (clots) of monoid semi-congruences via new syntactic relations generalising Eilenberg's equivalence and Pin's preorder. They introduce hierarchical conditions on submonoids guaranteeing compatibility, transitivity, and symmetry, covering normal submonoids and positive cones as special cases.
\begin{enumerate}
  \item Defines syntactic relations capturing zero-classes/clots.
  \item Establishes compatibility criteria and hierarchical strengthening.
  \item Applies to normal submonoids and positive cones with examples.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 480668] Clots and syntactic relations beyond congruences.
  \item[MO 480693] Hierarchies of submonoid conditions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 510301] "Syntactic relations for semi-congruences".
  \item[Math.SE 510328] "Examples of clots in monoids".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Semi-congruences.} Review definitions and classical examples (Math.SE 510328).
  \item \textbf{Syntactic relation.} Present the new relation and compatibility tests (MO 480668, Math.SE 510301).
  \item \textbf{Hierarchy.} Explain strengthening conditions (MO 480693).
  \item \textbf{Applications.} Highlight normal submonoids and positive cones.
  \item \textbf{Outlook.} Mention open problems in syntactic characterisations.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv source for definitions/examples.
  \item Link MO 480668/480693 and Math.SE 510301/510328.
  \item Emphasise hierarchical compatibility in the PlanetMath entry.
\end{itemize}
