% PlanetMath proposal draft for arXiv:2602.08954
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Equivalent definitions of fusion categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.08954, "Equivalent definitions of fusion category arising from separability" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Zuo studies semisimple multiring categories with left duals, proving the unit is simple iff tensor functors by any non-zero algebra are separable/faithful/Maschke/dual Maschke/conservative, yielding a suite of equivalent definitions of fusion category. Applications include weak Hopf algebras and transfer of simplicity.
\begin{enumerate}
  \item establishes equivalence between unit simplicity and separability of tensor functors;
  \item shows faithfulness, Maschke-type conditions are equivalent;
  \item applies to weak Hopf algebras for connectivity; and
  \item transfers simplicity between units, module categories, Grothendieck rings.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469960] Question on separable tensor functors implying unit simplicity.
  \item[MO 469990] Discussion on Maschke-type conditions in fusion categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507010] "Equivalent characterizations of fusion categories".
  \item[Math.SE 507042] "Weak Hopf algebras and separability".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Multiring categories.} Review context (Math.SE 507010).
  \item \textbf{Equivalences.} State separability/faithfulness vs. unit simplicity (MO 469960, MO 469990).
  \item \textbf{Applications.} Discuss weak Hopf algebras (Math.SE 507042).
  \item \textbf{Transfer results.} Mention module categories and Grothendieck rings.
  \item \textbf{PlanetMath links.} Connect to fusion categories and tensor functors.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for proofs.
  \item Fetch MO embeddings (469960, 469990) and Math.SE embeddings (507010, 507042).
  \item Draft the PlanetMath entry enumerating the equivalent definitions.
\end{itemize}
