% PlanetMath proposal draft for arXiv:2602.11943
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{The Cylinder Simplicial DG Ring}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.11943, "The Cylinder Simplicial DG Ring" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Yekutieli constructs $q$-th cylinder DG rings $Cyl_q(B)$ generalising Keller's path object ($q=1$) and organises them into a simplicial DG ring $Cyl(B)$. For a semi-free DG ring $A$, the mapping space $\mathrm{Hom}(A,Cyl(B))$ forms a Kan complex, with horns represented by explicit DG rings $N(Y,B)$. The construction promises extensions to DG categories, offering intrinsic Kan models for simplicial aspects of DG categories.
\begin{enumerate}
  \item Defines $Cyl_q(B)$ and assembles them into a simplicial DG ring.
  \item Shows $\mathrm{Hom}(A,Cyl(B))$ is Kan when $A$ is semi-free, using horn-representing DG rings $N(Y,B)$.
  \item Discusses expected extensions to DG categories for computing simplicial structures.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479672] Kan conditions for mapping spaces of DG rings.
  \item[MO 479701] Extending cylinder constructions to DG categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509156] "Understanding $Cyl_q$ objects" -- explicit small examples.
  \item[Math.SE 509182] "Horns in DG mapping spaces" -- verification of $N(Y,B)$ behavior.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Cylinder DG rings.} Recall Keller's path objects and define $Cyl_q(B)$ (Math.SE 509156).
  \item \textbf{Simplicial organization.} Explain how $Cyl(B)$ yields a simplicial DG ring.
  \item \textbf{Kan property.} Detail the horn representability proof (MO 479672, Math.SE 509182).
  \item \textbf{DG category extensions.} Discuss prospective generalisations (MO 479701).
  \item \textbf{Applications.} Mention computations of homotopies between DG functors.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source to capture the $Cyl_q$ definition and Kan proof.
  \item Reference MO 479672/479701 and Math.SE 509156/509182 posts in the entry.
  \item Emphasise the DG-category extension motivation for PlanetMath readers.
\end{itemize}
