% PlanetMath proposal draft for arXiv:2602.19655
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{$p$-adic span topoi and analytic geometries}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19655, "$p$-adic span topoi and analytic geometries" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
The article constructs $p$-adic analytic topoi by gluing condensed spans of Huber pairs and comparing them with dagger analytic geometry. This proposal emphasizes the analytic/gluing story, complementing the condensed-limits and ultrafilter-operads entries (which treat algebraic fixed points). Highlights:
\begin{enumerate}
  \item define $p$-adic span topoi whose objects are Huber pairs with span morphisms;
  \item compare the resulting topos with dagger analytic geometry;
  \item analyze the induced $p$-adic Galois action; and
  \item compute norms for condensed fields.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467711] $p$-adic condensed geometry thread explaining Huber pairs with span morphisms.
  \item[MO 467999] Discussion on dagger vs. condensed comparisons; provides examples for the comparison theorem.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512064] "$p$-adic condensed geometry overview".
  \item[Math.SE 513200] "How do dagger spaces interact with spans?".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Recap Huber pairs, condensed sets, and Math.SE 512064 so readers understand the analytic input.
  \item \textbf{Definition of $p$-adic span topoi.} Define the objects/morphisms, list universal properties, and distinguish this construction from the condensed-limits entry.
  \item \textbf{Dagger comparison.} Explain the theorem comparing $p$-adic span topoi with dagger analytic geometry, using MO 467999 and Math.SE 513200 as supporting cues.
  \item \textbf{Galois symmetry + examples.} Work through the condensed torus example, cite MO 467711, and describe how spans encode $p$-adic Galois action.
  \item \textbf{Applications + roadmap.} Note consequences for condensed fields, compatibility with ultrafilter-operads, and future analytic entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Sync the arXiv source and extract the dagger comparison proof steps.
  \item Pull MO embeddings (467711, 467999) and Math.SE embeddings (512064, 513200).
  \item Draft the entry following the expanded outline and cross-link to the condensed-limits + ultrafilter-operads pages to clarify scope.
\end{itemize}
