% PlanetMath proposal draft for arXiv:2602.12505
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Coalgebra measurings in cyclic, Hochschild, and matrix homologies}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.12505, ``Coalgebra measurings, cyclic theory and homologies of matrix algebras'' (February 2026)
  \item MathOverflow threads on cyclic homology, Lie algebra homology of matrices, and dihedral homology (IDs 121832, 346391, 215047)
  \item Math.StackExchange questions on Connes’ exact sequence and multiple definitions of Hochschild/cyclic homology (IDs 4720548, 3461430)
\end{itemize}
\subsection*{Synopsis}
Banerjee and Kour extend coalgebra measurings (Sweedler-style generalized morphisms) to induce compatible maps on Hochschild, cyclic, Lie, Leibniz, and dihedral homologies. They prove that measurings by cocommutative coalgebras respect the $\lambda$-decomposition, Connes operators, and product structures, and they identify how these maps interact with the primitive parts of matrix Lie/Leibniz homology. The paper culminates in an enrichment of commutative $K$-algebras by cocommutative coalgebras built from cyclic homology.
\begin{enumerate}
  \item Constructs maps $HH_\bullet^\Phi(x)$ and $HC_\bullet^\Phi(x)$ induced by a measuring $\Phi\colon C\to\Hom(A,A')$ and proves compatibility with Connes' periodicity sequence.
  \item Shows that for commutative algebras the induced maps respect the $\lambda$-decomposition, shuffle products, and make Hochschild homology a module measurement over cyclic homology.
  \item Relates these measuring-induced maps to those on Lie and Leibniz homology by identifying primitive parts of matrix algebras with cyclic/Hochschild homology.
  \item Extends the discussion to dihedral homology for involutive algebras, matching primitive Lie homology of symplectic/skew-symmetric matrices.
  \item Packages everything into an enrichment $c\widetilde{ALG}_K$ in cocommutative coalgebras via Sweedler Hom objects built from $HC'_\bullet$.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 121832] Asks about cyclic homology analogues for $E_n$-algebras—context for generalizing cyclic operations via coalgebra measurings.
  \item[MO 346391] Discusses product structures on Lie algebra homology of matrices, mirroring the compatibility results in the paper.
  \item[MO 215047] Studies Connes' SBI-sequence for dihedral homology, which the authors connect to measuring-induced maps.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 4720548] Clarifies Connes' long exact sequence, providing a reference for the SBI compatibility statements.
  \item[Math.SE 3461430] Surveys multiple definitions of Hochschild and cyclic homology, helpful for orienting encyclopedic readers before introducing coalgebra measurings.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Review of coalgebra measurings and Sweedler Hom objects.
  \item Induced maps on Hochschild and cyclic homology, including compatibility with $\lambda$-operations and Connes operators.
  \item Interaction with matrix Lie/Leibniz homology and dihedral homology.
  \item Enrichment of commutative algebras via cyclic homology and cocommutative coalgebras.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Develop a PlanetMath entry explaining measurings and how they induce homology operations.
  \item Summarize the compatibility proofs (shuffle products, module structures, SBI sequences).
  \item Provide explicit statements for the matrix algebra comparisons and cite classical isomorphisms (Feigin--Tsygan, Loday--Quillen, etc.).
  \item Reference existing entries on cyclic, Hochschild, Lie, Leibniz, and dihedral homologies to contextualize the new enrichment.
\end{itemize}
