% PlanetMath proposal draft for arXiv:2602.12239
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Tininess and right adjoints to exponentials}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.12239, "Tininess and right adjoints to exponentials" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Ruiz Hernández and Solórzano explore "amazingly tiny" objects $T$ in toposes whose exponential functor $(-)^T$ admits a right adjoint $(-)_T$. They study categorical behaviour (subobjects, quotients, retracts) of such $T$, and analyse their topological properties in precohesive toposes, testing Lawvere's intuitions from Synthetic Differential Geometry.
\begin{enumerate}
  \item Investigates categorical properties of objects with right adjoints to exponentials.
  \item Studies topological features under precohesive hypotheses.
  \item Relates findings to Lawvere's ATOM proposal for SDG.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479902] Examples of objects admitting right adjoints to exponentials.
  \item[MO 479934] Precohesive conditions for tininess in SDG.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509402] "Computing $(-)_T$ in elementary toposes" -- sample calculations.
  \item[Math.SE 509436] "Tininess tests in precohesive settings" -- verifying hypotheses.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Definitions.} Introduce objects where $(-)^T$ admits right adjoints (MO 479902).
  \item \textbf{Categorical behaviour.} Describe subobject/quotient properties (Math.SE 509402).
  \item \textbf{Topological aspects.} Summarise precohesive analyses (MO 479934, Math.SE 509436).
  \item \textbf{Connection to SDG.} Relate to Lawvere's ATOM viewpoint.
  \item \textbf{Examples.} Provide tiny/non-tiny examples inside various toposes.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv sections on categorical/topological behaviour.
  \item Reference MO 479902/479934 and Math.SE 509402/509436.
  \item Highlight ties to SDG foundations in the PlanetMath write-up.
\end{itemize}
