% PlanetMath proposal draft for arXiv:2602.10000
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Virtual double categories of split two-sided 2-fibrations}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.10000, "Virtual double categories of split two-sided 2-fibrations" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Koudenburg generalizes Street's split two-sided fibrations to sesquicategories, builds a virtual double category of such fibrations, and obtains Yoneda-type morphisms yielding a two-sided Grothendieck correspondence for locally discrete split two-sided 2-fibrations.
\begin{enumerate}
  \item defines internal split two-sided fibrations in a sesquicategory;
  \item constructs the virtual double category of these fibrations;
  \item studies the subcategory of locally discrete split two-sided 2-fibrations and their Yoneda morphisms; and
  \item derives a two-sided Grothendieck correspondence.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468982] Question on two-sided fibrations in sesquicategories.
  \item[MO 469015] Discussion on Yoneda structures for double categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505780] "Virtual double categories and fibrations".
  \item[Math.SE 505812] "Two-sided Grothendieck correspondences".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Split two-sided fibrations.} Review Street's notion and generalization (MO 468982).
  \item \textbf{Virtual double category.} Describe the construction (Math.SE 505780).
  \item \textbf{Locally discrete case.} Highlight Yoneda morphisms (MO 469015, Math.SE 505812).
  \item \textbf{Grothendieck correspondence.} State the two-sided result.
  \item \textbf{Applications.} Mention op-2-fibrations and functoriality improvements.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for formal proofs.
  \item Pull MO embeddings (468982, 469015) and Math.SE embeddings (505780, 505812).
  \item Draft the PlanetMath entry linking to double category resources.
\end{itemize}
