% PlanetMath proposal draft for arXiv:2602.14886
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Conservative geometric functors via purity}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.14886, "Conservative geometric functors via purity" (2026-02-16)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Castellana and Gómez use purity in compactly generated triangulated categories to detect joint conservativity of families of geometric functors. They introduce "pure descendability" and apply it to sequential limits of ring spectra, giving criteria for when pullback functors remain conservative.
\begin{enumerate}
  \item Defines pure descendability and relates it to purity notions in triangulated categories.
  \item Gives a criterion for joint conservativity of geometric functors via purity.
  \item Applies the criterion to sequential limit constructions for ring spectra.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 480432] Purity-based tests for conservativity.
  \item[MO 480465] Pure descendability and sequential limits of spectra.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 510015] "Purity in compactly generated triangulated categories" -- user computations.
  \item[Math.SE 510042] "Conservative functor criteria" -- concrete examples.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Purity background.} Review purity and compact generation (Math.SE 510015).
  \item \textbf{Pure descendability.} Present the new notion and relation to conservativity (MO 480432).
  \item \textbf{Applications.} Explain sequential limit examples (MO 480465, Math.SE 510042).
  \item \textbf{Implications.} Discuss monitoring descent in chromatic homotopy.
  \item \textbf{Further directions.} Note open problems on other functor families.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for proofs of the purity criterion and applications.
  \item Link MO 480432/480465 and Math.SE 510015/510042.
  \item Highlight pure descendability in the PlanetMath entry.
\end{itemize}
