% PlanetMath proposal draft for arXiv:2602.12738
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{$Λ$-sequences and unital operads}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.12738, "On the Kelly monoidal structure of $Λ$-sequences and unital operads" (2026-02-13)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Fan and Zou study Kelly's monoidal structure on $Λ$-sequences (based finite sets with based injections). They describe monoids/modules, show the forgetful functor to symmetric sequences is an isomorphism on right modules, extend lower data to a universal normal oplax monoidal structure, and identify unital operads as monoids in unital $Λ$-sequences.
\begin{enumerate}
  \item reviews Kelly's product and modules in $Λ$-sequences;
  \item proves the forgetful functor on right modules is an isomorphism;
  \item extends compatible lower data to a normal oplax monoidal structure;
  \item identifies unital operads as monoids in unital $Λ$-sequences; and
  \item establishes a closed monoidal localization theorem.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469310] Question on $Λ$-sequence modules vs. symmetric sequence modules.
  \item[MO 469342] Thread on normal oplax monoidal structures extending Kelly products.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506320] "Unital operads via $Λ$-sequences".
  \item[Math.SE 506352] "Closed monoidal localizations for $Λ$-sequences".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{$Λ$-sequences.} Recap the category and Kelly product (Math.SE 506320).
  \item \textbf{Modules.} Explain the forgetful functor result (MO 469310).
  \item \textbf{Oplax structures.} Present the extension to normal oplax monoidal structures (MO 469342).
  \item \textbf{Unital operads.} Describe identification as monoids.
  \item \textbf{Localization.} Summarize the closed monoidal localization theorem (Math.SE 506352).
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source to capture precise statements.
  \item Fetch MO embeddings (469310, 469342) and Math.SE embeddings (506320, 506352).
  \item Draft the PlanetMath entry linking to operad theory resources.
\end{itemize}
