% PlanetMath proposal draft for arXiv:2602.09674
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{A homotopical Dold--Kan correspondence for Joyal's category $\Theta$ and other test categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09674, "A homotopical Dold--Kan correspondence for Joyal's category $\Theta$ and other test categories" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Léo Hubert extends the classical Dold--Kan correspondence from simplicial abelian groups to abelian presheaves on test categories $A$ satisfying a compatibility between homology and weak equivalences. Under this hypothesis the homotopy category of abelian presheaves on $A$ matches the non-negative derived category of abelian groups, via a Quillen equivalence built from a new model structure. Joyal's $\Theta$ satisfies the compatibility, delivering a conceptual bridge between $\Theta$-spaces and chain complexes.
\begin{enumerate}
  \item Formulates the homology-vs-weak-equivalence compatibility for test categories.
  \item Constructs a model structure on abelian presheaves on $A$ and proves a Quillen equivalence to chain complexes.
  \item Interprets the equivalence as a homotopical Dold--Kan correspondence.
  \item Applies the theory to Joyal's $\Theta$ and related test categories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 478559] Criteria for test categories admitting Dold--Kan-style correspondences.
  \item[MO 478601] Discussion on model structures for abelian presheaves on $\Theta$.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 508012] "Fibrant replacements in $\Theta$-presheaves" -- practical computations.
  \item[Math.SE 508098] "Chain complexes vs. $\Theta$-spaces" -- explains the Quillen pair.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Test categories.} Recall Grothendieck test categories and compatibility condition (MO 478559).
  \item \textbf{Model structure.} Present Hubert's model structure on abelian presheaves, referencing Math.SE 508012.
  \item \textbf{Dold--Kan equivalence.} Summarize the Quillen equivalence and induced homotopy equivalence (MO 478601).
  \item \textbf{Applications to $\Theta$.} Detail the $\Theta$ case and implications for $\Theta$-spaces (Math.SE 508098).
  \item \textbf{Further test categories.} Indicate how the framework extends to other Grothendieck test categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Sync the arXiv source for theorem statements and proof sketches.
  \item Link MO 478559/478601 and Math.SE 508012/508098 discussion threads.
  \item Draft PlanetMath entry emphasising the Quillen equivalence and $\Theta$-specific consequences.
\end{itemize}
