% PlanetMath proposal draft for arXiv:2602.14424
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{The higher algebra and geometry of monoidal bicategories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.14424, "The higher algebra and geometry of monoidal bicategories" (2026-02-16)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Raffael Stenzel identifies braided, sylleptic, and symmetric monoidal bicategories as $\mathsf{E}_k$-monoids inside the cartesian monoidal $(\infty,1)$-category of bicategories, using little cubes operads to bridge 2-dimensional and $\infty$-categorical algebra.
\begin{enumerate}
  \item Models braided/sylleptic/symmetric monoidal bicategories via $\mathsf{E}_k$-operads.
  \item Utilises little cubes geometry to compare 2D algebra with $(\infty,1)$ structures.
  \item Clarifies the hierarchy and relationships among monoidal bicategory notions.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 480378] Relating monoidal bicategories to $\mathsf{E}_k$-monoids.
  \item[MO 480405] Little cubes operads mediating between 2D and $\infty$-algebra.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509968] "Examples of sylleptic bicategories" -- practical computations.
  \item[Math.SE 509996] "Operadic models for symmetric monoidal bicategories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Monoidal bicategories.} Summarise braided/sylleptic/symmetric notions (Math.SE 509968).
  \item \textbf{Operadic bridge.} Explain little cubes comparison (MO 480405).
  \item \textbf{$\mathsf{E}_k$ interpretation.} Detail the equivalence (MO 480378, Math.SE 509996).
  \item \textbf{Implications.} Discuss classification and geometric meaning.
  \item \textbf{Examples.} Provide sample bicategories fitting each level.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Download the arXiv source for precise $\mathsf{E}_k$-monoid identifications.
  \item Reference MO 480378/480405 and Math.SE 509968/509996.
  \item Emphasise operadic geometry in the PlanetMath entry.
\end{itemize}
