% PlanetMath proposal draft for arXiv:2602.11120
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Monoidal 2-categories from foam evaluations}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.11120, "Monoidal 2-categories from foam evaluation" (2026-02-11)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Goertz, Marino, and Wedrich construct locally linear semistrict monoidal 2-categories from closed foam evaluation formulas (gl(N) foams, Bar-Natan cobordisms). These 2-categories have duals, adjoints, and spatial duality structures.
\begin{enumerate}
  \item describes the data needed for foam evaluation and resulting 2-categories;
  \item constructs examples from gl(N)-foams and Bar-Natan cobordisms;
  \item analyzes duals, adjoints, and spatial duality; and
  \item relates the constructions to link homology theories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469060] Question on constructing 2-categories from foams.
  \item[MO 469101] Thread on spatial duality in link-homological 2-categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505880] "gl(N)-foam categories".
  \item[Math.SE 505918] "Bar-Natan cobordisms and link homology".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Foam evaluation data.} Summarize requirements (Math.SE 505880).
  \item \textbf{Construction.} Detail the semistrict monoidal 2-categories (MO 469060).
  \item \textbf{Duality structures.} Explain duals/adjoints/spatial duality (MO 469101).
  \item \textbf{Examples.} Cover gl(N) and Bar-Natan cases (Math.SE 505918).
  \item \textbf{Applications.} Link to general linear link homology theories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source to capture construction details.
  \item Fetch MO embeddings (469060, 469101) and Math.SE embeddings (505880, 505918).
  \item Draft the PlanetMath entry referencing link homology articles.
\end{itemize}
