% PlanetMath proposal draft for arXiv:2602.12085
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Refined half-integer conditions on RG flows}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.12085, "Refined half-integer condition on RG flows" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Kikuchi studies braided symmetry categories along renormalization group flows. For a surviving object $c$, UV/IR conformal dimensions satisfy $h_c^{\text{UV}}+h_c^{\text{IR}}\in\tfrac12\mathbb{Z}$. The paper finds necessary conditions for this half-integer sum using renormalization group defects and applies them to explicit flows.
\begin{enumerate}
  \item reviews braided symmetry categories and conformal dimensions;
  \item formulates the refined half-integer condition via RG defects;
  \item derives necessary conditions for half-integer sums; and
  \item solves example flows satisfying/refuting the condition.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470410] Question on half-integer constraints from braided categories.
  \item[MO 470438] Thread on RG defects and conformal dimensions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507480] "Superselection sectors and conformal dimensions".
  \item[Math.SE 507522] "Examples of RG flows with half-integer sums".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Summarize braided symmetries in QFT (Math.SE 507480).
  \item \textbf{Half-integer condition.} Present refined criterion (MO 470410).
  \item \textbf{RG defects.} Explain role in proofs (MO 470438).
  \item \textbf{Case studies.} List explicit flows (Math.SE 507522).
  \item \textbf{PlanetMath links.} Connect to TQFT, tensor categories, physics entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for detailed arguments.
  \item Pull MO embeddings (470410, 470438) and Math.SE embeddings (507480, 507522).
  \item Draft the PlanetMath entry illustrating the refined constraint on RG flows.
\end{itemize}
