% PlanetMath proposal draft for arXiv:2602.19364
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Cyclotomic fibrations in parametrized higher categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19364, "Cyclotomic fibrations in parametrized higher categories" (2026-02-21)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
The paper studies cyclotomic structures on parametrized $\infty$-categories arising from fibrations over $\mathbb{S}^1$. Highlights include:
\begin{enumerate}
  \item classification of cyclotomic fibrations via spans of monodromy automorphisms,
  \item interaction with topological cyclic homology, and
  \item explicit models using polynomial endofunctors.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 465855] Thread on Dirichlet series and cyclic structures, inspiring the TC story.
  \item[MO 467935] Discussion of Lie algebras/roots linking monodromy spans to representation theory.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 486220] "Parametrized $\infty$-categories and monodromy".
  \item[Math.SE 488901] "What is a cyclotomic spectrum?" for background.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Definitions (parametrized categories, cyclotomic structures).
  \item Main classification theorem and proof sketch.
  \item Relation to TC and polynomial functors.
  \item Worked example + SE cross-links.
\end{enumerate}
\subsection*{Action items}
Pull arXiv source, MO embeddings (465855, 467935), Math.SE embeddings (486220, 488901), then prepare PlanetMath EDN/TeX.
