% PlanetMath proposal draft for arXiv:2602.12363
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Parametrized equivalence relations on morphisms}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.12363, "Parametrized equivalence relation on the global class of morphisms of a category and frame-theoretic examples" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
El Idrissi defines an equivalence relation on the global class of morphisms of a category that generalizes group-action equivalence and captures examples like Bessel families via coarse invariants (pointwise norms of analysis operators). The aim is a categorical invariant theory for Bessel families and continuous frames.
\begin{enumerate}
  \item defines the parametrized equivalence relation and its axioms;
  \item shows classical group-action equivalence is a special case;
  \item treats the Bessel family example via coarse invariants; and
  \item discusses implications for categorical invariant theory.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469250] Question on equivalence relations on morphism classes.
  \item[MO 469270] Thread on Bessel families and categorical invariants.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506210] "Group-action equivalence as a categorical relation".
  \item[Math.SE 506245] "Continuous frames and coarse invariants".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Setup.} Describe the global class of morphisms and parametrized equivalence (Math.SE 506210).
  \item \textbf{Classical cases.} Recover group-action equivalence (MO 469250).
  \item \textbf{Bessel families.} Explain the coarse invariant example (MO 469270, Math.SE 506245).
  \item \textbf{Future directions.} Outline categorical invariant theory goals.
  \item \textbf{PlanetMath links.} Connect to entries on frames, invariant theory, and categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for definitions/proofs.
  \item Pull MO embeddings (469250, 469270) and Math.SE embeddings (506210, 506245).
  \item Draft the PlanetMath entry highlighting examples and conjectured applications.
\end{itemize}
