% PlanetMath proposal draft for arXiv:2602.09371
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Acyclic complexes of FP-injective modules over Ding-Chen rings}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09371, "Acyclic complexes of FP-injective modules over Ding-Chen rings" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
James Gillespie combines cotorsion pairs to construct a new abelian model structure on modules over a left coherent ring. Fibrant objects are weakly Ding injectives, characterised as cycles of acyclic complexes of FP-injective modules. Over Ding-Chen rings, these cycles coincide with modules arising from acyclic complexes of FP-injectives, yielding a description of the stable module category via Gorenstein FP-pro-injective modules. The method also lifts non-hereditary cotorsion pairs to derived categories.
\begin{enumerate}
  \item Develops a method for merging cotorsion pairs into an abelian model structure.
  \item Characterises fibrant objects via acyclic FP-injective complexes and applies to Ding-Chen rings.
  \item Introduces Gorenstein FP-pro-injective modules describing the stable module category.
  \item Lifts complete cotorsion pairs to abelian models for derived categories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479506] Weakly Ding injectives and acyclic FP-injective complexes.
  \item[MO 479534] Lifting non-hereditary cotorsion pairs to abelian models.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509005] "Stable categories via FP-injectives" -- Ding-Chen examples.
  \item[Math.SE 509042] "Cotorsion pair merging tricks" -- small case study.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Recall Ding-Chen rings, FP-injective modules, and cotorsion pairs (Math.SE 509042).
  \item \textbf{Model structure.} Outline Gillespie's construction and fibrant characterisation (MO 479506).
  \item \textbf{Stable category.} Explain the Gorenstein FP-pro-injective viewpoint (Math.SE 509005).
  \item \textbf{Lifting cotorsion pairs.} Summarise the derived-category applications (MO 479534).
  \item \textbf{Examples.} Provide explicit Ding-Chen computations.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv source detailing the model structure and Ding-Chen specialisation.
  \item Link MO 479506/479534 and Math.SE 509005/509042 references.
  \item Draft PlanetMath entry emphasising FP-injective complexes and stable module categories.
\end{itemize}
