% PlanetMath proposal draft for arXiv:2602.11971
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Hypercovers in differential geometry}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.11971, "Hypercovers in Differential Geometry" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Glass and Minichiello show that for sites of smooth manifolds with open covers (and cartesian spaces with good covers), the local and Čech projective model structures coincide. Consequently, the plus construction sheafifies presheaves in a single step on these sites.
\begin{enumerate}
  \item compares local vs. Čech projective model structures on differential sites;
  \item proves equality of the structures under geometric conditions;
  \item deduces that one plus construction suffices for sheafification; and
  \item applies to manifolds and cartesian spaces with good covers.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470340] Question on local vs. Čech model structures.
  \item[MO 470365] Thread on plus construction in differential geometry.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507420] "Čech vs. local model structures".
  \item[Math.SE 507456] "One-step sheafification via plus construction".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Sites of interest.} Describe manifolds/good covers (Math.SE 507420).
  \item \textbf{Model structures.} State equality result (MO 470340).
  \item \textbf{Plus construction.} Explain one-step sheafification (MO 470365, Math.SE 507456).
  \item \textbf{Applications.} Mention implications for homotopical geometry.
  \item \textbf{PlanetMath links.} Connect to entries on sites, stacks, and sheafification.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for proofs.
  \item Fetch MO embeddings (470340, 470365) and Math.SE embeddings (507420, 507456).
  \item Draft the PlanetMath entry summarizing the model-structure comparison.
\end{itemize}
