% PlanetMath proposal draft for arXiv:2602.19604
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Sheafified correspondences for spectral stacks}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19604, "Sheafified correspondences for spectral stacks" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Sheafified correspondences endow spans with quasicoherent sheaves and use them to encode power operations on spectral stacks. The authors:
\begin{enumerate}
  \item form a monoidal category $\mathrm{Corr}^\mathrm{shv}(\mathcal{X})$ by decorating every leg of a span with a quasicoherent sheaf;
  \item construct power operations and norm functors from these sheafified spans;
  \item compare the resulting structure with spectral Mackey functors; and
  \item work out examples for spectral Deligne--Mumford stacks.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 466615] Measure-theoretic spans illustrating how decorations behave.
  \item[MO 467167] Algebraic-geometry spans guiding the spectral stack example.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509312] "Quasicoherent sheaves on spectral stacks".
  \item[Math.SE 510448] "Mackey functors built from spans".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Spectral stack background.} Summarize Math.SE 509312, recall quasicoherent sheaves, and explain why spectral stacks need sheafified correspondences.
  \item \textbf{Sheafified correspondence category.} Define $\mathrm{Corr}^\mathrm{shv}(\mathcal{X})$, describe the monoidal convolution, and state the compatibilities for sheaf decorations.
  \item \textbf{Power operations and norms.} Build power operations/norms from sheafified spans, referencing MO 466615 for intuition about measure-theoretic decorations.
  \item \textbf{Comparison with spectral Mackey functors.} Relate the construction to spectral Mackey functors, cite Math.SE 510448, and outline the equivalence result.
  \item \textbf{Examples + data flow.} Present the spectral Deligne--Mumford stack example (MO 467167) and describe how to pipe the results into PlanetMath articles on power operations.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source and capture the precise definition of $\mathrm{Corr}^\mathrm{shv}$.
  \item Fetch MO embeddings (466615, 467167) and Math.SE embeddings (509312, 510448).
  \item Draft the PlanetMath entry with the expanded outline and link to existing spectral-stack pages.
\end{itemize}
