% PlanetMath proposal draft for arXiv:2602.13695
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Can a Lightweight Automated AI Pipeline Solve Research-Level Mathematical Problems?}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.13695, "Can a Lightweight Automated AI Pipeline Solve Research-Level Mathematical Problems?" (2026-02-14)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Meng et al. evaluate a lightweight natural-language pipeline combining modern LLMs (Gemini 3 Pro, GPT-5.2 Pro) with citation-aware verification to tackle research-grade problem sets (ICCM, First Proof). They report fully verified solutions for multiple contests and plan to release the pipeline.
\begin{enumerate}
  \item Describes the automated pipeline architecture and verification heuristics.
  \item Benchmarks on ICCM and First Proof datasets with verification outcomes.
  \item Discusses plans to open-source methodology and implications for AI-assisted research.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 480589] Discussion of AI-assisted proof verification pipelines.
  \item[MO 480615] Experiences with ICCM/First Proof datasets.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 510213] "Lightweight LLM workflows for research problems".
  \item[Math.SE 510239] "Verification metrics for AI-generated proofs".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Pipeline design.} Summarise components and verification (MO 480589).
  \item \textbf{Datasets.} Describe ICCM and First Proof benchmarks (Math.SE 510213).
  \item \textbf{Results.} Present solved problems and verification stats (MO 480615, Math.SE 510239).
  \item \textbf{Implications.} Discuss AI-for-math workflows for PlanetMath editors.
  \item \textbf{Future work.} Note open-sourcing and reproducibility plans.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for pipeline description and result tables.
  \item Link MO 480589/480615 and Math.SE 510213/510239.
  \item Highlight best practices for AI-assisted proof drafting on PlanetMath.
\end{itemize}
