% PlanetMath proposal draft for arXiv:2602.09974
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Profinite cosheaves valued in pro-regular categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09974, "Profinite Cosheaves Valued in Pro-regular Categories" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Jiacheng Tang proves that profinite cosheaves valued in a pro-regular category satisfying mild axioms inherit pro-regularity. The result extends Wilkes's cosheaf-bundle equivalence from profinite modules to profinite groups by showing that cosheaf categories preserve pro-regular structure.
\begin{enumerate}
  \item Defines profinite cosheaves with values in a target pro-regular category.
  \item Shows the cosheaf category is pro-regular under mild assumptions.
  \item Applies the theorem to extend Wilkes's equivalence from modules to groups.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479582] Clarifying pro-regular categories and cosheaf constructions.
  \item[MO 479618] Applications of cosheaf-bundle equivalence beyond modules.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509089] "Profinite cosheaves and pro-regularity" -- verifying hypotheses.
  \item[Math.SE 509111] "Wilkes equivalence for groups" -- concrete computations.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Preliminaries.} Review pro-regular categories and profinite cosheaves (MO 479582).
  \item \textbf{Main theorem.} Present Tang's pro-regularity result (Math.SE 509089).
  \item \textbf{Applications.} Describe the extension of Wilkes's equivalence (MO 479618, Math.SE 509111).
  \item \textbf{Examples.} Provide sample target categories satisfying the hypotheses.
  \item \textbf{Future directions.} Outline possible extensions to higher group stacks.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Download the arXiv source for the theorem and application details.
  \item Link MO 479582/479618 and Math.SE 509089/509111 posts.
  \item Emphasise the cosheaf-bundle equivalence upgrade in the PlanetMath entry.
\end{itemize}
