% PlanetMath proposal draft for arXiv:2602.13695
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Lightweight AI pipelines for research-level math}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.13695, "Can a Lightweight Automated AI Pipeline Solve Research-Level Mathematical Problems?" (2026-02-14)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Meng, Zhao, Zhang, Guan, and He evaluate lightweight natural-language AI pipelines (Gemini 3 Pro, GPT-5.2 Pro) on research-grade problem sets (ICCM, First Proof). Their citation-aware pipeline generates proofs for all problems tested, several of which have been verified and submitted.
\begin{enumerate}
  \item describes the citation-based automated pipeline and verification step;
  \item reports on ICCM and First Proof datasets and success rates;
  \item discusses proof verification and submission procedures; and
  \item outlines plans to open-source the methodology.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469580] Thread on AI pipelines for research mathematics.
  \item[MO 469612] Question on citation-based verification strategies.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506620] "Evaluating AI-generated proofs".
  \item[Math.SE 506648] "Datasets for automated theorem proving".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Pipeline overview.} Summarize architecture and models (MO 469580).
  \item \textbf{Datasets/results.} Report ICCM + First Proof outcomes (Math.SE 506648).
  \item \textbf{Verification.} Detail citation-based checks (MO 469612, Math.SE 506620).
  \item \textbf{Implications.} Discuss research workflows and future releases.
  \item \textbf{PlanetMath links.} Connect to automated reasoning and computability entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for pipeline specifics.
  \item Fetch MO embeddings (469580, 469612) and Math.SE embeddings (506620, 506648).
  \item Draft the PlanetMath entry as a survey of current AI-for-math pipelines.
\end{itemize}
