% PlanetMath proposal draft for arXiv:2602.08851
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Koszul duality for $\infty$-operad algebras}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.08851, "Koszul duality for algebras over infinity-operads" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Hoffbeck and Moerdijk define algebras over linear $\infty$-operads and coalgebras over $\infty$-cooperads, extending their Koszul duality to categories of algebras/coalgebras. The proof hinges on a duality between presheaves and copresheaves on a category of trees, yielding homology theories for $\infty$-operad algebras.
\begin{enumerate}
  \item introduces algebras/coalgebras over linear $\infty$-(co)operads;
  \item extends Koszul duality to these categories;
  \item proves a presheaf/copresheaf duality on trees supporting (co)algebra structures; and
  \item defines homology of $\infty$-operad algebras via tree homology.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469900] Question on extending Koszul duality to $\infty$-operads.
  \item[MO 469932] Thread on presheaf/copresheaf duality for trees.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506950] "$\infty$-operad algebras vs. classical operads".
  \item[Math.SE 506984] "Homology of $\infty$-operad algebras".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Review linear $\infty$-operads/cooperads (Math.SE 506950).
  \item \textbf{Algebras/coalgebras.} Define the new notions.
  \item \textbf{Duality theorem.} Present the extended Koszul duality (MO 469900).
  \item \textbf{Tree duality + homology.} Explain the presheaf duality and resulting homology (MO 469932, Math.SE 506984).
  \item \textbf{PlanetMath links.} Connect to operad theory and higher category entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for technical proofs.
  \item Pull MO embeddings (469900, 469932) and Math.SE embeddings (506950, 506984).
  \item Draft the PlanetMath entry detailing the duality framework.
\end{itemize}
