% PlanetMath proposal draft for arXiv:2602.19390
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Stable correspondences for ambidextrous functors}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19390, "Stable correspondences for ambidextrous functors" (2026-02-21)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Stable correspondences encode ambidexterity (co/limit compatibilities) in symmetric monoidal $\infty$-categories. The paper:
\begin{enumerate}
  \item defines a bicategory $\mathrm{Corr}^{\mathrm{st}}(\mathcal{C})$ whose morphisms are spans together with stabilization data;
  \item proves an ambidexterity theorem showing that norms and transfers agree inside $\mathrm{Corr}^{\mathrm{st}}$;
  \item applies the theorem to motivic spectra and power operations; and
  \item provides explicit norm formulas explained via MathOverflow 466503/467551.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 466503] Number-theoretic spans giving intuition for norm/trace compatibilities.
  \item[MO 467551] Green-function spans used to motivate the spectral examples.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 492014] "Ambidexterity in stable homotopy".
  \item[Math.SE 494288] "Span correspondences and traces".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Review ambidexterity for functors and recall classical norm/trace identities.
  \item Introduce $\mathrm{Corr}^{\mathrm{st}}$ and describe the stabilization data.
  \item State and sketch the ambidexterity theorem, referencing MO 466503.
  \item Present the motivic spectrum example that uses Math.SE 492014.
  \item Summarize the consequences for power operations and overlaps with Math.SE 494288.
\end{enumerate}
\subsection*{Action items}
Pull arXiv source, gather MO embeddings (466503, 467551), gather Math.SE embeddings (492014, 494288), draft the entry with the richer outline.
