% PlanetMath proposal draft for arXiv:2602.08954
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Equivalent definitions of fusion category arising from separability}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.08954, "Equivalent definitions of fusion category arising from separability" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Zhenbang Zuo studies semisimple multiring categories with left duals and shows that simplicity of the unit object is equivalent to separability (and several variants) of tensoring with any non-zero algebra. This produces a list of interchangeable fusion-category axioms and yields connectivity criteria for weak Hopf algebras plus transfer results for unit simplicity across module categories and Grothendieck rings.
\begin{enumerate}
  \item Shows equivalence between unit simplicity and separability/faithfulness/(dual) Maschke/ conservativity of tensor functors.
  \item Applies the equivalence to describe connected weak Hopf algebras via separable tensor functors.
  \item Transfers simplicity conditions between units, indecomposable module categories, and Grothendieck rings.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479005] Discussion on separable tensor functors in multiring categories.
  \item[MO 479044] Clarifying how unit simplicity propagates to module categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 508523] "Maschke vs. separable tensor functors" -- concrete fusion-category calculations.
  \item[Math.SE 508557] "Grothendieck ring simplicity transfer" -- examples covering weak Hopf algebras.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Setup.} Define semisimple multiring categories, left duals, and tensor-by-algebra functors.
  \item \textbf{Equivalences.} Present the unit-simplicity equivalences (MO 479005, Math.SE 508523).
  \item \textbf{Applications.} Summarise consequences for weak Hopf algebras and module categories (MO 479044).
  \item \textbf{Grothendieck rings.} Explain the transfer of simplicity to Grothendieck rings (Math.SE 508557).
  \item \textbf{Examples.} Work out explicit categories, highlighting separable tensor functors in practice.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Download the arXiv source to quote key equivalence theorems and proofs of the applications.
  \item Link MO 479005/479044 and Math.SE 508523/508557 discussions for context.
  \item Draft PlanetMath entry showcasing the hierarchy of equivalent fusion-category definitions.
\end{itemize}
