% PlanetMath proposal draft for arXiv:2602.11943
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Cylinder simplicial DG rings}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.11943, "The Cylinder Simplicial DG Ring" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Yekutieli constructs cylinder DG rings $Cyl_q(B)$ for $q\ge 0$, forming a simplicial DG ring $Cyl(B)$. For semi-free $A$, the simplicial set $Hom(A,Cyl(B))$ is Kan; horns are represented by DG rings $N(Y,B)$.
\begin{enumerate}
  \item defines the cylinder DG rings and simplicial object $Cyl(B)$;
  \item proves $Hom(A,Cyl(B))$ is a Kan complex when $A$ is semi-free;
  \item introduces $N(Y,B)$ representing horns; and
  \item discusses extensions to DG categories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469120] Question on cylinder DG rings and Kan properties.
  \item[MO 469148] Thread on horn-representing DG rings.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506010] "Keller's cylinder DG ring".
  \item[Math.SE 506042] "Kan complexes in DG ring mapping spaces".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{DG background.} Review cylinders/path objects (Math.SE 506010).
  \item \textbf{Cylinder simplicial DG ring.} Define $Cyl_q$ and $Cyl(B)$ (MO 469120).
  \item \textbf{Kan property.} Explain the proof using $N(Y,B)$ (MO 469148, Math.SE 506042).
  \item \textbf{Extensions.} Mention DG category generalizations.
  \item \textbf{PlanetMath links.} Connect to DG algebras and simplicial techniques.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source to capture constructions.
  \item Pull MO embeddings (469120, 469148) and Math.SE embeddings (506010, 506042).
  \item Draft the PlanetMath entry summarizing applications to DG categories.
\end{itemize}
