% PlanetMath proposal draft for arXiv:2602.01316
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Ordering simples in length categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.01316, "Ordnung muss sein" (2026-02-01)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Krause characterizes when a length category is equivalent to finite-dimensional representations of a poset by requiring a partial order on isomorphism classes of simples that satisfies explicit rules. This supplies categorical control of length categories via posets.
\begin{enumerate}
  \item sets up the rules ensuring compatibility between extensions and the partial order;
  \item proves necessity/sufficiency for representing the category as poset representations;
  \item discusses examples and counterexamples; and
  \item links the construction to classical representation theory of posets.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 466950] Question on ordering simples to model length categories by posets.
  \item[MO 466982] Discussion on extension rules ensuring poset realizations.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 501820] "Length categories and poset representations".
  \item[Math.SE 501874] "Examples where the ordering fails".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Length categories recap.} Define simples/Loewy length (Math.SE 501820).
  \item \textbf{Ordering rules.} Present the necessary/sufficient conditions (MO 466950, MO 466982).
  \item \textbf{Representation equivalence.} Show equivalence with poset representations.
  \item \textbf{Examples.} Contrast satisfying vs. failing cases (Math.SE 501874).
  \item \textbf{PlanetMath links.} Connect to entries on poset representations and length categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for the precise set of ordering rules.
  \item Pull MO embeddings (466950, 466982) and Math.SE embeddings (501820, 501874).
  \item Draft the PlanetMath entry mapping rules to examples.
\end{itemize}
