% PlanetMath proposal draft for arXiv:2602.09283
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Condensed sets and the Solovay model}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09283, Bannister--Basak, ``Condensed Sets and the Solovay Model'' (2026-02-20)
  \item Cross-reference MO 385129 on interpreting condensed/pyknotic sets via forcing; Math.SE 3790988 on Solovay’s model and regularity
\end{itemize}
\subsection*{Synopsis}
The authors construct a Grothendieck topos $\mathbf{Sh}(\mathsf{Sol})$ covering the topos of $\kappa$-pyknotic sets and identify its double-negation subtopos with the Solovay model $V(\mathbb{R})$ of Levy-collapse extensions. This bridge lets them:
\begin{enumerate}
  \item Interpret condensed/pyknotic sets as ``generically invariant'' data inside $V(\mathbb{R})$, clarifying MO 385129’s forcing heuristics.
  \item Use automatic continuity in the Solovay model to reprove Clausen--Scholze’s vanishing of $\underline{\mathrm{Ext}}(\underline{A},\underline{\mathbb{Z}})$ for discrete $A$ and locally compact abelian groups.
  \item Relate geometric morphisms, forcing names, and regularity properties (Math.SE 3790988) to condensed mathematics.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 385129] asks how condensed/pyknotic sets reflect forcing semantics; the paper gives a concrete Solovay-model avatar.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 3790988] discusses Solovay’s model where all sets of reals are Lebesgue measurable; these regularity features power the automatic continuity arguments.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Condensed and pyknotic sets.} Briefly review definitions and their connection to profinite sites.
  \item \textbf{The Solovay cover.} Describe the site $\mathsf{Sol}$, the geometric morphism $\mathbf{Sh}(\mathsf{Sol}) \to \mathbf{Pyk}_\kappa$, and the deduction that double negation yields $V(\mathbb{R})$.
  \item \textbf{Automatic continuity via Solovay.} Explain how regularity in $V(\mathbb{R})$ proves the vanishing of $\underline{\mathrm{Ext}}$ for discrete and locally compact groups.
  \item \textbf{Set-theoretic interpretation.} Elaborate on the forcing/Boolean-valued perspective linking condensed sets to Levy collapse (MO 385129).
  \item \textbf{Applications.} Record consequences for Whitehead problems, internal $\underline{\mathrm{Ext}}$, and potential new directions in condensed mathematics.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Check \texttt{pm-full-dictionary.json} for entries on ``condensed set'', ``pyknotic set'', and ``Solovay model'' to coordinate scope.
  \item Summarize the construction of $\mathbf{Sh}(\mathsf{Sol})$ and its double-negation core in PlanetMath style.
  \item Detail the automatic continuity argument for $\underline{\mathrm{Ext}}$ and relate it to existing Whitehead-problem articles.
  \item Provide cross-links to PlanetMath pages on forcing, Grothendieck toposes, and regularity properties of sets of reals.
\end{itemize}
