% PlanetMath proposal draft for arXiv:2602.12363
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Parametrized equivalence relation on the global class of morphisms}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.12363, "Parametrized equivalence relation on the global class of morphisms of a category and frame-theoretic examples" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Nizar El Idrissi defines an equivalence relation on the entire class of morphisms of a category, subsuming group-action orbit relations and new examples coming from Bessel families/continuous frames. The invariant is parametrized by coarse data such as pointwise norms of analysis operators, providing a categorical foothold for frame-theoretic classification problems.
\begin{enumerate}
  \item Defines the parametrized equivalence relation and shows it generalises classic orbit relations.
  \item Demonstrates the framework on Bessel families via the analysis-operator norm invariant.
  \item Suggests categorical invariant theory directions for frames.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479978] Relating morphism equivalence relations to group actions.
  \item[MO 480004] Bessel-family invariants viewed categorically.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509522] "Continuous frames as categorical morphisms".
  \item[Math.SE 509548] "Pointwise norm invariants" -- computations for Bessel families.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Construction.} Define the equivalence relation and relate to standard orbit notions (MO 479978).
  \item \textbf{Frame examples.} Explain the Bessel-family case (Math.SE 509548, MO 480004).
  \item \textbf{Properties.} Discuss stability under categorical operations.
  \item \textbf{Applications.} Outline directions for categorical invariant theory of frames (Math.SE 509522).
  \item \textbf{Further work.} Mention open problems on classification.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source describing the equivalence relation and examples.
  \item Capture MO 479978/480004 and Math.SE 509522/509548 references.
  \item Emphasise frame-theoretic applications in the PlanetMath entry.
\end{itemize}
