% PlanetMath proposal draft for arXiv:2602.01821
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Automorphic equivalence in universal algebraic geometry}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.01821, "Categories and functors of universal algebraic geometry. Automorphic equivalence of algebras" (2026-02-02)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Tsurkov revisits automorphic equivalence of algebras using categorical language: two algebras share the same algebraic geometry when their categories of algebraic closed sets are isomorphic via automorphisms. The paper streamlines Plotkin's original definitions and recalls key theorems in this setting.
\begin{enumerate}
  \item defines categories of algebraic closed sets for universal algebras;
  \item distinguishes geometric vs. automorphic equivalence;
  \item gives a categorical definition of automorphic equivalence; and
  \item surveys fundamental theorems and examples.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467781] Question on automorphic equivalence formulated categorically.
  \item[MO 467830] Discussion on Plotkin's program inside modern category theory.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 503930] "Geometric vs. automorphic equivalence of algebras".
  \item[Math.SE 503988] "Categories of algebraic closed sets and Plotkin's theory".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Universal algebraic geometry.} Introduce the categories of algebraic closed sets (Math.SE 503988).
  \item \textbf{Equivalence notions.} Compare geometric and automorphic equivalence (Math.SE 503930).
  \item \textbf{Categorical reformulation.} Present Tsurkov's definition and cite MO 467781.
  \item \textbf{Theorems/examples.} Summarize key results from Plotkin's school (MO 467830).
  \item \textbf{PlanetMath links.} Point to entries on algebraic geometry over algebras and equivalence concepts.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source to extract precise categorical definitions.
  \item Pull MO embeddings (467781, 467830) and Math.SE embeddings (503930, 503988).
  \item Draft the PlanetMath article summarizing the equivalence hierarchy.
\end{itemize}
