% PlanetMath proposal draft for arXiv:2602.11971
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Hypercovers in Differential Geometry}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.11971, "Hypercovers in Differential Geometry" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Glass and Minichiello show that, for several differential-geometric sites (smooth manifolds with open covers, cartesian spaces with good covers, etc.), the local projective and Čech projective model structures coincide. Consequently the plus construction sheafifies presheaves after a single iteration. The argument leverages hypercovers built from geometric refinements.
\begin{enumerate}
  \item Defines the relevant sites and model structures.
  \item Shows equality of local and Čech projective structures via hypercovers.
  \item Applies the result to sheafification via the plus construction.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479742] Hypercover refinements on smooth-manifold sites.
  \item[MO 479769] Čech vs. local model structures in differential geometry.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509230] "One-step sheafification via plus construction" -- worked example on manifolds.
  \item[Math.SE 509256] "Hypercovers for good open covers" -- explicit combinatorics.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Sites and model structures.} Describe the differential-geometric sites and both projective structures (MO 479769).
  \item \textbf{Hypercovers.} Explain the constructions ensuring equality (Math.SE 509256).
  \item \textbf{Sheafification.} Detail the plus-construction corollary (Math.SE 509230).
  \item \textbf{Examples.} Work through smooth manifolds and cartesian spaces (MO 479742).
  \item \textbf{Extensions.} Note potential applications to derived differential geometry.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Fetch the arXiv source for proofs of the equality and corollary.
  \item Capture MO 479742/479769 and Math.SE 509230/509256 references.
  \item Draft PlanetMath entry emphasising hypercovers and one-step sheafification.
\end{itemize}
