% PlanetMath proposal draft for arXiv:2602.14424
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Monoidal bicategories as $\mathsf{E}_k$-monoids}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.14424, "The higher algebra and geometry of monoidal bicategories" (2026-02-16)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Stenzel proves that braided, sylleptic, and symmetric monoidal bicategories correspond to $\mathsf{E}_k$-monoids in the cartesian monoidal $(\infty,1)$-category of bicategories for suitable $k$, using the geometry of little cubes operads to connect 2-dimensional algebra to higher algebra.
\begin{enumerate}
  \item interprets monoidal bicategories via little cubes operads;
  \item identifies braided, sylleptic, symmetric structures with $\mathsf{E}_k$-monoids;
  \item explains the geometric mediation between 2D and $(\infty,1)$ algebra; and
  \item discusses computational consequences.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469770] Question on relating monoidal bicategories to $\mathsf{E}_k$-monoids.
  \item[MO 469798] Thread on little cubes operads in 2-categorical settings.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506820] "Sylleptic bicategories and higher operads".
  \item[Math.SE 506856] "Computations with $\mathsf{E}_k$-monoids".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Review monoidal bicategories and little cubes (Math.SE 506820).
  \item \textbf{Correspondence.} State the identification with $\mathsf{E}_k$-monoids (MO 469770).
  \item \textbf{Geometry.} Explain operadic mediation (MO 469798).
  \item \textbf{Applications.} Mention computational benefits (Math.SE 506856).
  \item \textbf{PlanetMath links.} Connect to operad and bicategory entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for proof details.
  \item Pull MO embeddings (469770, 469798) and Math.SE embeddings (506820, 506856).
  \item Draft the PlanetMath entry highlighting the $\mathsf{E}_k$ perspective.
\end{itemize}
