% PlanetMath proposal draft for arXiv:2602.03739
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Semiseparable induction functors in monoidal categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.03739, "Semiseparability of induction functors in a monoidal category" (2026-02-03)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Bottegoni and Zuo give criteria for when induction functors attached to algebra morphisms in a monoidal category are semiseparable, show how the property behaves under lax monoidal functors, and mirror the results for coalgebra coinduction in duoidal settings.
\begin{enumerate}
  \item characterizes semiseparable induction functors for algebra morphisms;
  \item proves stability under lax monoidal functors;
  \item develops the dual theory for coinduction from coalgebra morphisms; and
  \item applies the results to duoidal categories and combinations of (co)induction functors.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467908] Query on semiseparable induction in monoidal categories.
  \item[MO 467966] Thread about transferring semiseparability via lax monoidal functors.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 504080] "Examples of semiseparable induction".
  \item[Math.SE 504110] "Coinduction in duoidal categories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Semiseparability basics.} Recall definitions and cite Math.SE 504080.
  \item \textbf{Induction criteria.} State the necessary/sufficient conditions (MO 467908).
  \item \textbf{Functoriality.} Discuss stability under lax monoidal functors (MO 467966).
  \item \textbf{Coinduction + duoidal examples.} Summarize dual statements (Math.SE 504110).
  \item \textbf{PlanetMath links.} Connect to entries on induction, duoidal categories, and separable functors.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for proofs and examples.
  \item Fetch MO embeddings (467908, 467966) and Math.SE embeddings (504080, 504110).
  \item Draft the PlanetMath entry highlighting the duoidal applications.
\end{itemize}
