% PlanetMath proposal draft for arXiv:2602.08694
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Generalized inflations and étale homotopy types}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.08694, "Homotopy types of finite étale spaces and generalized inflations" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Ayzenberg and Khoroshavkina generalize inflations of simplicial complexes by replacing simplices with arbitrary finite sets of copies organized via sheaves; the resulting generalized inflation is the étale space of the sheaf. Under flabbiness, the poset fiber theorem description of homotopy types still holds.
\begin{enumerate}
  \item introduces generalized inflations over simplicial posets via sheaves;
  \item interprets inflations as étale spaces of sheaves on finite topologies;
  \item proves the poset fiber theorem under flabby conditions; and
  \item recovers results on clique complexes of multigraphs.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468670] Question on poset fiber theorems for generalized inflations.
  \item[MO 468698] Thread on étale spaces of finite sheaves.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505300] "Inflation of simplicial complexes".
  \item[Math.SE 505332] "Flabby sheaves on finite topologies".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Classical inflation.} Review vertex inflations and the poset fiber theorem (Math.SE 505300).
  \item \textbf{Sheaf viewpoint.} Define generalized inflations as étale spaces (MO 468698).
  \item \textbf{Homotopy types.} Present the flabby condition and resulting theorem (MO 468670, Math.SE 505332).
  \item \textbf{Applications.} Mention clique complexes and multigraphs.
  \item \textbf{PlanetMath links.} Connect to entries on simplicial posets, étale spaces, and sheaves.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source to capture definitions and proofs.
  \item Fetch MO embeddings (468670, 468698) and Math.SE embeddings (505300, 505332).
  \item Draft the PlanetMath entry summarizing the generalized inflation framework.
\end{itemize}
