% PlanetMath proposal draft for arXiv:2602.04425
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Homological algebra in abelian framed bicategories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.04425, "Homological Algebra in Abelian Framed Bicategories: Exact Sequences and Embedding Theorems" (2026-02-04)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Albert, Dubut, and Goubault introduce abelian framed bicategories (locally abelian framed bicategories) and develop homology/cohomology theories for directed structures, including Mayer--Vietoris, Künneth, and embedding theorems analogous to Gabriel and Freyd-Mitchell.
\begin{enumerate}
  \item defines abelian framed bicategories and their homological gadgets;
  \item proves exact sequences (relative homology, Mayer--Vietoris) in this context;
  \item establishes Künneth theorems for closed monoidal abelian framed bicategories; and
  \item proves embedding theorems showing they can be realized as bicategories of bimodules.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468050] Question about directed homology in framed bicategories.
  \item[MO 468094] Discussion on Gabriel/Freyd-Mitchell analogues for bicategories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 504250] "Mayer--Vietoris in abelian framed bicategories".
  \item[Math.SE 504312] "Embedding framed bicategories as bimodules".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Definitions.} Introduce framed bicategories and the abelian condition (Math.SE 504250).
  \item \textbf{Exact sequences.} Present relative homology and Mayer--Vietoris (MO 468050).
  \item \textbf{Künneth + monoidal structure.} Explain the closed monoidal assumptions.
  \item \textbf{Embedding theorems.} Describe Gabriel/Freyd-Mitchell analogues (MO 468094, Math.SE 504312).
  \item \textbf{Applications.} Outline links to directed homology and bimodule bicategories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for the exact sequence and embedding proofs.
  \item Pull MO embeddings (468050, 468094) and Math.SE embeddings (504250, 504312).
  \item Draft the PlanetMath entry with diagrams illustrating framed bicategory homology.
\end{itemize}
