% PlanetMath proposal draft for arXiv:2602.09371
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Acyclic FP-injective complexes over Ding-Chen rings}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09371, "Acyclic complexes of FP-injective modules over Ding-Chen rings" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Gillespie combines cotorsion pairs to build new abelian model structures on modules over left coherent rings. Fibrant objects arise from weakly Ding injectives; he characterizes them as cycles of acyclic FP-injective complexes. For Ding-Chen rings this matches acyclic FP-injective complexes, giving new descriptions of stable module categories via Gorenstein FP-pro-injectives.
\begin{enumerate}
  \item presents a method to combine cotorsion pairs into model structures;
  \item constructs a model on modules with weakly Ding injective fibrants;
  \item characterizes fibrants as cycles of FP-injective complexes (Ding-Chen case);
  \item defines Gorenstein FP-pro-injectives and connects to stable categories;
  \item lifts complete cotorsion pairs to derived models even when non-hereditary.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470080] Question on combining cotorsion pairs into models.
  \item[MO 470112] Thread on weakly Ding injective modules.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507160] "FP-injective complexes over Ding-Chen rings".
  \item[Math.SE 507198] "Stable categories via Gorenstein FP-pro-injectives".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Cotorsion combination.} Explain the new method (MO 470080).
  \item \textbf{Model structure.} Describe weakly Ding injective fibrants (Math.SE 507160).
  \item \textbf{Characterization.} Detail cycle description and Ding-Chen specialization (MO 470112).
  \item \textbf{Stable category.} Present Gorenstein FP-pro-injectives (Math.SE 507198).
  \item \textbf{Applications.} Mention lifting to derived categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for proofs/details.
  \item Fetch MO embeddings (470080, 470112) and Math.SE embeddings (507160, 507198).
  \item Draft the PlanetMath entry focusing on the model structure and stable categories.
\end{itemize}
