% PlanetMath proposal draft for arXiv:2602.12239
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Tininess and right adjoints to exponentials}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.12239, "Tininess and right adjoints to exponentials" (2026-02-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Ruiz Hernández and Solórzano study objects $T$ in a topos such that $(-)^T$ admits a right adjoint, Lawvere's A.T.O.M.s. They analyze categorical behavior (subobjects, quotients, retracts) and topological behavior in precohesive toposes over decidable objects, relating to Synthetic Differential Geometry.
\begin{enumerate}
  \item surveys categorical properties of A.T.O.M.s (subobjects, quotients, retracts);
  \item studies topological behavior (connectedness, contractibility) in precohesive toposes;
  \item examines the right adjoint $(-)_T$ and its connected components; and
  \item relates findings to Lawvere's SDG program.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469170] Question on objects with right adjoints to exponentials in toposes.
  \item[MO 469199] Discussion on precohesive toposes over decidable objects.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506080] "A.T.O.M.s in elementary toposes".
  \item[Math.SE 506124] "Topological behavior of $(-)_T$".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Definition and motivation.} Introduce A.T.O.M.s (Math.SE 506080).
  \item \textbf{Categorical properties.} Summarize results on subobjects etc. (MO 469170).
  \item \textbf{Topological analysis.} Discuss precohesive settings (MO 469199, Math.SE 506124).
  \item \textbf{SDG connections.} Relate to Lawvere's proposals.
  \item \textbf{PlanetMath links.} Connect to topos theory, exponentials, and SDG entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source and extract categorical/topological statements.
  \item Fetch MO embeddings (469170, 469199) and Math.SE embeddings (506080, 506124).
  \item Draft the PlanetMath entry summarizing tininess phenomena.
\end{itemize}
