% PlanetMath proposal draft for arXiv:2602.09885
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Geometric differentiation of simplicial manifolds}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09885, "Geometric differentiation of simplicial manifolds" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Cabrera and del Hoyo solve the differentiation problem for simplicial manifolds by building compatible tubular neighbourhoods, identifying a differentiating ideal in cochains, and interpreting the quotient as the Chevalley--Eilenberg algebra of a higher Lie algebroid. They introduce a higher van Est map with an isomorphism theorem under connectivity hypotheses and explain the construction via a monoidal refinement of the dual Dold--Kan correspondence.
\begin{enumerate}
  \item Establishes a normal form via tubular neighbourhoods for simplicial manifolds.
  \item Constructs the differentiating ideal and resulting higher Lie algebroid.
  \item Defines the higher van Est map and proves an isomorphism theorem under connectivity assumptions.
  \item Relates the mechanism to a monoidal refinement of dual Dold--Kan.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479205] Higher Lie algebroids associated with simplicial manifolds.
  \item[MO 479241] van Est maps beyond Lie groupoids and their connectivity conditions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 508701] "Tubular neighbourhoods in simplicial geometry" -- worked example.
  \item[Math.SE 508745] "Dual Dold--Kan refinements" -- intuition for the monoidal explanation.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Differentiation problem.} Review existing approaches and motivate the geometric solution (Math.SE 508701).
  \item \textbf{Normal form.} Describe the tubular neighbourhood construction and differentiating ideal (MO 479205).
  \item \textbf{Higher Lie algebroid.} Explain the Chevalley--Eilenberg algebra identification.
  \item \textbf{van Est theorem.} Present the higher van Est map and connectivity criteria (MO 479241).
  \item \textbf{Dual Dold--Kan link.} Summarise the monoidal refinement (Math.SE 508745).
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for detailed proofs of the normal form and van Est sections.
  \item Capture MO 479205/479241 and Math.SE 508701/508745 references.
  \item Emphasise geometric vs. homotopical viewpoints when drafting the PlanetMath entry.
\end{itemize}
