% PlanetMath proposal draft for arXiv:2602.04049
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Categorical frameworks for cellular automata}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.04049, "A categorical framework for cellular automata" (2026-02-03)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Castillo-Ramirez, Vazquez-Aceves, and Zaldivar-Corichi define $\mathscr{C}$-cellular automata inside any category with products, proving a categorical Curtis--Hedlund--Lyndon theorem and generalizing to $\mathscr{C}$-automata between different group universes. The resulting morphisms form subcategories closed under finite products and weak products.
\begin{enumerate}
  \item defines $\mathscr{C}$-cellular automata as morphisms $A^G\to B^G$ and proves closure properties;
  \item establishes the categorical Curtis--Hedlund--Lyndon theorem;
  \item treats generalized automata $A^G\to B^H$ coming from homomorphisms $H\to G$; and
  \item studies weak products using free products of group universes.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467601] Question on categorical formulations of the Curtis--Hedlund theorem.
  \item[MO 467644] Thread about cellular automata between different groups.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 503412] "Cellular automata in an arbitrary category".
  \item[Math.SE 503498] "Generalized automata via homomorphisms $H\to G$".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Classical background.} Recap standard cellular automata and cite Math.SE 503412.
  \item \textbf{$\mathscr{C}$-Automata definition.} Explain the categorical setup and MO 467601.
  \item \textbf{Curtis--Hedlund--Lyndon.} State the categorical version and key lemmas.
  \item \textbf{Generalized automata.} Describe $A^G\to B^H$ and the role of homomorphisms (MO 467644, Math.SE 503498).
  \item \textbf{Weak products.} Record closure under finite weak products and implications for PlanetMath entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source and capture proofs of the categorical CHL theorem.
  \item Fetch MO embeddings (467601, 467644) and Math.SE embeddings (503412, 503498).
  \item Draft the PlanetMath entry comparing classical vs. categorical automata.
\end{itemize}
