% PlanetMath proposal draft for arXiv:2602.16017
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Homotopy Lie algebras and coherent 2-braidings}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.16017, "Homotopy Lie algebras and coherent infinitesimal 2-braidings" (2026-02-17)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Kemp constructs symmetric monoidal dg-categories of $L_\infty$-modules, compares them with Chevalley--Eilenberg dg-modules, and extracts coherent infinitesimal 2-braidings from 2-shifted Poisson structures. The paper also computes the differential of the Chevalley--Eilenberg algebra of a homotopy Lie algebra and builds an explicit dg-equivalence.
\begin{enumerate}
  \item builds a symmetric monoidal dg-category of $L_\infty$-modules and its homotopy 2-category;
  \item produces infinitesimal 2-braidings from shifted Poisson structures and proves coherence;
  \item computes Chevalley--Eilenberg differentials for finite-dimensional homotopy Lie algebras; and
  \item constructs the dg-equivalence with semi-free dg-modules.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468120] Question on extracting braidings from Poisson structures in $L_\infty$-geometry.
  \item[MO 468188] Thread clarifying the Chevalley--Eilenberg algebra of homotopy Lie algebras.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507012] "Representations of $L_\infty$-algebras via dg-categories".
  \item[Math.SE 507144] "Infinitesimal 2-braidings and perverse schobers".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{$L_\infty$ preliminaries.} Review homotopy Lie algebras and their modules (Math.SE 507012).
  \item \textbf{dg-categories of modules.} Describe the symmetric monoidal dg-category and its homotopy 2-category.
  \item \textbf{Infinitesimal 2-braidings.} Explain the construction from shifted Poisson structures, citing MO 468120.
  \item \textbf{Chevalley--Eilenberg side.} Detail the dg-equivalence and differential computation (MO 468188).
  \item \textbf{Applications.} Note interactions with perverse schobers/exit-path geometry (Math.SE 507144) and PlanetMath cross-links.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source and isolate definitions/examples.
  \item Fetch MO embeddings (468120, 468188) and Math.SE embeddings (507012, 507144).
  \item Draft the PlanetMath entry emphasizing bridges to schober and Poisson articles.
\end{itemize}
