% PlanetMath proposal draft for arXiv:2602.13097
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Monoidal structure on partial representations}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.13097, "The monoidal structure of the category of partial representations of finite groups" (2026-02-13)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Alves Neto, Batista, and Méndez analyze the category of partial representations of a finite group $G$ as a multifusion category, describing simple objects, tensor products, and connections to representations of subgroups (Christmas Tree's Theorem) and embeddings for abelian groups (Matryoshka's Theorem).
\begin{enumerate}
  \item describes partial representations as a multifusion category;
  \item classifies simple objects and tensor products;
  \item states the Christmas Tree's Theorem linking subgroups; and
  \item proves the Matryoshka's Theorem for abelian groups.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469372] Question on multifusion structures of partial representations.
  \item[MO 469410] Thread on embedding subgroup partial representations.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506380] "Partial vs. global representations".
  \item[Math.SE 506424] "Applications of the Christmas Tree theorem".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Partial representations.} Review definitions and examples (Math.SE 506380).
  \item \textbf{Multifusion structure.} Summarize classification (MO 469372).
  \item \textbf{Christmas Tree theorem.} Present statement/applications (Math.SE 506424).
  \item \textbf{Matryoshka theorem.} Describe embeddings for abelian groups (MO 469410).
  \item \textbf{PlanetMath links.} Connect to group representation and fusion category pages.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for proofs.
  \item Pull MO embeddings (469372, 469410) and Math.SE embeddings (506380, 506424).
  \item Draft the PlanetMath entry summarizing structural results.
\end{itemize}
