% PlanetMath proposal draft for arXiv:2602.12505
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Coalgebra measurings and cyclic theory}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.12505, "Coalgebra measurings, cyclic theory and homologies of matrix algebras" (2026-02-13)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Banerjee and Kour study coalgebra measurings and the induced maps between Hochschild/cyclic homology of algebras, showing these maps respect $λ$-decompositions, products, and module structures. They relate measurings to homologies of matrix algebras (cyclic, Lie, Leibniz, dihedral) and analyze primitive parts.
\begin{enumerate}
  \item defines coalgebra measurings and induced maps on homology;
  \item proves compatibility with $λ$-decomposition, products, module structures;
  \item relates measurings to matrix algebra homologies (Lie, Leibniz, dihedral);
  \item applies to cyclic homology, primitive parts, and Lie algebra homology.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470460] Question on measurings and Hochschild homology.
  \item[MO 470492] Thread on homologies of matrix algebras.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507560] "Coalgebra measurings".
  \item[Math.SE 507598] "Primitive parts in Lie/Leibniz homology".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Measurings.} Introduce definitions and examples (Math.SE 507560).
  \item \textbf{Homology maps.} Discuss properties (MO 470460).
  \item \textbf{Matrix contexts.} Relate to Lie/Leibniz/dihedral homologies (MO 470492, Math.SE 507598).
  \item \textbf{Applications.} Mention cyclic theory and primitive parts.
  \item \textbf{PlanetMath links.} Connect to Hochschild/cyclic homology entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for proofs.
  \item Pull MO embeddings (470460, 470492) and Math.SE embeddings (507560, 507598).
  \item Draft the PlanetMath entry summarizing the measuring-induced maps.
\end{itemize}
