% PlanetMath proposal draft for arXiv:2602.08480
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Notes on tensor triangular geometry}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.08480, "Some notes on tensor triangular geometry" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Stevenson surveys tensor triangular geometry for both essentially small and compactly generated categories through lattice-theoretic techniques. After covering the small case and Thomason's theorem, he experiments with compactly generated settings.
\begin{enumerate}
  \item introduces tensor triangular geometry via lattices of thick subcategories;
  \item discusses the spectrum of perfect complexes and Thomason's theorem;
  \item extends the discussion to compactly generated categories; and
  \item outlines new thoughts on presentable settings.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468610] Discussion on lattice approaches to tensor triangular geometry.
  \item[MO 468655] Question on compactly generated spectra.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505210] "Thomason's theorem via tensor triangular methods".
  \item[Math.SE 505244] "Compactly generated tensor triangular spectra".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Small case.} Review thick subcategories and spectra (Math.SE 505210).
  \item \textbf{Thomason's theorem.} Present the tensor triangular proof (MO 468610).
  \item \textbf{Compactly generated case.} Summarize experimental ideas (MO 468655, Math.SE 505244).
  \item \textbf{Applications.} Note links to derived categories, motives, and PlanetMath entries.
  \item \textbf{Further reading.} Point to standard references and how this note complements them.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source to capture key statements.
  \item Pull MO embeddings (468610, 468655) and Math.SE embeddings (505210, 505244).
  \item Draft the PlanetMath article as a cross-reference hub for tensor triangular geometry.
\end{itemize}
