% PlanetMath proposal draft for arXiv:2602.09283
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Condensed Sets and the Solovay Model}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09283, "Condensed Sets and the Solovay Model" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Bannister and Basak construct a geometric morphism from the topos encoding the Solovay model to $\kappa$-pyknotic sets (Clausen--Scholze), tying determinacy-inspired set theory to condensed mathematics. Automatic continuity in the Solovay model then yields a topos-theoretic proof of the Whitehead problem for discrete condensed abelian groups and an internal $Ext$ computation for locally compact abelian groups in that setting.
\begin{enumerate}
  \item Builds the geometric morphism between the Solovay topos and $\kappa$-pyknotic sets.
  \item Uses automatic continuity to reprove Clausen--Scholze's Whitehead result for condensed abelian groups.
  \item Computes internal $Ext$ between locally compact abelian groups in the Solovay model.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 479112] Questions on pyknotic vs. condensed morphisms arising from Solovay-style determinacy.
  \item[MO 479147] Automated continuity arguments inside the Solovay topos.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 508618] "Condensed Whitehead problem via Solovay model" -- sketch of key steps.
  \item[Math.SE 508642] "Internal Ext in Solovay topoi" -- computational example.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Summarise condensed and pyknotic sets plus the Solovay model (MO 479112).
  \item \textbf{Geometric morphism.} Detail the constructed morphism and its properties.
  \item \textbf{Whitehead problem.} Explain the automatic continuity argument (Math.SE 508618, MO 479147).
  \item \textbf{Ext computations.} Present the internal $Ext$ calculation (Math.SE 508642).
  \item \textbf{Implications.} Discuss broader connections between determinacy and condensed mathematics.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Sync the arXiv source sections on the geometric morphism and Whitehead application.
  \item Link MO 479112/479147 and Math.SE 508618/508642 posts when drafting PlanetMath.
  \item Highlight how automatic continuity feeds into condensed computations.
\end{itemize}
