% PlanetMath proposal draft for arXiv:2602.13097
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{The monoidal structure of the category of partial representations of finite groups}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.13097, "The monoidal structure of the category of partial representations of finite groups" (2026-02-13)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Alves Neto, Batista, and Méndez analyse partial representations of a finite group $G$ as a multifusion category. They classify simples, describe tensor products, connect to global representations of subgroups ("Christmas Tree" theorem), and prove an embedding result for partial representations of subgroups into those of $G$ when $G$ is abelian ("Matryoshka" theorem).
\begin{enumerate}
  \item Shows the category of partial representations is multifusion and classifies simple objects.
  \item Describes tensor products via subgroup representations (Christmas Tree theorem).
  \item Proves embedding results for abelian groups (Matryoshka theorem).
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 480221] Multifusion structures on partial representation categories.
  \item[MO 480249] Embedding partial representations of subgroups.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509789] "Simple objects in partial representation categories".
  \item[Math.SE 509816] "Christmas Tree theorem examples" -- explicit calculations.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Partial representations.} Review definitions and known tensor products (Math.SE 509789).
  \item \textbf{Multifusion structure.} Present classification and product rules (MO 480221).
  \item \textbf{Subgroup connections.} Detail Christmas Tree and Matryoshka theorems (MO 480249, Math.SE 509816).
  \item \textbf{Examples.} Provide abelian and non-abelian cases.
  \item \textbf{Applications.} Mention implications for partial actions and Hopf algebras.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Retrieve the arXiv source for theorem statements and proofs.
  \item Capture MO 480221/480249 and Math.SE 509789/509816 references.
  \item Emphasise multifusion/embedding results in the PlanetMath entry.
\end{itemize}
