% PlanetMath proposal draft for arXiv:2602.08846
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Impredicative universes in linear dependent type theory}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.08846, "Impredicativity in Linear Dependent Type Theory" (2026-02-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Speight and van der Weide build a realizability model of linear dependent type theory from a linear combinatory algebra, motivating an impredicative universe with decoders to cartesian and linear types plus a modality-injectivity rule. With these additions they encode linear inductive types and prove uniqueness principles for list types.
\begin{enumerate}
  \item constructs the realizability model and justifies new rules;
  \item adds an impredicative universe closed under large cartesian and linear dependent products;
  \item introduces a modality injectivity rule from linear to cartesian terms; and
  \item encodes linear inductive types, exemplified by lists.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468712] Discussion on universes for linear dependent type theory.
  \item[MO 468730] Question on modality injectivity rules.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505360] "Realizability models of linear type theory".
  \item[Math.SE 505402] "Encoding inductive types in linear settings".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Linear dependent type theory.} Recap syntax/semantics (Math.SE 505360).
  \item \textbf{Realizability model.} Summarize the linear combinatory algebra construction.
  \item \textbf{Impredicative universe + modality.} Detail the new rules (MO 468712, MO 468730).
  \item \textbf{Inductive types.} Explain list encoding and uniqueness (Math.SE 505402).
  \item \textbf{PlanetMath links.} Connect to HoTT, linear logic, and realizability entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for rule statements.
  \item Pull MO embeddings (468712, 468730) and Math.SE embeddings (505360, 505402).
  \item Draft the PlanetMath entry emphasizing the new impredicative universal structure.
\end{itemize}
