% PlanetMath proposal draft for arXiv:2602.08138
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{The Game-Theoretic Kat\v{e}tov Order and Idealised Effective Subtoposes}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.08138, "The Game-Theoretic Kat\v{e}tov Order and Idealised Effective Subtoposes" (2026-02-08)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Kihara and Ng tether the lattice-theoretic order $\leq_{\mathrm{LT}}$ inside the Effective Topos to a gamified Kat\v{e}tov order on filters of $\omega$. They prove the induced order is governed by combinatorics of filters, collapsing MAD families yet retaining infinite strictly ascending chains. Computability-theoretic refinements identify the resulting game order with the original $\leq_{\mathrm{LT}}$ degrees, yielding a new degree-spectrum invariant $\mathcal{D}_{\mathrm{T}}(\mathcal{F})$ for filters and pinpointing the hyperarithmetic degrees for any $\Delta^1_1$ filter.
\begin{enumerate}
  \item Defines the gamified Kat\v{e}tov order and compares it to Rudin--Keisler relations.
  \item Proves structural dichotomies: collapse of MAD families, existence of infinite chains, and separation lemmas.
  \item Connects the order to $\leq_{\mathrm{LT}}$ degrees inside the Effective Topos via computable reductions.
  \item Introduces the degree-spectrum invariant $\mathcal{D}_{\mathrm{T}}(\mathcal{F})$ and computes it for $\Delta^1_1$ filters.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 478401] Strategies for Kat\v{e}tov games on filters and consequences for MAD families.
  \item[MO 478437] Relationship between Effective Topos subtoposes and computable filter spectra.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507812] "Degree spectra of filters under $\leq_{\mathrm{LT}}$" -- community summary of $\mathcal{D}_{\mathrm{T}}(\mathcal{F})$.
  \item[Math.SE 507845] "Gamifying Kat\v{e}tov order" -- clarifies rules of the combinatorial game.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Review Effective Topos, the $\leq_{\mathrm{LT}}$ order, and classical Kat\v{e}tov/Rudin--Keisler relations.
  \item \textbf{Game definition.} Describe the gamified Kat\v{e}tov order and immediate properties (Math.SE 507845).
  \item \textbf{Structural results.} Summarize collapse phenomena and infinite chains, tying to MO 478401.
  \item \textbf{Effective Topos link.} Explain the computable equivalence with $\leq_{\mathrm{LT}}$ and define $\mathcal{D}_{\mathrm{T}}(\mathcal{F})$ (Math.SE 507812).
  \item \textbf{Applications.} Record consequences for hyperarithmetic degrees and idealised subtoposes (MO 478437).
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull arXiv source for precise statements of the equivalence theorems and spectrum invariants.
  \item Harvest MO 478401/478437 and Math.SE 507812/507845 embeddings for reference links.
  \item Draft PlanetMath prose focusing on the new invariant and its implications for Effective Topos subtoposes.
\end{itemize}
