% PlanetMath proposal draft for arXiv:2602.22986
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Relative $Q$-shaped model structures}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.22986, "Relative $Q$-shaped homological algebra" (2026-02-26)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Slaftsos--Vit\'oria upgrade Holm--J\o rgensen's $Q$-shaped derived categories by building exact model structures on an exact category $(\mathcal{A},\mathscr{E})$ that track relative Gorenstein projectives. Changing the exact structure induces Bousfield (co)localisation sequences that interpolate between split, objectwise exact, and abelian contexts, yielding recollements for representation categories ${}_{Q,A}\operatorname{Mod}$.
\begin{enumerate}
  \item Define classes of relative Gorenstein projectives and the detecting cohomology functors yielding exact model structures on $(\mathcal{A},\mathscr{E})$.
  \item Compare these model structures via Bousfield (co)localisations on homotopy categories when the exact structure varies.
  \item Apply the machinery to ${}_{Q,A}\operatorname{Mod}$ for a small $\Bbbk$-linear $Q$ and ring $A$, covering split-to-abelian exact structures.
  \item Identify the Verdier quotient from the $Q$-shaped homotopy category to the $Q$-shaped derived category and exhibit recollement diagrams generalising Verdier/Krause/Iyama--Kato--Miyachi.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO: exact model structures] Threads on constructing Hovey triples for exact categories and detecting trivial cofibrations.
  \item[MO: $Q$-indexed derived categories] Discussions of Holm--J\o rgensen's $Q$-shaped derived categories and recollements.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE: relative Gorenstein projectives] Q\&A explaining how relative projectives behave in exact categories.
  \item[Math.SE: Bousfield localisations] Community notes on moving between model structures via localisation sequences.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Exact-categorical background.} Recall exact categories, Hovey triples, and relative Gorenstein projectives.
  \item \textbf{Model structures from $Q$-shapes.} Present the construction of exact model structures and the detecting cohomology functors.
  \item \textbf{Localisation ladders.} Explain how varying the exact structure produces Bousfield (co)localisations and recollements.
  \item \textbf{Representation examples.} Detail ${}_{Q,A}\mathrm{Mod}$ for split, objectwise exact, and abelian structures, highlighting concrete computations.
  \item \textbf{Verdier quotients.} Describe the quotient from the homotopy to the derived category and list consequences for PlanetMath entries on recollement.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Extract the precise hypotheses for the relative model structures and encode them in the PlanetMath glossary.
  \item Diagram the localisation tower comparing split, objectwise exact, and abelian structures for a sample quiver $Q$.
  \item Link to existing entries on recollement, Gorenstein projectives, and exact model categories.
\end{itemize}
