% PlanetMath proposal draft for arXiv:2602.14332
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Commutativity in Lawvere 2-theories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.14332, "$2$-dimensional Lawvere theories: commutativity and lax phenomena" (2026-02-15)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Perutka studies categorified algebraic structures via Lawvere 2-theories and enhanced 2-dimensional sketches, focusing on 2-dimensional commutativity. A commutative structure on a Lawvere 2-theory $\mathbb{T}$ yields a closed 2-multicategory structure on lax models $\mathsf{Mod}_l(\mathbb{T},\mathbf{Cat})$, leading to a Fox-type theorem and extensions to Lawvere $(\infty,2)$-theories.
\begin{enumerate}
  \item defines 2-dimensional commutativity for Lawvere 2-theories;
  \item proves $\mathsf{Mod}_l(\mathbb{T},\mathbf{Cat})$ is a closed 2-multicategory under commutativity;
  \item generalizes Fox's theorem; and
  \item discusses higher analogues and multicategory structures on hom-categories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 469700] Question on commutative Lawvere 2-theories.
  \item[MO 469735] Thread on closed 2-multicategory structures.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 506750] "Lawvere 2-theories and lax homomorphisms".
  \item[Math.SE 506788] "Fox's theorem for categorified algebra".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Lawvere 2-theories.} Review basics and models (Math.SE 506750).
  \item \textbf{Commutativity structure.} Present definitions and consequences (MO 469700).
  \item \textbf{Closed 2-multicategories.} Detail the structure on lax models (MO 469735).
  \item \textbf{Fox/generalizations.} State the generalized theorem (Math.SE 506788).
  \item \textbf{Higher analogues.} Mention extensions to $(\infty,2)$-theories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for rigorous statements.
  \item Fetch MO embeddings (469700, 469735) and Math.SE embeddings (506750, 506788).
  \item Draft the PlanetMath entry connecting to higher Lawvere theory entries.
\end{itemize}
