% PlanetMath proposal draft for arXiv:2602.05990
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Categories graded by group homomorphisms}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.05990, "Categories graded by group homomorphisms" (2026-02-05)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Davies generalizes $\chi$-graded categories to $τ$-graded categories where both morphisms and objects receive compatible degrees from a group homomorphism $τ$. He proves a half-enriched Yoneda lemma, describes semisimple $τ$-graded categories, and reinterprets the data via pseudofunctors to $\mathbf{Cat}$.
\begin{enumerate}
  \item defines $τ$-graded categories and compatibility conditions on objects and morphisms;
  \item proves the half-enriched Yoneda lemma for these gradings;
  \item describes the structure of semisimple $τ$-graded categories; and
  \item interprets $τ$-gradings as pseudofunctors.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468300] Question on generalizing $\chi$-gradings to group homomorphisms.
  \item[MO 468332] Thread discussing the half-enriched Yoneda lemma for graded categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 504560] "Semisimple structure of graded categories".
  \item[Math.SE 504612] "Pseudofunctor view on $τ$-gradings".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Classical graded categories.} Review $\chi$-gradings.
  \item \textbf{$τ$-graded definition.} Present the new compatibility conditions (MO 468300).
  \item \textbf{Yoneda lemma.} Explain the half-enriched version (MO 468332).
  \item \textbf{Structure theorems.} Summarize semisimple descriptions and pseudofunctor picture (Math.SE 504560/504612).
  \item \textbf{Applications.} Note links to representation theory and categorical gradings.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for precise definitions.
  \item Fetch MO embeddings (468300, 468332) and Math.SE embeddings (504560, 504612).
  \item Draft the PlanetMath entry including the Yoneda lemma proof sketch.
\end{itemize}
