% PlanetMath proposal draft for arXiv:2602.07604
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Free fibrations and Kan extensions for $(\infty,2)$-categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.07604, "Free fibrations, lax colimits and Kan extensions for $(\infty,2)$-categories" (2026-02-07)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Abellán, Haugseng, and Martini study fibrations of $(\infty,2)$-categories via pullback-characterized squares, construct free fibrations with prescribed (co)cartesian lifts, and apply the machinery to partially lax/weighted (co)limits and Kan extensions.
\begin{enumerate}
  \item characterizes fibrations of $(\infty,2)$-categories using pullback squares;
  \item constructs free fibrations with specified lifts and describes right adjoints to pullback;
  \item applies this to partially lax and weighted (co)limits; and
  \item develops partially lax Kan extensions and cofinality results.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468420] Question on defining fibrations of $(\infty,2)$-categories via pullbacks.
  \item[MO 468451] Discussion on partially lax Kan extensions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 504860] "Free fibrations for $(\infty,2)$".
  \item[Math.SE 504914] "Weighted colimits in $(\infty,2)$-categories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Fibration definitions.} Recount the pullback characterization (MO 468420).
  \item \textbf{Free fibrations.} Explain construction and adjointness.
  \item \textbf{Lax colimits/limits.} Describe partially lax and weighted versions (Math.SE 504914).
  \item \textbf{Kan extensions/cofinality.} Present resulting theorems (MO 468451).
  \item \textbf{PlanetMath links.} Connect to entries on $(\infty,2)$-categories and Kleisli-style fibrations.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for detailed constructions.
  \item Fetch MO embeddings (468420, 468451) and Math.SE embeddings (504860, 504914).
  \item Draft the PlanetMath article summarizing the fibrational viewpoint.
\end{itemize}
