% PlanetMath proposal draft for arXiv:2602.19315
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Exit weaving for constructible stacks}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19315, "Exit weaving for constructible stacks" (2026-02-21)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
The paper refines exit-path constructions for constructible stacks by introducing exit weaving data that records tangential smoothing across strata:
\begin{enumerate}
  \item define exit weaves as iterated spans of exit-path $\infty$-categories,
  \item use the weaves to build factorization charts on constructible stacks, and
  \item classify perverse schobers via the resulting span correspondences.
\end{enumerate}
PlanetMath focus: translate the new jargon into the PlanetMath dictionary, present a stratified 3-manifold example, and describe how span symmetries enforce compatibilities.
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467375] Constructible cosheaf discussion referencing exit-path spans.
  \item[MO 466359] Higher graph-coloring spans that mirror the weaving excision data.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 480112] "Exit-path $\infty$-groupoid of a cone" for a warm-up.
  \item[Math.SE 482764] "Factorization homology on a stratified sphere" to illustrate excision.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Review exit-path $\infty$-categories and constructible stacks.
  \item Define exit weaving and relate it to span correspondences.
  \item Explain the classification theorem for schobers.
  \item Work through the stratified 3-manifold example and cite MO/Math.SE.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Sync the arXiv source into futon6 proof-state for citation harvesting.
  \item Pull embeddings for MO 467375 and MO 466359 via storage/mo-processed-gpu.
  \item Fetch Math.SE embeddings for 480112 and 482764 via storage/math-processed-gpu.
  \item Draft the PlanetMath EDN + TeX pair per outline.
\end{itemize}
