% PlanetMath proposal draft for arXiv:2602.07604
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Free fibrations, lax colimits, and Kan extensions for $(\infty,2)$-categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.07604, Abell\'an--Haugseng--Martini, ``Free fibrations, lax colimits and Kan extensions for $(\infty,2)$-categories'' (2026-02-16)
  \item Cross-reference MO 447560 on pushforward of cocartesian fibrations; Math.SE 2661848 on defining $(\infty,2)$-categories and Kan extensions
\end{itemize}
\subsection*{Synopsis}
The paper develops a model-independent theory of fibrations in $(\infty,2)$-categories, treating decorated oplax arrow categories, partial fibrations, and lax colimits. Main contributions:
\begin{enumerate}
  \item Characterize $(0,1)$-fibrations via pullback squares in decorated oplax arrow categories, generalizing the orthogonality viewpoint.
  \item Construct free, cofree, and partially lax fibrations; describe right adjoints to pullback functors, answering MO 447560-type pushforward questions.
  \item Provide fibrational descriptions of weighted colimits, partially lax Kan extensions, and cofinality for $(\infty,2)$-categories, complementing Math.SE 2661848 discussions.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 447560] asks about pushing forward cocartesian fibrations; the authors’ right adjoint to pullback settles the $(\infty,2)$ analogue.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 2661848] seeks practical definitions of $(\infty,2)$-categories and Kan extensions; this paper supplies explicit fibrational models.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Decorated arrow categories.} Define $\mathcal{A}^\mathrm{oplax}$ and decorations marking cocartesian 1-morphisms/2-morphisms.
  \item \textbf{Partial $(\varepsilon)$-fibrations.} Explain the characterization via pullback squares; relate to orthogonality.
  \item \textbf{Free and cofree constructions.} Describe the adjunctions producing free fibrations and the right adjoint to pullback (MO 447560).
  \item \textbf{Lax colimits and Kan extensions.} Summarize fibrational formulas for partially lax/weighted colimits, citing Math.SE 2661848 motivation.
  \item \textbf{Applications.} Note cofinality, presentable $(\infty,2)$-categories, and interactions with enriched $\infty$-category theory.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Search \texttt{pm-full-dictionary.json} for ``$(\infty,2)$-category'' and ``Kan extension'' entries to coordinate terminology.
  \item Prepare diagrams illustrating the pullback characterization and the decorated Gray tensor product.
  \item Summarize the free/cofree adjunctions with explicit formulas for $\mathcal{A} \times_{\mathcal{B}} \mathrm{AR}^{\mathrm{oplax}}(\mathcal{B})$.
  \item Connect to PlanetMath articles on cocartesian fibrations, lax limits, and $(\infty,1)$-category theory to highlight upgrades.
\end{itemize}
