% PlanetMath proposal draft for arXiv:2602.23086
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Effectful toposes and Lawvere--Tierney modalities}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.23086, "Effectful toposes" (2026-02-26)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Birkedal--Letouzey--Munch-Maccagnoni introduce \emph{effectful toposes}: higher toposes equipped with evidenced geometric morphisms modelling computational effects. Lawvere--Tierney topologies classify such effects, and the authors show how Kripke--Joyal semantics internalises CPS translations, producing synthetic accounts of double-negation, exception, and probabilistic modalities.
\begin{enumerate}
  \item Define evidenced geometric morphisms and the axioms for an effectful topos.
  \item Develop the semantic/categorical correspondence between Lawvere--Tierney topologies, modalities, and effect handlers.
  \item Prove that classical CPS transforms and double-negation translations arise as specific effectful topologies.
  \item Work out sheafification procedures and coherence theorems ensuring the existence of effectful realizability models.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO: modalities in toposes] Threads on Lawvere--Tierney topologies and their computational interpretations.
  \item[MO: CPS via Kripke--Joyal] Discussions linking CPS translations to internal topos logic.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE: effect handlers categorically] Explanations of how algebraic effects become monads/modalities.
  \item[Math.SE: double-negation sheaves] Notes on when double-negation yields Boolean subtoposes.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Effectful topos axioms.} Present the definition and compare with the effective topos.
  \item \textbf{Lawvere--Tierney dictionary.} Map modalities/effects to topologies and describe the semantic pipeline.
  \item \textbf{CPS and translations.} Detail how standard CPS/double-negation translations are internalised.
  \item \textbf{Sheafification and realizability.} Summarize the existence theorems for effectful sheaves and their realizability semantics.
  \item \textbf{Examples + future work.} List exception, state, and probabilistic modalities with links to PlanetMath entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Extract the formal definition of evidenced geometric morphisms for reuse in PlanetMath.
  \item Create a table translating common programming effects into Lawvere--Tierney topologies.
  \item Cross-link to entries on realizability toposes, modalities, and CPS.
\end{itemize}
