% PlanetMath proposal draft for arXiv:2602.19422
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Cohesive operads and shape theory}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19422, "Cohesive operads and shape theory" (2026-02-21)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Cohesive operads live inside cohesive $\infty$-topoi and encode shape-theoretic invariants. The authors:
\begin{enumerate}
  \item define operads internal to a cohesive topos and explain how spans realize operations;
  \item prove a shape-invariance theorem comparing cohesive operads with classical Borsuk shape;
  \item relate the construction to condensed symmetry actions; and
  \item provide test cases based on condensed tori.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467871] Geometric group theory thread guiding the symmetry discussion.
  \item[MO 466991] Descriptive set-theory spans motivating shape invariants.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 486912] "What is a cohesive topos?"
  \item[Math.SE 495120] "Operads detecting shape invariants".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item Explain cohesive $\infty$-topoi and summarize Math.SE 486912.
  \item Define internal operads via spans and record the shape-invariance theorem.
  \item Compare with Borsuk shape and discuss condensed symmetry (MO 467871).
  \item Work through the condensed torus example and list the consequences for Galois actions.
\end{enumerate}
\subsection*{Action items}
Sync arXiv source, pull MO embeddings (467871, 466991), pull Math.SE embeddings (486912, 495120), then expand the PlanetMath entry accordingly.
