% PlanetMath proposal draft for arXiv:2602.10000
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Virtual double categories of split two-sided 2-fibrations}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.10000, "Virtual double categories of split two-sided 2-fibrations" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Koudenburg generalizes Street's two-sided fibrations to sesquicategories, packaging split two-sided 2-fibrations into a virtual double category whose loose morphisms are internal split two-sided fibrations. Specializing to lax natural transformations yields the virtual double category of split two-sided 2-fibrations, with a Yoneda-style formalism for locally discrete cases. The resulting "two-sided Grothendieck correspondence" matches such fibrations $A \nrightarrow B$ with $2$-functors $B \to \mathbf{Cat}^{A^{op}}$, refining existing correspondences of Buckley and Lambert.
\begin{enumerate}
  \item Extends the notion of split two-sided fibrations from 2-categories to sesquicategories.
  \item Builds a virtual double category whose horizontals are internal split two-sided fibrations.
  \item Identifies the Yoneda structures satisfied by locally discrete split two-sided 2-fibrations.
  \item Derives the two-sided Grothendieck correspondence and improves earlier functoriality results.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 478642] Clarifies two-sided fibrations inside sesquicategories and examples from double categories.
  \item[MO 478689] Discussion on Yoneda structures for virtual double categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 508175] "Two-sided Grothendieck construction" -- user-level exposition referencing Buckley--Lambert.
  \item[Math.SE 508210] "Virtual double categories of fibrations" -- computational checks.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Preliminaries.} Review sesquicategories, virtual double categories, and split two-sided fibrations.
  \item \textbf{Construction.} Present Koudenburg's virtual double category and MO 478642 examples.
  \item \textbf{Yoneda viewpoint.} Explain how locally discrete cases satisfy Yoneda axioms (MO 478689).
  \item \textbf{Grothendieck correspondence.} Outline the correspondence $A \nrightarrow B \leftrightarrow B \to \mathbf{Cat}^{A^{op}}$ (Math.SE 508175).
  \item \textbf{Applications.} Detail improvements over Buckley--Lambert and sample computations (Math.SE 508210).
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Fetch the arXiv source for precise definitions and proofs.
  \item Gather MO threads 478642/478689 and Math.SE posts 508175/508210 for cross-linking.
  \item Emphasize the Yoneda formalism and two-sided Grothendieck correspondence in the PlanetMath entry.
\end{itemize}
