% PlanetMath proposal draft for arXiv:2602.14332
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{$2$-dimensional Lawvere theories: commutativity and lax phenomena}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.14332, "$2$-dimensional Lawvere theories: commutativity and lax phenomena" (2026-02-15)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Tomáš Perutka develops Lawvere $2$-theories/enhanced sketches to study categorified algebraic structures with pseudo and lax homomorphisms. Introducing a notion of $2$-dimensional commutativity, he proves that $\mathsf{Mod}_l(\mathbb{T},\mathbf{Cat})$ admits a closed $2$-multicategory structure and extends Fox's theorem. Analogues for Lawvere $(\infty,2)$-theories produce multicategory structures on hom-categories in monoidal $(\infty,2)$-categories.
\begin{enumerate}
  \item Defines $2$-dimensional commutativity and Lawvere $2$-theory enhancements.
  \item Shows lax model categories form closed $2$-multicategories, generalising Fox.
  \item Extends constructions to Lawvere $(\infty,2)$-theories and $(\infty,2)$-operads.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 480305] Lax homomorphisms in Lawvere $2$-theories.
  \item[MO 480333] Multicategory structures on hom-categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 509895] "Examples of $2$-dimensional commutativity".
  \item[Math.SE 509921] "Fox theorem in categorified settings".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Lawvere $2$-theories.} Review setup and prior results (Math.SE 509895).
  \item \textbf{Commutativity notion.} Present Perutka's definition (MO 480305).
  \item \textbf{Closed $2$-multicategories.} Describe the structure on $\mathsf{Mod}_l$ (Math.SE 509921).
  \item \textbf{Higher extensions.} Outline the $(\infty,2)$-theory analogues (MO 480333).
  \item \textbf{Applications.} Mention categorified algebra examples benefiting from the framework.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv sections on commutativity definitions and closed $2$-multicategory proofs.
  \item Link MO 480305/480333 and Math.SE 509895/509921 discussions.
  \item Emphasise the generalised Fox theorem in PlanetMath.
\end{itemize}
