% PlanetMath proposal draft for arXiv:2602.15358
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Symmetry shifting for monoidal bicategories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.15358, "Symmetry shifting for monoidal bicategories" (2026-02-17)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Stenzel proves that any braided monoidal bicategory inherits a monoidal structure on its bicategory of monoids whose symmetry level upgrades (braided $\Rightarrow$ sylleptic, sylleptic $\Rightarrow$ symmetric). The proof leverages the $\infty$-operadic Additivity Theorem to bypass complicated coherence diagrams. Highlights:
\begin{enumerate}
  \item reformulates braidings on bicategories using operadic nerves to access the Additivity Theorem;
  \item equips the bicategory of monoids with a monoidal product compatible with the original braiding;
  \item tracks how syllepsis/symmetry propagates through the construction; and
  \item sketches examples coming from higher traces and cyclotomic structures.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468031] Discussion on when braided monoidal bicategories admit sylleptic refinements; provides references for the Additivity input.
  \item[MO 468115] Thread on coherence data for bicategory-of-monoids constructions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505812] "How do braided monoidal bicategories yield braided monoid categories?"
  \item[Math.SE 506090] "Tracing Joyal--Street's theorem in higher settings".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Recall braided/sylleptic/symmetric monoidal bicategories and summarize Math.SE 505812.
  \item \textbf{Operadic perspective.} Explain how the Additivity Theorem controls the bicategory-of-monoids construction, citing MO 468031.
  \item \textbf{Symmetry shifting theorem.} State the main upgrade result and relate it to Math.SE 506090.
  \item \textbf{Examples.} Detail the higher trace/cyclotomic examples from the paper and MO 468115.
  \item \textbf{PlanetMath cross-links.} Plan links to existing entries on monoidal bicategories, syllepsis, and traced monoidal bicategories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Ingest the arXiv source into futon6 for excerpts and references.
  \item Pull MO embeddings (468031, 468115) and Math.SE embeddings (505812, 506090).
  \item Draft the PlanetMath entry following the outline and note overlaps with earlier symmetry articles.
\end{itemize}
