% PlanetMath proposal draft for arXiv:2602.01761
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Auslander correspondence for connective DG-algebras}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.01761, "Auslander correspondence for proper connective DG-algebras via extended module categories" (2026-02-02)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Mochizuki proves a $d$-dimensional Auslander correspondence for $d$-truncated proper connective DG-algebras, phrased in terms of $d$-extended module categories. The endomorphism algebra of an additive generator is Auslander precisely when the $d$-extended module category is $d$-Auslander extriangulated.
\begin{enumerate}
  \item defines $d$-extended module categories and Auslander DG-algebras;
  \item proves the correspondence between DG-endomorphism algebras and Auslander algebras;
  \item shows every Auslander $d$-truncated DG-algebra arises this way; and
  \item illustrates examples with finitely many indecomposables.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 467720] Question on $d$-Auslander extriangulated categories arising from DG-algebras.
  \item[MO 467758] Discussion on extended module categories and Auslander correspondences.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 503765] "Examples of $d$-extended module categories".
  \item[Math.SE 503822] "Auslander correspondence in DG-settings".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Review DG-algebras, truncations, and $d$-extended module categories.
  \item \textbf{Auslander condition.} Define when the extended category is $d$-Auslander extriangulated (MO 467720).
  \item \textbf{Correspondence theorem.} Present the bijection between DG-endomorphism algebras and Auslander DG-algebras (MO 467758, Math.SE 503822).
  \item \textbf{Examples.} Work through finite indecomposable cases (Math.SE 503765).
  \item \textbf{PlanetMath links.} Connect to entries on Auslander--Reiten theory and extriangulated categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source and capture the main theorem proof.
  \item Pull MO embeddings (467720, 467758) and Math.SE embeddings (503765, 503822).
  \item Draft the PlanetMath entry emphasizing DG vs. extriangulated perspectives.
\end{itemize}
