% PlanetMath proposal draft for arXiv:2602.19532
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Warped Kan extensions for indexed $(\infty,1)$-categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.19532, "Warped Kan extensions for indexed $(\infty,1)$-categories" (2026-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Warped Kan extensions add span data to the usual Kan-extension calculus in an indexed $\infty$-category $\mathcal{E}\to \mathcal{B}$. The authors:
\begin{enumerate}
  \item package correspondences between fibers of $\mathcal{E}$ into a bicategory of spans;
  \item define warped left/right Kan extensions as coends over that bicategory;
  \item establish Beck--Chevalley and mate correspondences for the warped construction; and
  \item apply the machinery to parametrized spectra and $t$-structures.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 465935] Functional-analysis spans modeling norms, reused for Beck--Chevalley intuition.
  \item[MO 467211] Homotopy-theory thread on indexed categories ties into the parametrized spectrum example.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 503872] "Kan extensions for indexed categories".
  \item[Math.SE 505120] "Span-based Beck-Chevalley conditions".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Indexed foundations.} Review indexed $\infty$-categories, fiberwise Kan extensions, and the Math.SE 503872 primer to ground notation.
  \item \textbf{Warped span bicategory.} Construct the bicategory of spans between fibers, explain the extra ``warp'' data, and compare with the ordinary correspondence bicategory.
  \item \textbf{Warped Kan extensions.} Define warped left/right Kan extensions as coends over the span bicategory and spell out the universal properties.
  \item \textbf{Beck--Chevalley + mates.} Prove the Beck--Chevalley and mate correspondences, highlighting how MO 465935 and Math.SE 505120 motivate the calculus.
  \item \textbf{Applications.} Develop the parametrized spectra example (MO 467211), note the impact on $t$-structures/base-change, and list future PlanetMath cross-links.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Ingest the arXiv source and extract the precise definition of warped Kan extensions.
  \item Gather MO embeddings (465935, 467211) and Math.SE embeddings (503872, 505120) for reuse in the encyclopedia entry.
  \item Draft the entry following the outline and ensure the parametrized spectrum example is written out in detail.
\end{itemize}
