% PlanetMath proposal draft for arXiv:2602.06787
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Categorical Weisfeiler-Lehman frameworks}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.06787, "Weisfeiler and Lehman Go Categorical" (2026-02-06)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Choi, Kim, and Yun frame lifting maps as functors from arbitrary data categories to graded posets, producing categorical Weisfeiler-Lehman frameworks. Applied to hypergraphs, this yields hypergraph isomorphism networks whose topology is determined by the functor (incidence or symmetric simplicial), capturing complex intersection geometries and subsuming Hypergraph WL expressivity.
\begin{enumerate}
  \item formalizes lifting as a functor to graded posets;
  \item derives hypergraph isomorphism networks from incidence and symmetric simplicial functors;
  \item analyzes expressivity relative to Hypergraph WL; and
  \item validates on benchmarks.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470280] Thread on categorical views of Weisfeiler-Lehman.
  \item[MO 470318] Question on functorial hypergraph liftings.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507360] "Graded posets and lifting schemes".
  \item[Math.SE 507392] "Hypergraph WL expressivity".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Weisfeiler-Lehman basics.} Summarize classical WL (Math.SE 507392).
  \item \textbf{Categorical lifting.} Describe functorial setup (MO 470280).
  \item \textbf{Hypergraph functors.} Present incidence/symmetric constructions (MO 470318).
  \item \textbf{Expressivity + experiments.} Outline theoretical guarantees and benchmarks.
  \item \textbf{PlanetMath links.} Connect to categorical machine learning entries.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for definitions/proofs.
  \item Pull MO embeddings (470280, 470318) and Math.SE embeddings (507360, 507392).
  \item Draft the PlanetMath entry bridging WL theory and categorical ML.
\end{itemize}
