% PlanetMath proposal draft for arXiv:2602.09674
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Homotopical Dold-Kan for test categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09674, "A homotopical Dold-Kan correspondence for Joyal's category $Θ$ and other test categories" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Hubert proves that for any test category $A$ satisfying a compatibility between homology and weak equivalences, the homotopy category of abelian presheaves on $A$ matches the non-negative derived category of abelian groups. He introduces a model structure on abelian presheaves and shows it applies to Joyal's $Θ$.
\begin{enumerate}
  \item establishes criteria for the homotopical Dold-Kan correspondence on test categories;
  \item constructs a model structure on abelian presheaves under these conditions;
  \item deduces equivalence of homotopy categories with derived categories;
  \item specializes to Joyal's $Θ$.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 470150] Question on Dold-Kan for test categories.
  \item[MO 470188] Thread on model structures for abelian presheaves.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507230] "Joyal's $Θ$ and test categories".
  \item[Math.SE 507268] "Derived categories from abelian presheaves".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Test categories.} Summarize background (Math.SE 507230).
  \item \textbf{Compatibility condition.} Describe the homology vs. weak equivalence requirement (MO 470150).
  \item \textbf{Model structure.} Present the construction (MO 470188, Math.SE 507268).
  \item \textbf{Applications.} Highlight the case of $Θ$ and implications for Higher Topos Theory.
  \item \textbf{PlanetMath links.} Connect to classical Dold-Kan entries and test category references.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for detailed proofs.
  \item Pull MO embeddings (470150, 470188) and Math.SE embeddings (507230, 507268).
  \item Draft the PlanetMath entry summarizing the generalized correspondence.
\end{itemize}
