% PlanetMath proposal draft for arXiv:2602.09885
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Geometric differentiation of simplicial manifolds}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.09885, "Geometric differentiation of simplicial manifolds" (2026-02-10)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Cabrera and del Hoyo give a geometric solution to differentiating simplicial manifolds, extending Lie theory. They build compatible tubular neighborhoods, identify a differentiating ideal in cochains, produce a semi-free quotient as a Chevalley-Eilenberg algebra, and obtain higher Lie algebroids plus van Est theorems.
\begin{enumerate}
  \item constructs compatible tubular neighborhoods for simplicial manifolds;
  \item identifies the differentiating ideal in the cochain algebra and its semi-free quotient;
  \item interprets the quotient as the Chevalley-Eilenberg algebra of a higher Lie algebroid; and
  \item proves van Est isomorphism theorems and describes the Dold-Kan refinement.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 468910] Question on differentiating simplicial manifolds.
  \item[MO 468948] Thread on higher van Est maps.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 505690] "Tubular neighborhoods in simplicial manifolds".
  \item[Math.SE 505732] "Higher Lie algebroids from simplicial data".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Simplicial manifolds.} Review basics and motivation (Math.SE 505690).
  \item \textbf{Differentiating ideal.} Describe the construction and semi-free quotient (MO 468910).
  \item \textbf{Higher Lie algebroids.} Interpret the quotient (Math.SE 505732).
  \item \textbf{van Est theorem.} Present the higher version (MO 468948).
  \item \textbf{Dold-Kan refinement.} Explain the monoidal refinement viewpoint.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Pull the arXiv source for technical proofs and statements.
  \item Fetch MO embeddings (468910, 468948) and Math.SE embeddings (505690, 505732).
  \item Draft the PlanetMath entry linking to Lie groupoid/algebroid articles.
\end{itemize}
