% PlanetMath proposal draft for arXiv:2602.23218
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{$j$-translations and Kripke forcing in topos logic}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.23218, "A $j$-translation with Kripke forcing relation" (2026-02-26)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Awodey--Frey extend the standard $j$-translation (a Lawvere--Tierney modality) by equipping an elementary topos with an explicit Kripke forcing relation. The translation is sound for intuitionistic first-order logic and Heyting arithmetic, provides uniform Kripke semantics for semi-classical principles, and subsumes realizability/sheaf models built from a $j$-topology.
\begin{enumerate}
  \item Define the Kripke forcing relation associated to a Lawvere--Tierney topology $j$.
  \item Prove soundness/completeness for intuitionistic logic and Heyting arithmetic under the $j$-translation.
  \item Analyse semi-classical axioms (LLPO, WLEM, MP) within the forcing semantics.
  \item Compare with realizability/sheaf models to show the forcing construction generalises prior semantics.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO: Lawvere--Tierney forcing] Threads on interpreting topological modalities as forcing relations.
  \item[MO: Kripke models in toposes] Discussions on internal Kripke semantics for arithmetic.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE: $j$-topologies and logic] Questions about how Lawvere--Tierney topologies act on formulas.
  \item[Math.SE: semi-classical principles] Explanations of LLPO/WLEM/Markov's principle in constructive settings.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{$j$-translations.} Recall the definition and connection to modalities.
  \item \textbf{Kripke forcing relation.} Detail the categorical forcing relation and its properties.
  \item \textbf{Logical soundness.} Summarize the soundness/completeness proofs for logic and arithmetic.
  \item \textbf{Semi-classical analysis.} Record how LLPO, WLEM, and MP behave under $j$-forcing.
  \item \textbf{Comparison with realizability.} Explain how realizability/sheaf models emerge as special cases.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Formalize the forcing relation definition for reference snippets.
  \item Draft PlanetMath diagrams comparing Kripke frames induced by different $j$.
  \item Link to entries on Lawvere--Tierney topologies, forcing, and constructive arithmetic.
\end{itemize}
