% PlanetMath proposal draft for arXiv:2602.07604
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Free fibrations, lax colimits and Kan extensions for $(\infty,2)$-categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:2602.07604, "Free fibrations, lax colimits and Kan extensions for $(\infty,2)$-categories" (2026-02-07)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Abellán, Haugseng, and Martini give a fibration-centric toolkit for $(\infty,2)$-categories. They characterize fibrations by pullback squares, construct free fibrations admitting prescribed (co)cartesian lifts, and describe adjoints to restriction along partial fibrations. These ingredients feed into lax/oplax (co)limit constructions and Kan extensions in a model-independent fashion, yielding cofinality statements and presentations of presentable $(\infty,2)$-categories as accessible localizations.
\begin{enumerate}
  \item Characterizes fibrations of $(\infty,2)$-categories via a universal pullback property.
  \item Builds free fibrations with constrained lift data and identifies adjoints to restriction functors.
  \item Develops fibrational descriptions of lax, oplax, and weighted (co)limits plus partially lax Kan extensions.
  \item Applies the machinery to cofinality and presentability results for $(\infty,2)$-categories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 478265] Examples of free $(\infty,2)$-fibrations generated by specified lifts.
  \item[MO 478312] Discussion of fibrational criteria for lax Kan extensions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 507588] "Cofinality for $(\infty,2)$-categories" -- user intuition aligning with the paper's corollaries.
  \item[Math.SE 507634] "Weighted lax colimits vs. fibrations" -- computational examples.
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Recollect definitions of $(\infty,2)$-categories, fibrations, and partial lift data.
  \item \textbf{Free fibrations.} Describe the pullback characterization and construction (MO 478265).
  \item \textbf{Lax (co)limits.} Explain the fibrational description and consequences for Kan extensions (MO 478312).
  \item \textbf{Cofinality.} Connect to Math.SE 507588 and applications to presentable $(\infty,2)$-categories.
  \item \textbf{Examples.} Work through weighted diagram computations from Math.SE 507634.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source, focusing on Sections 1--3 for the fibration toolkit and Section 4 for applications.
  \item Link MO threads 478265/478312 and Math.SE references 507588/507634 in the PlanetMath entry.
  \item Illustrate at least one accessible localization example derived from the authors' cofinality theorem.
\end{itemize}
