% PlanetMath proposal draft for arXiv:math/9907150
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Higher dimensional hypercategories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9907150, "Higher dimensional hypercategories" (1999-07-24)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Higuchi, Miyoshi, and Tsujishita generalize opetopic sets and multigraphs via higher-dimensional hypergraphs built from shells and formal composites. They define strict hypercategories, weak $ω$-hypercategories, and illustrate the framework with Lafont's interaction combinator.
\begin{enumerate}
  \item Introduces shells and formal composites to build hypergraphs.
  \item Defines strict and weak hypercategories.
  \item Shows usual categories embed as special weak hypercategories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 484551] Hypergraphs generalizing opetopes.
  \item[MO 484578] Weak $ω$-hypercategories and examples.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 514390] "Shells and hypergraphs".
  \item[Math.SE 514417] "Strict vs. weak hypercategories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Motivation.} Compare opetopes/multigraphs (Math.SE 514390).
  \item \textbf{Shells.} Describe combinatorial structure (MO 484551).
  \item \textbf{Hypercategories.} Define strict/weak versions (Math.SE 514417).
  \item \textbf{Examples.} Mention interaction combinator, usual categories.
  \item \textbf{Outlook.} Note planned follow-up papers.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv details on shells and hypercategories.
  \item Link MO 484551/484578 and Math.SE 514390/514417.
  \item Emphasize how hypercategories generalize opetopes and categories.
\end{itemize}
