% PlanetMath proposal draft for arXiv:math/9904073
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{A canonical Tannaka duality for finite semisimple tensor categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9904073, "A canonical Tannaka duality for finite semisimple tensor categories" (1999-04-15)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Hayashi associates to each finite semisimple tensor category a quantum group (face algebra) whose comodules recover the category, generalizing Tannaka-Krein by embedding the tensor category into bimodules.
\begin{enumerate}
  \item Constructs face algebras canonically from finite semisimple tensor categories.
  \item Demonstrates equivalence between comodules and the original category.
  \item Generalizes Tannaka-Krein duality via bimodule embeddings.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483878] Face algebras and Tannaka duality.
  \item[MO 483905] Embedding tensor categories into bimodules.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 513573] "Quantum groups attached to tensor categories".
  \item[Math.SE 513599] "Canonical Tannaka reconstruction".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Tensor categories.} Review finite semisimple case (Math.SE 513573).
  \item \textbf{Face algebras.} Describe construction (MO 483878).
  \item \textbf{Comodule equivalence.} Explain equivalence (Math.SE 513599).
  \item \textbf{Generalization.} Show relation to Tannaka-Krein (MO 483905).
  \item \textbf{Examples.} Mention typical categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv details on face algebra construction and equivalence proof.
  \item Link MO 483878/483905 and Math.SE 513573/513599.
  \item Highlight canonical Tannaka duality for PlanetMath.
\end{itemize}
