% PlanetMath proposal draft for arXiv:math/9901139
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Generalized enrichment for categories and multicategories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9901139, "Generalized Enrichment for Categories and Multicategories" (1999-01-29)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Tom Leinster answers what sort of structures general multicategories can be enriched in: an $(n)$-type multicategory can be enriched in one level up. In particular, ordinary categories can be enriched in fc-multicategories (encompassing monoidal categories, multicategories, bicategories, and double categories), clarifying relaxed multicategories of Borcherds and Soibelman.
\begin{enumerate}
  \item Describes enrichment of multicategories in higher-level multicategories.
  \item Shows categories can be enriched in fc-multicategories.
  \item Explains relaxed multicategories via this framework.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483660] Multicategory enrichment across levels.
  \item[MO 483687] fc-multicategories and relaxed multicategories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 513339] "Enriching categories in fc-multicategories".
  \item[Math.SE 513365] "General multicategory enrichment".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Question.} Motivate generalized enrichment (Math.SE 513365).
  \item \textbf{Higher-type enrichment.} Summarize main theorem (MO 483660).
  \item \textbf{fc-multicategory enrichment.} Detail category case (Math.SE 513339).
  \item \textbf{Relaxed multicategories.} Connect to Borcherds/Soibelman (MO 483687).
  \item \textbf{Future work.} Note directions for multicategory towers.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import sections of the arXiv paper covering the general enrichment theorem.
  \item Link MO 483660/483687 and Math.SE 513339/513365.
  \item Emphasize fc-multicategory enrichment as a unifying perspective.
\end{itemize}
