% PlanetMath proposal draft for arXiv:math/0001146
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu + math-processed-gpu
\section*{Interchanging homotopy limits and colimits in CAT}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/0001146, "Interchanging homotopy limits and colimits in CAT" (2000-01-26)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Cortiñas proves that for a functor $C:I\times J\to \CAT$, if $I$ has a final object then $\mathrm{hocolim}_J\mathrm{holim}_I C \simeq \mathrm{holim}_I\mathrm{hocolim}_JP$ via strong homotopy equivalence.
\begin{enumerate}
  \item States the interchange theorem for homotopy limits/colimits in CAT.
  \item Provides proof using categorical homotopy techniques.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 485586] Interchanging homotopy limits/colimits.
  \item[MO 485613] Final objects and CAT homotopy equivalences.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 515489] "When do homotopy limits commute with colimits?".
  \item[Math.SE 515515] "Examples in CAT".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Setup.} Describe functors $C:I\times J\to \CAT$ (Math.SE 515489).
  \item \textbf{Final object condition.} Explain role (MO 485613).
  \item \textbf{Interchange theorem.} State equivalence (MO 485586).
  \item \textbf{Applications.} Mention calculations in categorical homotopy theory.
  \item \textbf{Examples.} Provide simple diagrams.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv proof and examples.
  \item Link MO 485586/485613 and Math.SE 515489/515515.
  \item Emphasize the strong homotopy equivalence result.
\end{itemize}
