% PlanetMath proposal draft for arXiv:math/9901091
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{$K$-Theory for Triangulated Categories III(A): The Theorem of the Heart}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9901091, "$K$-Theory for Triangulated Categories III(A): The Theorem of the Heart" (1999-01-21)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Amnon Neeman continues his series on $K$-theory of triangulated categories, focusing on attaching a $K$-theory space via the theorem of the heart.
\begin{enumerate}
  \item Reviews attaching $K$-theory to triangulated categories.
  \item Explains the theorem of the heart in this context.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483278] Theorem of the heart for triangulated categories.
  \item[MO 483305] $K$-theory constructions in Neeman's series.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512947] "Understanding Neeman's theorem of the heart".
  \item[Math.SE 512973] "$K$-spaces of triangulated categories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Summarize previous installments (Math.SE 512947).
  \item \textbf{Theorem of the heart.} Present main statement (MO 483278).
  \item \textbf{$K$-space attachment.} Explain construction (MO 483305, Math.SE 512973).
  \item \textbf{Examples.} Mention typical triangulated categories.
  \item \textbf{Applications.} Note how this informs categorical $K$-theory.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import relevant sections of the arXiv paper for definitions and theorem statements.
  \item Link MO 483278/483305 and Math.SE 512947/512973.
  \item Emphasize the role of the heart in building $K$-spaces.
\end{itemize}
