% PlanetMath proposal draft for arXiv:math/9503217
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Existence of Orbifolds IV: Examples}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9503217, "Existence of Orbifolds IV: Examples" (1995-03-14)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Paul Feit concludes a series on orbifolds and stacks by presenting explicit examples: orbifolds derived from manifolds, descriptions of their topological base spaces, and how categorical axioms manifest concretely.
\begin{enumerate}
  \item Applies the developed theory to orbifolds obtained from manifolds.
  \item Explains manipulation of associated topological base spaces.
  \item Interprets categorical axioms in explicit contexts.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483002] Examples of orbifolds derived from manifolds.
  \item[MO 483029] Translating orbifold axioms into concrete topology.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512598] "Working through Feit's orbifold examples".
  \item[Math.SE 512624] "Stack-theoretic description of orbifold base spaces".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Summarize previous parts of Feit's series (Math.SE 512598).
  \item \textbf{Manifold-derived orbifolds.} Detail examples (MO 483002).
  \item \textbf{Topological base spaces.} Explain manipulations (Math.SE 512624).
  \item \textbf{Categorical interpretation.} Link axioms to explicit cases (MO 483029).
  \item \textbf{Applications.} Point to geometry and stacky topologies.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv paper for detailed manifold-based orbifold constructions.
  \item Link MO 483002/483029 and Math.SE 512598/512624.
  \item Emphasize concrete orbifold manipulations.
\end{itemize}
