% PlanetMath proposal draft for arXiv:math/9802029
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Categorification}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9802029, "Categorification" (1998-02-05)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Baez and Dolan survey categorification: replacing sets with categories, functions with functors, and equations with coherent natural isomorphisms. They discuss $n$-categories, tangle/cobordism examples, and operadic definitions of weak $n$-categories.
\begin{enumerate}
  \item Introduces categorification and $n$-categories.
  \item Highlights examples (tangles, cobordisms, homotopy types).
  \item Sketches operadic approaches to weak $n$-categories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 481002] Historical development of categorification.
  \item[MO 481029] Operadic definitions of weak $n$-categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 510611] "Beginner examples of categorification".
  \item[Math.SE 510639] "Operads and weak $n$-categories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Concept.} Define categorification and coherence (Math.SE 510611).
  \item \textbf{n-categories.} Summarize structures and homotopy links (MO 481002).
  \item \textbf{Examples.} Detail tangle/cobordism/homotopy categorifications.
  \item \textbf{Operadic definitions.} Outline Baez-Dolan approach (MO 481029, Math.SE 510639).
  \item \textbf{Applications.} Point to quantum invariants and loop spaces.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for definitions and examples.
  \item Reference MO 481002/481029 and Math.SE 510611/510639 threads.
  \item Emphasize operadic weak $n$-category definitions.
\end{itemize}
