% PlanetMath proposal draft for arXiv:math/9910135
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{C*-tensor categories and free product bimodules}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9910135, "C*-tensor categories and free product bimodules" (1999-10-26)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Yamagami shows a C*-tensor category with simple unit is realizable by von Neumann algebra bimodules of finite Jones index iff it is rigid.
\begin{enumerate}
  \item States rigidity criterion for realizing C*-tensor categories via bimodules.
  \item Uses finite Jones index and free product bimodules.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 485124] Realizing tensor categories with bimodules.
  \item[MO 485151] Rigidity and Jones index conditions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 514968] "Rigid C*-tensor categories".
  \item[Math.SE 514994] "Jones index and bimodule realizations".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{C*-tensor categories.} Review rigidity/simple unit (Math.SE 514968).
  \item \textbf{Bimodule realization.} Outline free product bimodule approach (MO 485124).
  \item \textbf{Jones index.} Explain role in criterion (MO 485151, Math.SE 514994).
  \item \textbf{Examples.} Provide sample categories.
  \item \textbf{Applications.} Mention operator algebra representations.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv results on rigidity and bimodule realizations.
  \item Link MO 485124/485151 and Math.SE 514968/514994.
  \item Emphasize connection between tensor categories and operator algebras.
\end{itemize}
