% PlanetMath proposal draft for arXiv:math/9811139
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Higher-Dimensional Algebra IV: 2-Tangles}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9811139, "Higher-Dimensional Algebra IV: 2-Tangles" (1998-11-24)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Baez and Langford describe 2-category models of 2-tangles (embedded surfaces in $
 R^4$), showing the 2-category is the free semistrict braided monoidal 2-category with duals on one unframed self-dual object. This yields invariants from any such object.
\begin{enumerate}
  \item Constructs the 2-category of 2-tangles with objects/morphisms/2-morphisms.
  \item Proves the universal property (free semistrict braided monoidal 2-category with duals).
  \item Explains how self-dual objects produce invariants.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482685] 2-tangles and braided monoidal 2-categories.
  \item[MO 482712] Duals/self-dual objects yielding invariants.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512304] "Understanding the 2-category of 2-tangles".
  \item[Math.SE 512330] "Semistrict braided monoidal 2-categories with duals".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{2-tangles.} Define surfaces and categories (Math.SE 512304).
  \item \textbf{2-category structure.} Explain compositions and duals (MO 482685).
  \item \textbf{Universal property.} State free semistrict characterization (Math.SE 512330).
  \item \textbf{Invariants.} Describe how objects give invariants (MO 482712).
  \item \textbf{Examples.} Mention relations to Crane-Yetter style invariants.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for category construction and universal property.
  \item Link MO 482685/482712 and Math.SE 512304/512330.
  \item Highlight interplay between 2-tangles and braided monoidal 2-categories.
\end{itemize}
