% PlanetMath proposal draft for arXiv:math/9809104
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Monoidal categories and multiextensions}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9809104, "Monoidal categories and multiextensions" (1998-09-18)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Breen identifies the obstruction to a strict symmetric monoidal structure on a monoidal stack $\mathcal{C}$ via a commutator biextension, alternating under extra hypotheses. He extends the construction to monoidal 2-stacks and generalizes biextensions.
\begin{enumerate}
  \item Associates commutator biextensions to monoidal stacks.
  \item Shows alternating behavior leading to symmetric structures.
  \item Extends to monoidal 2-stacks with generalized biextensions.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482315] Obstructions to symmetric structures via biextensions.
  \item[MO 482342] Monoidal 2-stack multiextensions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 511935] "Commutator biextensions of monoidal categories".
  \item[Math.SE 511962] "Symmetric structures on monoidal stacks".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Monoidal stacks.} Review data and obstructions (Math.SE 511935).
  \item \textbf{Biextensions.} Describe commutator biextension construction (MO 482315).
  \item \textbf{Symmetry.} Explain alternating condition and symmetric structures (Math.SE 511962).
  \item \textbf{2-stacks.} Outline extensions to monoidal 2-stacks (MO 482342).
  \item \textbf{Applications.} Mention relations to Picard stacks.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for biextension definitions and obstruction theory.
  \item Link MO 482315/482342 and Math.SE 511935/511962.
  \item Emphasize biextension viewpoint in PlanetMath entry.
\end{itemize}
