% PlanetMath proposal draft for arXiv:math/9805102
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Nuclear and trace ideals in tensored $*$-categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9805102, "Nuclear and Trace Ideals in Tensored $*$-Categories" (1998-05-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Abramsky, Blute, and Panangaden generalize nuclear maps to ``nuclear ideals'' inside tensored $*$-categories, motivated by probabilistic relations. They define nuclear and trace ideals, relate them to compact closed structure, and exhibit categories where integration acts as composition. The work extends Joyal-Street-Verity traces to ideals.
\begin{enumerate}
  \item Defines nuclear ideals and examples (tame distributions, probabilistic relations).
  \item Connects nuclear ideals to trace ideals and compact closure.
  \item Extends traced monoidal notions to ideal-defined traces.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 481802] Nuclear ideals in tensored $*$-categories.
  \item[MO 481828] Trace ideals vs. Hilbert-Schmidt operators.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 511412] "Probabilistic relations as nuclear morphisms".
  \item[Math.SE 511439] "Traces on ideals".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Motivation.} Compare compact closed vs. probabilistic categories (Math.SE 511412).
  \item \textbf{Nuclear ideals.} Present definitions/examples (MO 481802).
  \item \textbf{Trace ideals.} Outline correspondence with nuclear ideals (MO 481828, Math.SE 511439).
  \item \textbf{Applications.} Mention tame distributions and probabilistic relations.
  \item \textbf{Traces.} Discuss ideal-based trace axioms extending JSV.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv source describing nuclear/trace ideals and examples.
  \item Link MO 481802/481828 and Math.SE 511412/511439.
  \item Emphasize probabilistic relation motivation in PlanetMath entry.
\end{itemize}
