% PlanetMath proposal draft for arXiv:math/9906038
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{On categorification}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9906038, "On Categorification" (1999-06-06)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Lucian Ionescu surveys categorification procedures and introduces a functorial categorification of group extensions with applications to nonabelian group cohomology. He also mentions categorification of acyclic models and spaces.
\begin{enumerate}
  \item Reviews existing categorification techniques.
  \item Presents functorial categorification of group extensions and nonabelian cohomology.
  \item Notes categorification of acyclic models/topological spaces.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 484231] Categorifying group extensions.
  \item[MO 484258] Categorification surveys.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 514009] "Functorial categorification examples".
  \item[Math.SE 514035] "Categorification and nonabelian cohomology".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Survey.} Summarize known categorifications (MO 484258).
  \item \textbf{Group extensions.} Detail functorial categorification (Math.SE 514035, MO 484231).
  \item \textbf{Acyclic/topological models.} Mention further directions.
  \item \textbf{Applications.} Relate to nonabelian cohomology.
  \item \textbf{Examples.} Provide sample extensions.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import sections on categorification procedures and group extensions.
  \item Link MO 484231/484258 and Math.SE 514009/514035.
  \item Emphasize new functorial categorification in PlanetMath entry.
\end{itemize}
