% PlanetMath proposal draft for arXiv:math/9811109
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Adelic Chern Forms and Applications}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9811109, "Adelic Chern Forms and Applications" (1998-11-18)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Huebl and Yekutieli construct adelic Chern forms $c_i(E;\nabla)$ in Beilinson adele sheaves for vector bundles with adelic connections on characteristic-0 varieties. When the variety is smooth, these represent usual Chern classes in algebraic de Rham cohomology. Applications include adelic Chern-Simons classes, Bott residue formula for vector fields, and a Gauss-Bonnet formula in the de Rham-residue complex.
\begin{enumerate}
  \item Defines adelic connections and associated Chern forms.
  \item Shows compatibility with algebraic de Rham cohomology.
  \item Applies to Chern-Simons classes, Bott residue, and Gauss-Bonnet.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482612] Adelic connections and Chern forms.
  \item[MO 482639] Bott residue via adelic methods.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512232] "Working with Beilinson adeles".
  \item[Math.SE 512258] "Adelic Gauss-Bonnet formula".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Adeles.} Introduce Beilinson adele complexes (Math.SE 512232).
  \item \textbf{Adelic connections.} Define and explain constructions (MO 482612).
  \item \textbf{Chern forms.} Relate to de Rham classes.
  \item \textbf{Applications.} Summarize Chern-Simons, Bott residue, Gauss-Bonnet (MO 482639, Math.SE 512258).
  \item \textbf{Examples.} Provide sample vector bundles.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for definitions and application proofs.
  \item Link MO 482612/482639 and Math.SE 512232/512258.
  \item Highlight adelic techniques for characteristic class computations.
\end{itemize}
