% PlanetMath proposal draft for arXiv:math/9812097
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Applications of rewriting systems and Gr"obner bases to computing Kan extensions}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9812097, "Applications of Rewriting Systems and Groebner Bases to Computing Kan Extensions and Identities Among Relations" (1998-12-17)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Heyworth develops rewriting/Groebner methods for combinatorial problems phrased as Kan extensions. Knuth-Bendix is shown to be a special case of Buchberger's algorithm, connections to automata/petri nets are drawn, and completion techniques compute identities among relations via contracting homotopies.
\begin{enumerate}
  \item Applies rewrite systems to Kan extensions and combinatorial problems.
  \item Relates Knuth-Bendix and Buchberger algorithms.
  \item Uses completions to compute identities among relations through contracting homotopies.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482851] Rewriting approaches to Kan extensions.
  \item[MO 482878] Identities among relations via completion.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512449] "Buchberger vs. Knuth-Bendix".
  \item[Math.SE 512476] "Computing contracting homotopies via rewriting".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Kan extensions.} Explain combinatorial framing (Math.SE 512449).
  \item \textbf{Rewriting machinery.} Summarize algorithms and equivalence (MO 482851).
  \item \textbf{Automata/Petri nets.} Mention reduction machines.
  \item \textbf{Identities among relations.} Outline contracting homotopy computation (MO 482878, Math.SE 512476).
  \item \textbf{Implementation.} Note GAP3 scripts from thesis.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv thesis for algorithm descriptions and case studies.
  \item Link MO 482851/482878 and Math.SE 512449/512476.
  \item Highlight rewriting-Groebner synergy for Kan extensions.
\end{itemize}
