% PlanetMath proposal draft for arXiv:math/9810059
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Homotopy types of strict 3-groupoids}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9810059, "Homotopy types of strict 3-groupoids" (1998-10-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Carlos Simpson shows strict $n$-groupoids (with a realization functor compatible with homotopy groups) cannot model the $n$-type of $S^2$ when $n\ge 3$, highlighting limits of strictness. He suggests introducing ``snucategories''—strictly associative $n$-categories with weak units—to address the issue.
\begin{enumerate}
  \item Demonstrates non-realizability of $S^2$ $n$-types by strict $n$-groupoids.
  \item Explains necessary properties of realization functors.
  \item Proposes snucategories as a remedy.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 481964] Limits of strict $n$-groupoids for homotopy types.
  \item[MO 481991] Snucategories and weak units.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 511585] "Why strict 3-groupoids miss $S^2$".
  \item[Math.SE 511611] "What are snucategories?".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Strict $n$-groupoids.} Define and recall realization functors (Math.SE 511585).
  \item \textbf{Obstruction.} Summarize Simpson's argument (MO 481964).
  \item \textbf{Snucategories.} Introduce proposal for weak units (MO 481991, Math.SE 511611).
  \item \textbf{Implications.} Discuss modeling homotopy types.
  \item \textbf{Future work.} Outline open problems.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv argument and snucategory discussion.
  \item Link MO 481964/481991 and Math.SE 511585/511611.
  \item Emphasize limitations of strict models in PlanetMath entry.
\end{itemize}
