% PlanetMath proposal draft for arXiv:math/9912075
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu + math-processed-gpu
\section*{Relaxed multicategory structure of a global category of rings and modules}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9912075, "Relaxed multi category structure of a global category of rings and modules" (1999-12-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Snydal endows a global category of rings/modules with a relaxed multicategory structure, with algebras in this setting recovering vertex algebras.
\begin{enumerate}
  \item Constructs relaxed multicategory on global rings/modules.
  \item Shows certain algebras yield vertex algebra structures.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 485786] Relaxed multicategories for rings/modules.
  \item[MO 485813] Vertex algebras from relaxed multicategories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 515711] "Global category of rings/modules".
  \item[Math.SE 515737] "Relaxed multicategory algebras".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Global category.} Describe objects/morphisms (Math.SE 515711).
  \item \textbf{Relaxed multicategory.} Explain structure (MO 485786).
  \item \textbf{Algebras.} Show vertex algebra emergence (MO 485813, Math.SE 515737).
  \item \textbf{Examples.} Provide simple ring/module instances.
  \item \textbf{Applications.} Mention connections to vertex algebra theory.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv details on relaxed multicategory structure.
  \item Link MO 485786/485813 and Math.SE 515711/515737.
  \item Emphasize vertex algebra realization.
\end{itemize}
