% PlanetMath proposal draft for arXiv:math/0002180
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu + math-processed-gpu
\section*{Homotopy algebras for operads}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/0002180, "Homotopy Algebras for Operads" (2000-02-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Leinster defines homotopy algebras for operads in monoidal categories equipped with designated homotopy equivalences, providing examples (loop spaces, $A_\infty$-structures, enriched categories) and change-of-base results.
\begin{enumerate}
  \item Gives general definition of homotopy $P$-algebra for operad $P$.
  \item Provides examples: loop spaces, $n$-fold homotopy monoids, enriched categories.
  \item Discusses change-of-base behavior.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 485933] Homotopy algebras for operads.
  \item[MO 485960] Examples of homotopy monoids.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 515853] "Definition of homotopy algebra for an operad".
  \item[Math.SE 515879] "Loop spaces as homotopy monoids".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Setup.} Monoidal categories with homotopy equivalences (Math.SE 515853).
  \item \textbf{Definition.} Detail homotopy $P$-algebras (MO 485933).
  \item \textbf{Examples.} Present loop space cases (Math.SE 515879, MO 485960).
  \item \textbf{Change of base.} Summarize base-change results.
  \item \textbf{Advantages/limitations.} Note discussion on future infinity-categorical refinements.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv definition and examples.
  \item Link MO 485933/485960 and Math.SE 515853/515879.
  \item Emphasize loop spaces and homotopy monoids as key examples.
\end{itemize}
