% PlanetMath proposal draft for arXiv:math/9903004
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{fc-multicategories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9903004, "fc-multicategories" (1999-02-28)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Tom Leinster introduces fc-multicategories, unifying bicategories, monoidal categories, double categories, and multicategories. He shows how fc-multicategories naturally support bimodule constructions and enrichment.
\begin{enumerate}
  \item Defines fc-multicategories as general two-dimensional structures.
  \item Explains bimodule constructions within fc-multicategories.
  \item Develops enrichment theory over fc-multicategories.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483499] fc-multicategory definitions.
  \item[MO 483526] Enrichment over fc-multicategories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 513200] "Examples of fc-multicategories".
  \item[Math.SE 513226] "Bimodules in fc-multicategories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Definition.} Present data and axioms (Math.SE 513200).
  \item \textbf{Examples.} Relate bicategories, double categories, multicategories.
  \item \textbf{Bimodules.} Describe constructions (Math.SE 513226).
  \item \textbf{Enrichment.} Explain enrichment theory (MO 483526).
  \item \textbf{Future work.} Mention larger phenomena.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv paper for definitions and examples.
  \item Link MO 483499/483526 and Math.SE 513200/513226.
  \item Emphasize fc-multicategories as a unifying framework.
\end{itemize}
