% PlanetMath proposal draft for arXiv:math/9804106
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Obstructions to Coherence: Natural Noncoherent Associativity}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9804106, "Obstructions to Coherence: Natural Noncoherent Associativity" (1998-04-22)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Yanofsky studies associative categories lacking pentagon coherence, constructing Catalan groupoids $\mathcal{A}_n$ where naturality squares commute but pentagons fail. Fundamental groups $\pi(\mathcal{A}_n)$ measure obstruction classes, yielding a theory of associative categories and criteria for coherence.
\begin{enumerate}
  \item Defines associative categories and Catalan groupoids.
  \item Computes fundamental groups $\pi(\mathcal{A}_n)$, describing generators/relations.
  \item Identifies obstructions to coherence via images of $\pi(P_n)$.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 481085] Noncoherent associativity diagrams.
  \item[MO 481112] Catalan groupoids and obstruction classes.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 510702] "Associative categories without pentagon coherence".
  \item[Math.SE 510729] "Computing $\pi(\mathcal{A}_n)$".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Associative categories.} Review definitions (Math.SE 510702).
  \item \textbf{Catalan groupoids.} Describe construction (MO 481085).
  \item \textbf{Obstructions.} Explain $\pi(\mathcal{A}_n)$ and homomorphisms $\pi(P_n)$ (Math.SE 510729, MO 481112).
  \item \textbf{Coherence tests.} Summarize when obstructions vanish.
  \item \textbf{Examples.} Provide noncoherent monoidal categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for constructions and obstruction theory.
  \item Link MO 481085/481112 and Math.SE 510702/510729.
  \item Highlight Catalan groupoid viewpoint in PlanetMath.
\end{itemize}
