% PlanetMath proposal draft for arXiv:math/9810053
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{General operads and multicategories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9810053, "General Operads and Multicategories" (1998-10-08)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Leinster introduces $(S,*)$-multicategories built from a monad $*$ on a category $S$, encompassing many notions of operad/multicategory. He describes algebras for these multicategories and shows how the framework captures opetopes and Batanin operads.
\begin{enumerate}
  \item Defines $(S,*)$-multicategories and conditions on $S$.
  \item Describes algebras and demonstrates unifying power.
  \item Applies to opetopes/Batanin operads.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 481885] Comparing operad definitions via monads.
  \item[MO 481911] $(S,*)$-multicategory algebras.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 511506] "Examples of $(S,*)$-multicategories".
  \item[Math.SE 511532] "Opetopes through Leinster's framework".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Framework.} Present $(S,*)$-multicategories (Math.SE 511506).
  \item \textbf{Algebras.} Explain associated algebra notions (MO 481911).
  \item \textbf{Examples.} Show recovery of classical operads (MO 481885).
  \item \textbf{Opetopes.} Outline concise description (Math.SE 511532).
  \item \textbf{Further work.} Mention tentative developments.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv content on definitions/algebras/examples.
  \item Link MO 481885/481911 and Math.SE 511506/511532.
  \item Highlight unification of operad notions in PlanetMath entry.
\end{itemize}
