% PlanetMath proposal draft for arXiv:math/9808111
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Spaces of maps into classifying spaces for equivariant crossed complexes, II}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9808111, "Spaces of maps into classifying spaces for equivariant crossed complexes, II" (1998-08-27)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Brown, Golasiński, Porter, and Tonks generalize equivariant homotopy theory of crossed complexes from discrete to topological groups. Using homotopy coherence and Eilenberg-Zilber theory, they classify equivariant maps and describe weak equivariant homotopy types of mapping spaces.
\begin{enumerate}
  \item Extends equivariant crossed complex theory to topological groups.
  \item Utilizes homotopy coherence via Eilenberg-Zilber results.
  \item Provides classification of equivariant maps and mapping space homotopy types.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482222] Equivariant crossed complexes for topological groups.
  \item[MO 482248] Homotopy coherence in crossed complex mapping spaces.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 511854] "Classifying spaces for equivariant crossed complexes".
  \item[Math.SE 511881] "Eilenberg-Zilber tools for crossed complexes".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Background.} Review crossed complexes and equivariance (Math.SE 511854).
  \item \textbf{Topological groups.} Explain generalization beyond discrete cases (MO 482222).
  \item \textbf{Homotopy coherence.} Detail methods using Eilenberg-Zilber (MO 482248, Math.SE 511881).
  \item \textbf{Mapping spaces.} Summarize classification and weak types.
  \item \textbf{Applications.} Mention equivariant function spaces.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for coherence constructions and classification results.
  \item Link MO 482222/482248 and Math.SE 511854/511881.
  \item Highlight mapping-space consequences in PlanetMath entry.
\end{itemize}
