% PlanetMath proposal draft for arXiv:math/9901103
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{On faded cosheaves of sets}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9901103, "On Faded Cosheaves of Sets" (1999-01-24)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Zouboff proves the category of faded cosheaves on a sober space $(B,立)$ is equivalent to a category $\mathrm{Sett}(B,立)$ of maps over $B$ with enlarged morphisms. Conversely, if every cosheaf over a $T_0$-space is isomorphic to a cosheaf of tubes, then the space is sober.
\begin{enumerate}
  \item Equates faded cosheaves with $\mathrm{Sett}(B,立)$.
  \item Provides converse: cosheaves of tubes imply sobriety.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483351] Faded cosheaves vs. cosheaves of tubes.
  \item[MO 483378] Sobriety criteria via cosheaves.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 513031] "Examples of faded cosheaves".
  \item[Math.SE 513057] "Category Sett(B,立)".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Faded cosheaves.} Define and motivate (Math.SE 513031).
  \item \textbf{Sett category.} Describe equivalence (MO 483351, Math.SE 513057).
  \item \textbf{Sobriety.} Explain converse criterion (MO 483378).
  \item \textbf{Examples.} Work out sober/non-sober cases.
  \item \textbf{Applications.} Link to cosheaf theory in geometry.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for the equivalence proof and converse.
  \item Link MO 483351/483378 and Math.SE 513031/513057.
  \item Emphasize categorical interpretation for PlanetMath.
\end{itemize}
