% PlanetMath proposal draft for arXiv:math/9903167
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{A Giraud-type characterization of simplicial categories associated to closed model categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9903167, "A Giraud-type characterization of the simplicial categories associated to closed model categories as $\infty$-pretopoi" (1999-03-29)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Carlos Simpson characterizes simplicial categories arising as Dwyer-Kan localizations of cofibrantly generated model categories via Giraud-style axioms, defining $\infty$-pretopoi and $
fty$-topoi.
\begin{enumerate}
  \item Shows equivalence between being a DK localization of a model category and satisfying homotopy colimit generation conditions.
  \item Introduces $\infty$-pretopos and $\infty$-topos notions via adjoint pairs.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483573] $\infty$-pretopoi and model categories.
  \item[MO 483600] $
fty$-topos vs. Segal categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 513271] "DK localizations and $\infty$-pretopoi".
  \item[Math.SE 513298] "When does an $\infty$-pretopos become an $\infty$-topos?".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{DK localization.} Explain Dwyer-Kan simplicial localization (Math.SE 513271).
  \item \textbf{Giraud-type axioms.} Present conditions for $\infty$-pretopoi (MO 483573).
  \item \textbf{Adjoint pair.} Discuss inclusion $i:A\to \hat{C}$ and left homotopy adjoint (Math.SE 513298).
  \item \textbf{$\infty$-topos.} State extra finite homotopy limit preservation (MO 483600).
  \item \textbf{Examples.} Provide model categories satisfying the axioms.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv paper to capture the equivalence and definitions.
  \item Link MO 483573/483600 and Math.SE 513271/513298.
  \item Highlight how $\infty$-pretopoi characterize DK localizations.
\end{itemize}
