% PlanetMath proposal draft for arXiv:math/9912060
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu + math-processed-gpu
\section*{Glutoses: a generalization of topos theory}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9912060, "Glutoses: a Generalization of Topos Theory" (1999-12-08)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Molotkov proposes glutoses, generalizing topoi to encompass categories like manifolds, schemes, and noncommutative geometries. The theory yields an extension of Grothendieck schemes to "etale schemes" including etale sheaves. For presites with local generators, glutoses provide universal completions.
\begin{enumerate}
  \item Defines glutoses extending topos theory.
  \item Shows applications to manifolds, schemes, and etale completions.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 485440] Glutoses and generalizing topoi.
  \item[MO 485467] Etale scheme extensions via glutoses.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 515344] "Presite completions to glutoses".
  \item[Math.SE 515370] "Glutoses vs. Grothendieck topoi".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Motivation.} Discuss limits of classical topoi (Math.SE 515370).
  \item \textbf{Definition.} Present glutoses and local generators (MO 485440).
  \item \textbf{Applications.} Describe manifolds/schemes/etale completions (MO 485467, Math.SE 515344).
  \item \textbf{Noncommutative geometry.} Mention universal perspectives.
  \item \textbf{Examples.} Illustrate with presites.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv definitions and application discussions.
  \item Link MO 485440/485467 and Math.SE 515344/515370.
  \item Emphasize glutoses as topos generalizations.
\end{itemize}
