% PlanetMath proposal draft for arXiv:math/9906079
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{An ambiguity in the concept of partial and total derivatives}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9906079, "On an ambiguity in the concept of partial and total derivatives in classical analysis" (1999-06-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Chubykalo, Flores, and Pérez analyze ambiguity in multivariable differential calculus, providing categorical definitions resolving partial vs. total derivative ambiguities and relating their notion to existing definitions.
\begin{enumerate}
  \item Identifies ambiguity in partial/total derivatives for several variables.
  \item Uses category-theoretic language to define derivatives resolving ambiguities.
  \item Shows equivalence with classical definitions.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 484997] Category-theoretic views on derivatives.
  \item[MO 485024] Comparing partial vs. total derivatives.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 514822] "Ambiguity between partial and total derivatives".
  \item[Math.SE 514848] "Categorical definition of derivative".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Ambiguity example.} Describe classic multivariable issue (Math.SE 514822).
  \item \textbf{Categorical reformulation.} Present authors' definition (MO 484997).
  \item \textbf{Comparison.} Relate to standard definitions (MO 485024, Math.SE 514848).
  \item \textbf{Examples.} Work through simple functions.
  \item \textbf{Implications.} Note relevance for classical analysis pedagogy.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv arguments resolving derivative ambiguity.
  \item Link MO 484997/485024 and Math.SE 514822/514848.
  \item Emphasize categorical perspective on derivatives.
\end{itemize}
