% PlanetMath proposal draft for arXiv:math/9906080
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{A Morita theorem for algebras of operators on Hilbert space}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9906080, "A Morita theorem for algebras of operators on Hilbert space" (1999-06-12)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Blecher shows two operator algebras are strongly Morita equivalent (Blecher-Muhly-Paulsen sense) iff their operator module categories are equivalent via completely contractive functors, which are Haagerup tensor products with Morita equivalence bimodules.
\begin{enumerate}
  \item Characterizes strong Morita equivalence through operator module categories.
  \item Identifies implementing functors as Haagerup tensor products with equivalence bimodules.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 484478] Strong Morita equivalence for operator algebras.
  \item[MO 484505] Haagerup tensor implementation of functors.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 514316] "Operator module categories and Morita equivalence".
  \item[Math.SE 514342] "Haagerup tensor products as functors".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Operator algebras.} Summarize strong Morita equivalence (Math.SE 514316).
  \item \textbf{Categorical characterization.} Present theorem (MO 484478).
  \item \textbf{Haagerup tensor products.} Explain functor implementation (MO 484505, Math.SE 514342).
  \item \textbf{Examples.} Provide simple operator algebras.
  \item \textbf{Implications.} Discuss consequences for module theory.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv proof of the Morita theorem.
  \item Link MO 484478/484505 and Math.SE 514316/514342.
  \item Highlight categorical Morita characterization.
\end{itemize}
