% PlanetMath proposal draft for arXiv:math/9810045
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Braided $n$-categories and $\Sigma$-structures}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9810045, "Braided $n$-categories and $\Sigma$-structures" (1998-10-07)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Lawrence Breen associates to a braided 2-stack a torsor with symmetric cube structure ($\Sigma$-structure); triviality equals existence of a fully symmetric monoidal structure. Extending to braided 4-stacks requires $\Gamma_3$-torsor pairs, relating to cubic forms and higher symmetry obstructions.
\begin{enumerate}
  \item Constructs torsors with $\Sigma$-structure encoding symmetry.
  \item Shows triviality corresponds to fully symmetric monoidal structures.
  \item Introduces $\Gamma_3$-torsor pairs for braided 4-stacks.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 481642] $\Sigma$-structures and symmetric refinements.
  \item[MO 481669] $\Gamma_3$-torsor pairs for higher stacks.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 511244] "Braided stacks and torsor structures".
  \item[Math.SE 511271] "Understanding $\Gamma_3$-torsor pairs".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Braided $n$-categories.} Summarize stacks involved (Math.SE 511244).
  \item \textbf{$\Sigma$-structures.} Explain torsor construction and symmetry (MO 481642).
  \item \textbf{Higher torsors.} Detail $\Gamma_3$-pairs and cubic forms (MO 481669, Math.SE 511271).
  \item \textbf{Applications.} Note implications for symmetric monoidal structures on stacks.
  \item \textbf{Examples.} Provide sample braided 2- and 4-stacks.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for constructions and equivalence proofs.
  \item Link MO 481642/481669 and Math.SE 511244/511271.
  \item Emphasize torsor obstructions in PlanetMath entry.
\end{itemize}
