% PlanetMath proposal draft for arXiv:math/9901003
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Meromorphic braided category arising in quantum affine algebras}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9901003, "Meromorphic braided category arising in quantum affine algebras" (1999-01-02)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Yan Soibelman constructs a category of flat vector bundles on an elliptic curve whose representation theory encodes quantum affine algebras. The category carries a braided structure meromorphic along the diagonal.
\begin{enumerate}
  \item Builds the category of flat bundles on an elliptic curve tied to quantum affine algebras.
  \item Shows it carries a meromorphic braided structure with diagonal singularities.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483138] Meromorphic braidings from elliptic curves.
  \item[MO 483164] Quantum affine algebras and flat bundle categories.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512780] "Flat bundles and braided structures".
  \item[Math.SE 512807] "Meromorphic braidings".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Setup.} Describe flat bundle category (Math.SE 512780).
  \item \textbf{Braided structure.} Explain meromorphic braiding (MO 483138, Math.SE 512807).
  \item \textbf{Quantum affine link.} Outline representation-theoretic origin (MO 483164).
  \item \textbf{Applications.} Mention connections to elliptic quantum groups.
  \item \textbf{Future work.} Indicate open problems.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv paper for construction details.
  \item Link MO 483138/483164 and Math.SE 512780/512807.
  \item Highlight meromorphic braided categories for PlanetMath readers.
\end{itemize}
