% PlanetMath proposal draft for arXiv:math/9805134
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Reduction of quantum systems with arbitrary first class constraints and Hecke algebras}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9805134, "Reduction of quantum systems with arbitrary first class constraints and Hecke algebras" (1998-05-28)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Sevostyanov formulates quantum reduction via homology of associative algebras. Given $(A,B,e)$, the associated Hecke algebra $\mathrm{Hk}^*(A,B)$ acts on $\mathrm{H}^*(B,V)$ for an $A$-module $V$, with degree-zero part acting on $B$-invariants to implement reduction. This generalizes BRST complexes to arbitrary first-class constraints.
\begin{enumerate}
  \item Defines Hecke algebras $\mathrm{Hk}^*(A,B)$ via cohomological complexes.
  \item Shows action on $\mathrm{H}^*(B,V)$ and reduction on $B$-invariants.
  \item Interprets the construction as BRST generalization.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482141] Hecke algebras from associative algebra pairs.
  \item[MO 482168] BRST vs. Hecke-based reductions.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 511757] "Computing $\mathrm{Hk}^*(A,B)$ in practice".
  \item[Math.SE 511783] "Associative algebra homology for quantum constraints".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Setup.} Describe associative algebra pairs $(A,B,e)$ (Math.SE 511783).
  \item \textbf{Hecke algebra.} Define $\mathrm{Hk}^*(A,B)$ and BRST generalization (MO 482141).
  \item \textbf{Action.} Explain module actions and reduction (Math.SE 511757, MO 482168).
  \item \textbf{Examples.} Provide simple constrained systems.
  \item \textbf{Outlook.} Mention links to quantum group reductions.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for the Hecke algebra construction and examples.
  \item Reference MO 482141/482168 and Math.SE 511757/511783.
  \item Highlight BRST generalization in PlanetMath entry.
\end{itemize}
