% PlanetMath proposal draft for arXiv:math/9904039
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Joins for (augmented) simplicial sets}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9904039, "Joins for (Augmented) Simplicial Sets" (1999-04-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Ehlers and Porter define a join operation for augmented simplicial sets generalizing the classical join of geometric simplicial complexes, arising naturally from the ordinal sum on $Δ$.
\begin{enumerate}
  \item Introduces joins for augmented simplicial sets.
  \item Connects joins to ordinal sums in $Δ$.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483806] Joins of simplicial sets via ordinal sum.
  \item[MO 483833] Augmented simplicial joints vs. classical join.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 513500] "Computing joins of simplicial sets".
  \item[Math.SE 513526] "Augmented simplicial structures".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Classical join.} Recall geometric join (Math.SE 513500).
  \item \textbf{Augmented simplicial sets.} Discuss setup (Math.SE 513526).
  \item \textbf{Ordinal sum construction.} Explain definition (MO 483806).
  \item \textbf{Properties.} Compare to classical join (MO 483833).
  \item \textbf{Examples.} Provide simple augmented joins.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv definitions/proofs for the join operation.
  \item Link MO 483806/483833 and Math.SE 513500/513526.
  \item Highlight ordinal-sum approach to simplicial joins.
\end{itemize}
