% PlanetMath proposal draft for arXiv:math/9810144
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Periodic cyclic homology as sheaf cohomology}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9810144, "Periodic cyclic homology as sheaf cohomology" (1998-10-23)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Cortiñas shows that the cohomology of the structure sheaf modulo commutators on the noncommutative infinitesimal site of an algebra equals periodic cyclic cohomology. He also computes cohomology of other sheaves (e.g., K-theory) and identifies hypercohomology fiber sequences for the Jones-Goodwillie character.
\begin{enumerate}
  \item Defines the noncommutative infinitesimal site and sheaf modulo commutators.
  \item Proves periodic cyclic cohomology arises as sheaf cohomology.
  \item Computes other sheaf cohomologies, relating to K-theory and negative cyclic homology.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482536] Noncommutative infinitesimal sites.
  \item[MO 482563] Interpreting periodic cyclic homology as sheaf cohomology.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512161] "Jones-Goodwillie fiber via sheaf cohomology".
  \item[Math.SE 512187] "Sheaf modulo commutators".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Infinitesimal sites.} Present Grothendieck vs. noncommutative versions (Math.SE 512187).
  \item \textbf{Structure sheaf.} Describe modulo-commutator sheaf (MO 482536).
  \item \textbf{Periodic cyclic = sheaf cohomology.} Summarize main theorem (MO 482563).
  \item \textbf{Other sheaves.} Include K-theory hypercohomology fiber (Math.SE 512161).
  \item \textbf{Implications.} Connect to cyclic homology/K-theory interactions.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for site definitions and cohomology computations.
  \item Link MO 482536/482563 and Math.SE 512161/512187 discussions.
  \item Highlight interplay between sheaf cohomology and cyclic homology.
\end{itemize}
