% PlanetMath proposal draft for arXiv:math/9908083
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu + math-processed-gpu
\section*{Invitation to composition}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9908083, "Invitation to composition" (1999-08-16)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Kluge, Paal, and Stasheff abstract Gerstenhaber's composition calculus from Hochschild complexes into "comp systems," yielding graded Lie algebras and pre-coboundary operators (derivation deviations) with new proofs via auxiliary variables.
\begin{enumerate}
  \item Defines comp systems mirroring Gerstenhaber composition.
  \item Associates graded Lie algebra and pre-coboundary operators.
  \item Computes derivation deviations using auxiliary variables.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 485640] Comp systems and Gerstenhaber brackets.
  \item[MO 485667] Derivation deviations in Hochschild-like settings.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 515566] "Gerstenhaber brackets via composition".
  \item[Math.SE 515592] "Pre-coboundary operators and derivation deviation".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Gerstenhaber calculus.} Review background (Math.SE 515566).
  \item \textbf{Comp systems.} Present abstract definition (MO 485640).
  \item \textbf{Pre-coboundary operators.} Describe construction (Math.SE 515592).
  \item \textbf{Derivation deviation.} Summarize new proof (MO 485667).
  \item \textbf{Applications.} Mention composition calculus in deformation theory.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv exposition of comp systems and derivation deviations.
  \item Link MO 485640/485667 and Math.SE 515566/515592.
  \item Emphasize abstraction of Gerstenhaber's calculus.
\end{itemize}
