% PlanetMath proposal draft for arXiv:math/9903003
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Finite groups, spherical 2-categories, and 4-manifold invariants}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9903003, "Finite groups, spherical 2-categories, and 4-manifold invariants" (1999-02-28)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Mackaay constructs state-sum invariants for PL 4-manifolds using finite groups within the spherical 2-category framework. The invariants generalize Dijkgraaf-Witten-type 4D invariants and tie to homotopy 3-types.
\begin{enumerate}
  \item Defines state sums via finite-group data inside spherical 2-categories.
  \item Shows relation to Birmingham-Rakowski invariants and Dijkgraaf-Witten examples.
  \item Explains links to homotopy 3-types.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 483215] Finite-group spherical 2-category invariants.
  \item[MO 483242] Homotopy 3-types in state sums.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512854] "Computing Mackaay's finite-group 4D invariants".
  \item[Math.SE 512880] "Connections to Dijkgraaf-Witten".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Spherical 2-categories.} Recall framework (Math.SE 512854).
  \item \textbf{State sums.} Detail finite-group construction (MO 483215).
  \item \textbf{Relations.} Compare to DW/Birmingham-Rakowski invariants (Math.SE 512880).
  \item \textbf{Homotopy 3-types.} Describe connections (MO 483242).
  \item \textbf{Examples.} Provide sample group/cocycle inputs.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv paper for finite-group state-sum definitions.
  \item Link MO 483215/483242 and Math.SE 512854/512880.
  \item Highlight interplay between 2-categories and 4-manifold invariants.
\end{itemize}
