% PlanetMath proposal draft for arXiv:math/9812040
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Galois Theory for Braided Tensor Categories and the Modular Closure}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9812040, "Galois Theory for Braided Tensor Categories and the Modular Closure" (1998-12-07)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Müger studies braided tensor $*$-categories with conjugates and a symmetric subcategory $S$, defining the crossed product $C\rtimes S$ and establishing a Doplicher-Roberts-style Galois correspondence. He analyzes degeneracy, modular closure, and when braidings extend.
\begin{enumerate}
  \item Constructs $C\rtimes S$ and establishes Galois correspondence with closed subgroups.
  \item Determines when braidings extend (depending on degenerate objects $D$).
  \item Defines modular closure $C\rtimes D$ and shows modularity in rational case.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482769] Crossed products of braided tensor categories.
  \item[MO 482796] Degenerate objects and modular closure.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512377] "Understanding $C\rtimes S$".
  \item[Math.SE 512405] "When does the braiding extend?".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Setup.} Review braided tensor $*$-categories with conjugates (Math.SE 512377).
  \item \textbf{Crossed products.} Present construction and Galois correspondence (MO 482769).
  \item \textbf{Degenerate subcategory.} Discuss $D$ and extension criteria (Math.SE 512405, MO 482796).
  \item \textbf{Modular closure.} Explain $C\rtimes D$ and modularity.
  \item \textbf{Applications.} Mention modular data and ribbon categories.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv details on crossed products and Galois correspondence.
  \item Link MO 482769/482796 and Math.SE 512377/512405.
  \item Highlight modular closure concept in PlanetMath entry.
\end{itemize}
