% PlanetMath proposal draft for arXiv:math/0001151
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu + math-processed-gpu
\section*{Deformations of algebras over operads and Deligne's conjecture}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/0001151, "Deformations of algebras over operads and Deligne's conjecture" (2000-01-26)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Kontsevich and Soibelman develop deformation theory for operads/algebras via free resolutions, describe formal moduli spaces, and prove Deligne's conjecture by constructing an operad acting on the Hochschild complex. They show Grothendieck-Teichmüller group acts on moduli of 2-algebra structures.
\begin{enumerate}
  \item Builds deformation theory for operads using Boardman-Vogt resolutions.
  \item Constructs geometric operad acting on Hochschild complexes, proving Deligne's conjecture.
  \item Notes Grothendieck-Teichmüller actions.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 485859] Operadic deformation theory.
  \item[MO 485886] Operads acting on Hochschild complexes.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 515784] "Deligne's conjecture explanations".
  \item[Math.SE 515810] "Grothendieck-Teichmüller actions on 2-algebras".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Operadic deformations.} Present general theory (MO 485859).
  \item \textbf{Hochschild complex action.} Describe geometric operad (MO 485886, Math.SE 515784).
  \item \textbf{GT actions.} Summarize consequences (Math.SE 515810).
  \item \textbf{Formal moduli.} Explain Boardman-Vogt resolutions.
  \item \textbf{Examples.} Mention brace vs. new operad comparison.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv proofs of Deligne's conjecture and deformation framework.
  \item Link MO 485859/485886 and Math.SE 515784/515810.
  \item Highlight GT action on moduli of 2-algebra structures.
\end{itemize}
