% PlanetMath proposal draft for arXiv:math/9810058
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{On the Breen--Baez--Dolan stabilization hypothesis for Tamsamani weak $n$-categories}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9810058, "On the Breen-Baez-Dolan stabilization hypothesis for Tamsamani's weak $n$-categories" (1998-10-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Carlos Simpson proves that if $2k \ge n$, any $k$-connected weak $n$-category can be delooped to a $k+1$-connected weak $n+1$-category with equivalent endomorphism $\mathrm{Hom}_Y(y,y) \cong A$, giving substantial evidence for Baez-Dolan stabilization.
\begin{enumerate}
  \item States and proves the delooping result for Tamsamani weak $n$-categories.
  \item Relates to stabilization hypothesis and earlier work (q-alg/9503002, math/9802029).
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482389] Delooping Tamsamani weak $n$-categories.
  \item[MO 482415] Connections to stabilization hypothesis.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512008] "Understanding Simpson's stabilization result".
  \item[Math.SE 512034] "Examples of $k$-connected weak $n$-categories".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Stabilization hypothesis.} Summarize Baez-Dolan/Breen context (MO 482415).
  \item \textbf{Tamsamani weak $n$-categories.} Review definitions (Math.SE 512034).
  \item \textbf{Delooping theorem.} Present Simpson's main result (MO 482389, Math.SE 512008).
  \item \textbf{Implications.} Discuss structural consequences.
  \item \textbf{Open questions.} Note remaining parts of stabilization.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv argument for the delooping result.
  \item Link MO 482389/482415 and Math.SE 512008/512034.
  \item Emphasize stabilization context in PlanetMath entry.
\end{itemize}
