% PlanetMath proposal draft for arXiv:math/9904075
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{The Whittaker model of the center of the quantum group and Hecke algebras}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9904075, "The Whittaker model of the center of the quantum group and Hecke algebras" (1999-04-15)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Sevostyanov generalizes Kostant's Whittaker model for $U(\mathfrak{g})$ to quantum groups, using quantum analogues of regular nilpotent elements and Hecke algebras $Hk^*(A,B)$ introduced earlier. The Whittaker model yields a commutative subalgebra of $U_q(\mathfrak{b})$, feeds into deformed quantum Toda lattices, and relates to conjugacy classes via quasi-classical limits.
\begin{enumerate}
  \item Constructs a quantum Whittaker model using regular nilpotent analogues.
  \item Interprets the model homologically via Hecke algebras $Hk^*(A,B)$.
  \item Applies to deformed quantum Toda lattices and conjugacy classes.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 484259] Quantum Whittaker models.
  \item[MO 484286] Hecke algebra interpretations of quantum centers.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 514082] "Extending Kostant's Whittaker model to $U_q(\mathfrak{g})$".
  \item[Math.SE 514108] "Hecke algebra actions on quantum centers".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Kostant's Whittaker model.} Recall classical case (Math.SE 514082).
  \item \textbf{Quantum analogue.} Present Sevostyanov's construction (MO 484259).
  \item \textbf{Hecke algebras.} Explain homological interpretation (MO 484286, Math.SE 514108).
  \item \textbf{Applications.} Outline quantum Toda lattice results.
  \item \textbf{Quasi-classical limit.} Mention relation to conjugacy classes.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv sections on quantum Whittaker models and Hecke algebra actions.
  \item Link MO 484259/484286 and Math.SE 514082/514108.
  \item Emphasize interplay between quantum centers and Toda lattices.
\end{itemize}
