% PlanetMath proposal draft for arXiv:math/9807049
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Descente pour les n-champs (Descent for n-stacks)}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9807049, "Descente pour les n-champs" (1998-07-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Hirschowitz and Simpson develop Segal $n$-stacks via closed model categories, giving definition via limits, characterizations through descent data, construction of associated stacks, strictification, and descent for the $(n+1)$-prestack of $n$-stacks. They also prove descent for Segal 1-prestacks arising from left Quillen presheaves of model categories.
\begin{enumerate}
  \item Defines $n$-stacks using cmc methods and limit descriptions.
  \item Gives effectivity/descent characterizations and strictification results.
  \item Proves descent for $	ext{Segal }1$-prestacks from left Quillen presheaves, applying to complexes.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 481401] Descent conditions for $n$-stacks via cmc.
  \item[MO 481428] Strictification of weak $n$-stacks.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 511012] "Building $n$-stacks from prestacks".
  \item[Math.SE 511039] "Left Quillen presheaves and Segal prestacks".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Definitions.} Present $n$-stacks via limits (Math.SE 511012).
  \item \textbf{Descent criteria.} Summarize effectivity characterizations (MO 481401).
  \item \textbf{Strictification.} Explain equivalence with strict $n$-stacks (MO 481428).
  \item \textbf{Segal prestacks.} Discuss left Quillen presheaf descent (Math.SE 511039).
  \item \textbf{Applications.} Mention complexes of sheaves and higher geometry.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source for definitions and descent proofs.
  \item Link MO 481401/481428 and Math.SE 511012/511039.
  \item Emphasize strictification/descent interplay in PlanetMath entry.
\end{itemize}
