% PlanetMath proposal draft for arXiv:math/9904041
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Freeness conditions for crossed squares and squared complexes}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9904041, "Freeness conditions for crossed squares and squared complexes" (1999-04-09)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Mutlu and Porter investigate totally free crossed squares and squared complexes, interpreting free simplicial groups with CW-basis via tensor products of crossed modules, yielding algebraic derivations of results by Brown and Loday.
\begin{enumerate}
  \item Defines totally free crossed squares/squared complexes.
  \item Interprets free simplicial group data via crossed modules.
  \item Provides algebraic proofs of Brown-Loday results.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 484026] Totally free crossed squares.
  \item[MO 484053] Tensor products of crossed modules.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 513797] "Crossed squares from simplicial groups".
  \item[Math.SE 513823] "Squared complexes and freeness".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Crossed squares.} Review definitions and freeness (Math.SE 513797).
  \item \textbf{Simplicial interpretation.} Explain CW-basis translation (MO 484026).
  \item \textbf{Tensor descriptions.} Summarize Ellis's results (MO 484053, Math.SE 513823).
  \item \textbf{Applications.} Highlight algebraic derivations of Brown-Loday.
  \item \textbf{Examples.} Provide simple crossed square data.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv paper for definitions and tensor-product descriptions.
  \item Link MO 484026/484053 and Math.SE 513797/513823.
  \item Emphasize connections between simplicial groups and crossed squares.
\end{itemize}
