% PlanetMath proposal draft for arXiv:math/9911207
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu + math-processed-gpu
\section*{External tensor product of categories of perverse sheaves}
\subsection*{Source}
\begin{itemize}
  \item arXiv:math/9911207, "External tensor product of categories of perverse sheaves" (1999-11-26)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Lyubashenko shows that, under assumptions, the Deligne tensor product of categories of constructible perverse sheaves on pseudomanifolds $X$ and $Y$ equals the category on $X\times Y$, identifying Deligne's external product functor with the geometric external tensor product.
\begin{enumerate}
  \item States conditions ensuring $\mathcal{P}(X) \boxtimes \mathcal{P}(Y) \simeq \mathcal{P}(X\times Y)$.
  \item Identifies Deligne external tensor product with geometric external tensor product.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 485713] Tensor products of perverse sheaf categories.
  \item[MO 485740] Deligne vs. geometric external products.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 515638] "External tensor products of perverse sheaves".
  \item[Math.SE 515664] "Deligne tensor product interpretations".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Perverse sheaf categories.} Summarize setup (Math.SE 515638).
  \item \textbf{Deligne tensor product.} Review definition (MO 485713).
  \item \textbf{External tensor product.} Present equivalence (MO 485740, Math.SE 515664).
  \item \textbf{Examples.} Provide pseudomanifold cases.
  \item \textbf{Applications.} Mention tensor products in geometric representation theory.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import arXiv conditions and equivalence proof.
  \item Link MO 485713/485740 and Math.SE 515638/515664.
  \item Highlight identification of Deligne and geometric external products.
\end{itemize}
