% PlanetMath proposal draft for arXiv:q-alg/9503002
% Source corpora: arXiv math.CT eprints, storage/mo-processed-gpu, storage/math-processed-gpu
\section*{Higher-dimensional algebra and topological quantum field theory}
\subsection*{Source}
\begin{itemize}
  \item arXiv:q-alg/9503002, "Higher-dimensional Algebra and Topological Quantum Field Theory" (1995-03-05)
  \item StackExchange cross-links via storage/mo-processed-gpu + math-processed-gpu
\end{itemize}
\subsection*{Synopsis}
Baez and Dolan outline a program describing extended TQFTs via weak $n$-categories. They propose suspension operations on weak $n$-categories, conjecture stabilization after $k\ge n+2$, and describe unitary extended TQFTs as weak $n$-functors from a free stable weak $n$-category with duals to $n$-Hilbert spaces. Examples include tangle categories, cobordisms, and quantum double constructions.
\begin{enumerate}
  \item Reviews progress toward a definition of $n$-category suited to TQFTs.
  \item Proposes stabilization via suspensions.
  \item Describes extended TQFTs as weak $n$-functors into $n$-Hilbert spaces.
  \item Sketches applications to deformation quantization and quantum doubles.
\end{enumerate}
\subsection*{MathOverflow cues}
\begin{description}
  \item[MO 482925] Stabilization hypotheses for weak $n$-categories.
  \item[MO 482952] $n$-Hilbert spaces in extended TQFTs.
\end{description}
\subsection*{Math.SE anchors}
\begin{description}
  \item[Math.SE 512514] "Understanding Baez--Dolan's suspension operation".
  \item[Math.SE 512541] "Extended TQFTs as weak functors".
\end{description}
\subsection*{Encyclopedia outline}
\begin{enumerate}
  \item \textbf{Motivation.} Summarize higher-dimensional algebra for TQFT (Math.SE 512514).
  \item \textbf{Weak $n$-categories.} Present stabilization ideas (MO 482925).
  \item \textbf{Extended TQFT functors.} Describe the proposed $n$-Hilbert functor picture (MO 482952, Math.SE 512541).
  \item \textbf{Examples.} Mention tangles, cobordisms, quantum doubles.
  \item \textbf{Outlook.} Note links to later stabilization results.
\end{enumerate}
\subsection*{Action items}
\begin{itemize}
  \item Import the arXiv source to capture stabilization conjectures and extended TQFT model.
  \item Link MO 482925/482952 and Math.SE 512514/512541 threads.
  \item Emphasize the proposed program for PlanetMath readers.
\end{itemize}
